### 2015-02-17 proofs.tex
moved proofs to new file

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb,amsthm}
\usepackage{color}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{verbatim}

\numberwithin{equation}{section}
\newtheorem{theorem}[equation]{Theorem}
\newtheorem{proposition}[equation]{Proposition}
\newtheorem{lemma}[equation]{Lemma}
\newtheorem{corollary}[equation]{Corollary}
\newtheorem{conjecture}[equation]{Conjecture}
\newtheorem{problem}[equation]{Problem}
\newtheorem{remark}[equation]{Remark}
\newtheorem{definition}[equation]{Definition}
\newenvironment{defn}[1][]{%
    \begin{definition}[#1]\pushQED{\qed}}{\popQED \end{definition}}
\parindent=0in
\parskip=0.15in

\newcommand{\xx}[1]{\textcolor{blue}{#1}}
\newcommand{\zb}{\overline{z}}
\newcommand{\cc}[1]{\overline{#1}}
\newcommand{\m}[1]{\left|#1\right|}
\newcommand{\p}[1]{\left(#1\right)}
\newcommand{\cis}{\text{cis}\,}
\newcommand{\sgn}{\text{sgn}}
\newcommand{\D}{\triangle}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\f}[1]{\sum_{n=-\infty}^\infty #1_ne^{inx}}
\newcommand{\fn}[1]{\sum_{n=-\infty}^\infty #1e^{inx}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\mm}[1]{\m{\m{#1}}}
\newcommand{\ang}[1]{\left\langle #1 \right\rangle}

\begin{document}

\section{$p=3, 3 \mid n$, $n-1$ case full argument}

\subsection{Generators}

Let $x_1,\dots,x_{n-1}$ be a basis for the $n-1$ dimensional representation of $S_n$ derived from the standard representation with basis $e_0,\dots,e_{n-1}$ by the relation $x_i=e_i-e_0$ and the action of the symmetric group defined accordingly. Let $s_{ij}$ be the transposition of $i$ and $j$, for $0 \le i < j \le n-1$.

For $1 \le i < j \le n-1$, the relevant eigenvectors are $x_i-x_j$. For $s_{0i}$ for $1 \le i \le n-1$, the relevant eigenvector is $x_i$.

Let $f_a$ for $a=1,\dots, n-1$ be $f_a = -x_a^3+c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)$. We will show that all the $f_a$ are killed by Dunkl operators. Because of their symmetry, we need only consider $f_1$. Since $f_1$ is symmetric in the $x_i$ excluding $x_1$, the only Dunkl operators we need consider are $D_1,D_2$.

We note that $f_1$ is preserved by $s_{ij}$ for all $i,j >1$. We consider $s_{1a}$ for $2 \le a$. We see that $s_{1a}f_1=-x_a^3+c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)=f_a$. Then:

\begin{align*}
f_1-f_a&=-(x_1-x_a)^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)-x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j(x_1-x_a)\right)\\
&=-(x_1-x_a)^3+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_a-x_i)(x_1-x_a)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j(x_1-x_a)\right)\\
\end{align*}

Then $\frac{f_1-s_{1a}f_1}{x_1-x_a}=-(x_1-x_a)^2+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.

We consider $s_{0a}$ for $2 \le a$. We see that $s_{01}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$. We see that $s_{0a}f_1=-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)$. %todo

The only remaining case to consider is $s_{01}$. We see that $s_{01}$ sends $x_1$ to $-x_1$ and $x_a$ for $a \ge 2$ to $x_a-x_1$. Then $s_{01}f_1$ goes to

\begin{align*}
&-(-x_1)^3+c \left(\sum_{i=2}^{n-1} (-x_1)(x_i-x_1)(-x_1-(x_i-x_1))\right)+c^2 \left(\sum_{i=2}^{n-1} \sum_{j=2}^{n-1} (x_i-x_1)(x_j-x_1)(-x_1)\right)+\\&2c^2\left(\sum_{i=2}^{n-1}(x_i-x_1)x_1^2\right)+c^2(-x_1)^3\\
&=x_1^3+c \left(\sum_{i=2}^{n-1} x_1x_i(x_i-x_1)\right)+c^2 \left(\sum_{i=2}^{n-1} \sum_{j=2}^{n-1}-x_ix_jx_1+x_ix_1^2+x_jx_1^2-x_1^3\right)+\\&2c^2\left(\sum_{i=2}^{n-1}(x_i-x_1)x_1^2\right)+2c^2x_1^3\\
&=x_1^3+c \left(\sum_{i=2}^{n-1} x_1x_i(x_i-x_1)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1}-x_ix_jx_1\right)\\  
&=-f_1\\
\end{align*}

The above used the fact that $n-2 \equiv 1 \mod 3$. Therefore $\frac{f_1-s_{01}f_1}{x_1}=2f_1/x_1=-f_1/x_1=x_1^2+c \left(\sum_{i=1}^{n-1} x_i(x_i-x_1)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.

We can use these to calculate the effects of the Dunkl operators.

\subsection{Dunkl operators}

\subsubsection{$D_1f_1$}

We first consider $D_1f_1=\partial_1f_1-c\sum_{a > 1} \frac{f_1-s_{1a}f_1}{x_1-x_a}-c\frac{f_1-s_{01}f_1}{x_1}$. Let $G_1=\sum_{a > 1} \frac{f_1-s_{1a}f_1}{x_1-x_a}, G_2=\frac{f_1-s_{01}f_1}{x_1}$. We wish to show that $\partial_1f_1=cG_1+cG_2$, since then $D_1f_1=0$. We calculate $\partial_1f_1$:

\begin{align*}
\partial_1f_1&=\partial_1\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
&=c \left(\sum_{i=2}^{n-1} x_1x_i+x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=2}^{n-1} \sum_{j=2}^{n-1} x_ix_j\right)+2c^2 \left(\sum_{i=2}^{n-1} 2x_ix_1\right)\\
&=c \left(\sum_{i=2}^{n-1} x_1x_i+x_ix_1-x_i^2\right)+c^2 \left(\sum_{i=2}^{n-1} \sum_{j=2}^{n-1} x_ix_j\right)+c^2 \left(\sum_{i=2}^{n-1} x_ix_1\right)\\
&=c \left(\sum_{i=2}^{n-1} -x_1x_i-x_i^2\right)+c^2 \left(\sum_{i=2}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)\\
\end{align*}

We also see that $G_1= \sum_{a > 1} \frac{f_1-s_{1a}f_1}{x_1-x_a} = \sum_{a=2}^{n-1} -(x_1-x_a)^2+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$ and $G_2=x_1^2+c \left(\sum_{i=1}^{n-1} x_i(x_i-x_1)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.

Since $n-2 \equiv 1 \mod 3$, we see that the $c^2$ terms cancel in $G_1+G_2$. We also note that $x_i(x_i-x_1)=x_i(x_1+x_1-x_i)-x_i^2$ for all $i$, so $G_1+G_2= x_1^2-c\left(\sum_{i=1}^{n-1} x_i^2\right)+\sum_{a=1}^{n-1} -(x_1-x_a)^2+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_a-x_i)\right)$.

\begin{align*}
G_1+G_2&= x_1^2-c\left(\sum_{i=1}^{n-1} x_i^2\right)+\sum_{a=1}^{n-1} -(x_1-x_a)^2+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_a-x_i)\right)\\
&= x_1^2-c\left(\sum_{i=1}^{n-1} x_i^2\right)+\sum_{a=1}^{n-1} -x_1^2-x_a^2+2x_ax_1+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_a-x_i)\right)\\
&= x_1^2-c\left(\sum_{i=1}^{n-1} x_i^2\right)+\sum_{j=1}^{n-1} -x_1^2-x_j^2+2x_jx_1+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_j-x_i)\right)\\
&= x_1^2+-(n-1)x_1^2-c\left(\sum_{i=1}^{n-1} x_i^2\right)+\sum_{j=1}^{n-1} -x_j^2-x_jx_1+c \left(\sum_{i=1}^{n-1} x_i(x_1+x_j-x_i)\right)\\
&= 2x_1^2-c\left(\sum_{i=1}^{n-1} x_i^2\right)+\sum_{j=1}^{n-1} \left(-x_j^2-x_jx_1\right)+c \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_1+x_ix_j-x_i^2\right)\\
&= \sum_{j=2}^{n-1} \left(-x_j^2-x_jx_1\right)-c\left(\sum_{i=1}^{n-1} x_i^2\right)+c \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_1+x_ix_j-x_i^2\right)\\
&= \sum_{j=2}^{n-1} \left(-x_j^2-x_jx_1\right)-c\left(\sum_{i=1}^{n-1} x_i^2\right)+c \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1}x_ix_j\right)-c \left(\sum_{i=1}^{n-1} x_ix_1-x_i^2\right)\\
&= \sum_{j=2}^{n-1} \left(-x_j^2-x_jx_1\right)-c\left(\sum_{i=1}^{n-1} x_i^2\right)+c \left(\sum_{i=1}^{n-1} \sum_{j=2}^{n-1}x_ix_j\right)+c \left(\sum_{i=1}^{n-1} x_i^2\right)\\
&= \sum_{j=2}^{n-1} \left(-x_j^2-x_jx_1\right)+c \left(\sum_{i=1}^{n-1} \sum_{j=2}^{n-1}x_ix_j\right)\\
\end{align*}

Then a simple change of indices tells us that $cG_1+cG_2=\partial_1f_1$ as desired.

\subsubsection{$D_2f_1$}

We see that $D_2f_1 = \partial_2f_1-c\frac{f_1-s_{12}f_1}{x_2-x_1} + \dots$. %todo

\subsection{Complete intersection}

Then we see that the ideal $I$ generated by $f_1,\dots,f_{n-1}$ has $I \subseteq J$ where $J$ is the kernel of the $\beta$ form, since the generators $f_1,\dots,f_{n-1}$ are killed by the Dunkl operators.

Let $I$ be the ideal generated by $f_1,\dots, f_{n-1}$. We will show that $A/I$, where $A=k[x_1,\dots,x_{n-1}]$, is a complete intersection by showing that $f_1(x) = \dots = f_{n-1}(x)=0$ implies $x=0$.

A simple algebraic manipulation lets us see that $f_a=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$. %todo
We also note that $\sum_{i=1}^{n-1} f_i = (c^2+2)\sum_{i=1}^{n-1} x_i^3 = (c^2+2)\left(\sum_{i=1}^{n-1} x_i \right)^3$ %todo
Therefore if $f_1(x) = \dots = f_{n-1}(x)=0$, we see that $\sum_{i=1}^{n-1} x_i = 0$. %notational fix?
Modulo this new relation, we see that $f_a=x_a\left(-x_a^2+\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$. Therefore if $f_a=0$ for all $a$, we see that for each $a$, either $x_a=0$ or $x_a$ is a square root of $C=\sum_{1 \le i < j  \le n-1} 2cx_ix_j$. If $C=0$ or $C$ has no square roots, then all the $x_a$ are 0 and we are done; so we assume $C$ has two square roots which are additive inverses of each other. Then each pair $x_ix_j$ either multiply to $\pm C$ or $0$, so $C=2cmC$ for some integer $m$. Then $(1+cm)C=0$; if $C \ne 0$, then $1+cm=0$; however, $m$ is an integer, so this is impossible. Therefore $C=0$, so all the $x_a$ are $0$.

Therefore $f_1(x) = \dots = f_{n-1}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection; it then must have Hilbet polynomial $h_{A/I}(t)=(t^2+t+1)^{n-1}$.

By Proposition 3.4 in http://arxiv.org/abs/1107.0504, we see that the Hilbert polynomial of $A/J$ is $(t^2+t+1)^{n-1}h(t^3)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$. Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal.

\end{document}

### 2015-02-19 proofs.tex
more dunkl operators

@@
 
-We consider $s_{0a}$ for $2 \le a$.
-We see that $s_{01}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$.
-We see that $s_{0a}f_1=-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)$.
-%todo
+We consider $s_{0a}$ for $2 \le a$. We see that $s_{0a}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$. We see that:
+
+\begin{align*}
+s_{0a}f_1&=s_{0a}\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
+&=s_{0a}\left(-x_1^3+c \left(\sum_{i \ne a} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i \ne a} \sum_{j \ne a} x_ix_jx_1\right)+cx_1x_a(x_1-x_i)+c^2x_a^2x_1+2c^2 \sum_{i \ne a} x_ix_ax_1 \right)\\
+&=-(x_1-x_a)^3+c \left(\sum_{i \ne a} (x_1-x_a)(x_i-x_a)(x_1-x_a-x_i+x_a)\right)+\\&c^2 \left(\sum_{i \ne a} \sum_{j \ne a} (x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+c(x_1-x_a)(-x_a)(x_1-x_a-x_i+x_a)+c^2(-x_a)^2(x_1-x_a)+\\&2c^2 \sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a) \\
+&=-x_1^3+x_a^3+c \left(\sum_{i \ne a} (x_1-x_a)(x_i-x_a)(x_1-x_i)\right)+\\&c^2 \left(\sum_{i \ne a} \sum_{j \ne a} (x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+c(x_1-x_a)(-x_a)(x_1-x_i)+c^2x_a^2(x_1-x_a)+\\&2c^2 \sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a) \\
+\end{align*} %todo
 
@@
 
-Let $I$ be the ideal generated by $f_1,\dots, f_{n-1}$.
+We note that the $f_i$ are linearly independent, since $x_i^3$ has nonzero coefficient in $f_j$ only when $i=j$.
 We will show that $A/I$, where $A=k[x_1,\dots,x_{n-1}]$, is a complete intersection by showing that $f_1(x) = \dots = f_{n-1}(x)=0$ implies $x=0$.

### 2015-02-19 proofs.tex
cleaned up s_02 calculation

--- 2015-02-17 proofs.tex
@@
 
-We consider $s_{0a}$ for $2 \le a$.
-We see that $s_{01}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_a-x_1$.
-We see that $s_{0a}f_1=-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)$.
-%todo
+We consider $s_{0a}$ for $2 \le a$. We see that $s_{0a}$ sends $x_a$ to $-x_a$ and $x_i$ for $i \ne a$ to $x_i-x_a$. We see that:
+
+\begin{align*}
+s_{0a}f_1&=s_{0a}\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
+&=s_{0a}\left(-x_1^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)+cx_1x_a(x_1-x_a)+c^2 \left(\sum_{i\ne a}\sum_{j \ne a}x_ix_jx_1\right)+2c^2\left(\sum_{i \ne a} x_ix_ax_1\right)+c^2x_a^2x_1\right)\\
+&=-(x_1-x_a)^3+c \left(\sum_{i \ne 1,a} (x_1-x_a)(x_i-x_a)(x_1-x_i)\right)+c(x_1-x_a)(-x_a)(x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\\end{align*}\begin{align*}
+&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1(x_i-x_a)(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_a(x_a-x_i)(x_i-x_1)\right)+c(x_1-x_a)(-x_a)(x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_ax_i(x_a-x_i)\right)+c\left(\sum_{i \ne 1,a}-x_1^2x_a+x_a^2x_1\right)+c(x_1-x_a)(-x_a)(x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_ax_i(x_a-x_i)\right)
+-cx_1x_a(x_1-x_a)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i \ne 1,a} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i \ne 1,a} x_ax_i(x_a-x_i)\right)
++cx_1x_a(x_1-x_a)-cx_1x_a(x_a-x_1)+\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_i-x_a)(x_j-x_a)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_i-x_a)(-x_a)(x_1-x_a)\right)+c^2(-x_a)^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j-x_ax_j-x_ax_i+x_a^2)(x_1-x_a)\right)+2c^2\left(\sum_{i \ne a} (x_a^2-x_ax_i)(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j+x_a^2)(x_1-x_a)\right)+c^2\left(\sum_{i \ne a} x_ax_i(x_1-x_a)\right)+c^2\left(\sum_{i \ne a} (x_a^2-x_ax_i)(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++\\&c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j+x_a^2)(x_1-x_a)\right)+c^2\left(\sum_{i \ne a} x_a^2(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\\end{align*}\begin{align*}
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j)(x_1-x_a)\right)+\\&2c^2\left(\sum_{i \ne a} x_a^2(x_1-x_a)\right)+c^2x_a^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j)(x_1-x_a)\right)+\\& 2c^2x_a^2(x_1-x_a)+c^2x_a^2(x_1-x_a)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++c^2 \left(\sum_{i\ne a}\sum_{j \ne a}(x_ix_j)(x_1-x_a)\right)\\
+&=-x_1^3+x_a^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)
++c^2 \left(\sum_{i\ne a}\sum_{j \ne a}x_ix_jx_1-x_ix_jx_a)\right)\\
+&=f_1-f_a
+\end{align*}
+
+Then $\frac{f_1-s_{0a}f_1}{x_a}=-f_a/x_a=x_a^2+c \left(\sum_{i=1}^{n-1} x_i(x_i-x_a)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.
 
@@
 
-We see that $D_2f_1 = \partial_2f_1-c\frac{f_1-s_{12}f_1}{x_2-x_1} + \dots$. %todo
+We see that $D_2f_1 = \partial_2f_1-c\frac{f_1-s_{12}f_1}{x_2-x_1} -c\frac{f_1-s_{02}f_1}{x_2}$.
 

### 2015-02-20 proofs.tex
writeup for n=0 mod 3 complete

@@
 
-Then $\frac{f_1-s_{0a}f_1}{x_a}=-f_a/x_a=x_a^2+c \left(\sum_{i=1}^{n-1} x_i(x_i-x_a)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.
+Then $\frac{f_1-s_{0a}f_1}{x_a}=f_a/x_a=-x_a^2-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_a)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.
 
@@
 
+We calculate $\partial_2f_1$:
+
+\begin{align*}
+\partial_2f_1&=\partial_2\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
+&=\partial_2\left(-x_1^3+c \left(\sum_{i=3}^{n-1} x_1x_i(x_1-x_i)\right)+cx_1x_2(x_1-x_2)+c^2 \left(\sum_{i \ne 2}\sum_{j \ne 2} x_ix_jx_1\right)+2c^2\left(\sum_{i \ne 2}x_ix_1x_2\right)+c^2x_2^2x_1\right)\\
+&=cx_1^2-2cx_1x_2+2c^2\left(\sum_{i \ne 2}x_ix_1\right)+2c^2x_2x_1\\
+&=cx_1^2+cx_1x_2+2c^2\left(\sum_{i=1}^{n-1}x_ix_1\right)\\
+\end{align*}
+
+Let $G_1=\frac{f_1-s_{12}f_1}{x_2-x_1}, G_2=\frac{f_1-s_{02}f_1}{x_2}$. If $c(G_1+G_2)=\partial_2f_1$, then $D_2f_1=0$.
+
+\begin{align*}
+G_1+G_2&=\frac{f_1-s_{12}f_1}{x_2-x_1}+\frac{f_1-s_{02}f_1}{x_2}\\
+&=(x_1-x_2)^2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)-
+x_2^2-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_2)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)\\
+&=x_1^2+x_1x_2+x_2^2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i)\right)-
+x_2^2-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_2)\right)\\
+&=x_1^2+x_1x_2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_2)\right)\\
+&=x_1^2+x_1x_2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i+x_i-x_2)\right)\\
+&=x_1^2+x_1x_2-c \left(\sum_{i=1}^{n-1} x_ix_1\right)\\
+\end{align*}
+
+Then we see easily that $\partial_2f_1=cG_1+cG_2$, so $D_2f_1=0$ as desired.
+
 \subsection{Complete intersection}
@@
 
-A simple algebraic manipulation lets us see that $f_a=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$.
-%todo
-We also note that $\sum_{i=1}^{n-1} f_i = (c^2+2)\sum_{i=1}^{n-1} x_i^3 = (c^2+2)\left(\sum_{i=1}^{n-1} x_i \right)^3$ %todo
-Therefore if $f_1(x) = \dots = f_{n-1}(x)=0$, we see that $\sum_{i=1}^{n-1} x_i = 0$. %notational fix?
+Recall $f_a = -x_a^3+c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)$.
+
+We also note that $\left(\sum_{i=1}^{n-1} x_i \right)^2= \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$, and $\left(\sum_{i=1}^{n-1} x_i \right)^2+\sum_{1 \le i < j \le n-1} x_ix_j = \sum_{i=1}^{n-1} x_i^2$ modulo $3$.
+
+Therefore:
+
+\begin{align*}
+f_a &= -x_a^3+c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)\\
+&= -x_a^3+c \left(\sum_{i=1}^{n-1} x_a^2x_i-x_ax_i^2\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)\\
+&= -x_a^3+cx_a^2 \left(\sum_{i=1}^{n-1} x_i\right) -cx_a\left( \sum_{i=1}^{n-1} x_i^2\right)+c^2x_a \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)\\
+&= -x_a^3+cx_a^2 \left(\sum_{i=1}^{n-1} x_i\right) +2cx_a\left(\sum_{i=1}^{n-1} x_i \right)^2+2cx_a\left(\sum_{1 \le i < j \le n-1} x_ix_j\right)+c^2x_a\left(\sum_{i=1}^{n-1} x_i \right)^2\\
+&=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)
+\end{align*}
+
+We see that $f_a=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$.
+
+We now consider the sum of the $f_a$:
+
+\begin{align*}
+\sum_{a=1}^{n-1} f_a &= \sum_{a=1}^{n-1}\left(-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)\right)\\
+ &= \left(\sum_{a=1}^{n-1}-x_a^3\right)+c\left(\sum_{a=1}^{n-1}x_a^2\right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{a=1}^{n-1}x_a\right)\left(\sum_{i=1}^{n-1} x_i\right)^2+\left(\sum_{a=1}^{n-1}x_a\right)\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)\\
+  &= 2\left(\sum_{i=1}^{n-1}x_i^3\right)+c\left(\sum_{i=1}^{n-1}x_i^2\right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{i=1}^{n-1} x_i\right)^2+\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)\\
+    &= 2\left(\sum_{i=1}^{n-1}x_i^3\right)+c\left(\left(\sum_{i=1}^{n-1} x_i \right)^2+\left(\sum_{1 \le i < j \le n-1} x_ix_j\right) \right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{i=1}^{n-1}x_i\right)^3+\\&2c\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{1 \le i < j  \le n-1} x_ix_j\right)\\
+        &= 2\left(\sum_{i=1}^{n-1}x_i^3\right)+c\left(\sum_{i=1}^{n-1} x_i \right)^3+c\left(\sum_{1 \le i < j \le n-1} x_ix_j\right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{i=1}^{n-1}x_i\right)^3+\\&2c\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{1 \le i < j  \le n-1} x_ix_j\right)\\
+        &=(c^2+2)\left(\sum_{i=1}^{n-1} x_i\right)^3\\
+\end{align*}
+
+We see that $\sum_{a=1}^{n-1} f_a=  (c^2+2)\left(\sum_{i=1}^{n-1} x_i \right)^3$.
+
+Therefore if $f_1(x) = \dots = f_{n-1}(x)=0$, we see that $\sum_{i=1}^{n-1} x_i = 0$.
 Modulo this new relation, we see that $f_a=x_a\left(-x_a^2+\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$.

### 2015-04-07 proofs.tex
fixed dunkl operators

@@
 \newcommand{\m}[1]{\left|#1\right|}
+\newcommand{\Res}{\operatorname{Res}}
 \newcommand{\p}[1]{\left(#1\right)}
@@
 
+\section{$p \mid n$, $n-1$ case full argument}
+
+We assume $p > 2$ since $p=2$ has been fully characterized.
+
+\subsection{Generators}
+
+Let $x_0,\dots,x_{n-2}$ be a basis for the $n-1$ dimensional representation of $S_n$ derived from the standard representation with basis $e_0,\dots,e_{n-1}$ by taking the quotient by $e_0+\dots+e_{n-1}$; assume $x_i$ is the representative for $e_i$ in the quotient.
+We see that we can in fact say that the representation is spanned by $x_0,\dots,x_{n-1}$ with the relation $x_0+\dots+x_{n-1}=0$, or $x_{n-1}=-x_0-\dots-x_{n-2}$.
+Let $s_{ij}$ be the transposition of $i$ and $j$ for $0 \le i < j \le n-1$.
+For $0 \le i < j \le n-1$ the relevant eigenvectors are $x_i-x_j$.
+
+We let $g=\prod_{j=0}^{n-1} (1-x_jz)$, where $z$ is another variable.
+
+Let $f_a$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $f_a=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.
+We will show that the coefficient of $z^p$ in $f_a$ is killed by the Dunkl operators for all $a$.
+Since the Dunkl operators consist of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, linear operations, and the action of the symmetric group on the $x_i$, we see that we can just apply the Dunkl operators to the $f_a$ and check that the coefficient of $z^p$ in the resulting formal power series is $0$.
+
+Let $y_0,\dots,y_{n-1}$ be a basis for the dual of the standard representation of $S_n$.
+Then the dual of the $(n-1)$-dimensional quotient we are considering is spanned by $y_i-y_0$ for $0 < i \le n-1$.
+Therefore if $D_i$ is the Dunkl operator corresponding to $y_i$ acting on the standard representation of $S_n$, we see that the Dunkl operators on our quotient representation are $D_i-D_0$ for $0 < i \le n-1$
+
+Because of the symmetry in the $f_a$, we need only consider the action of the Dunkl operators on $f_0$. Then again by symmetry we need only consider the action of $D_1-D_0$ on $f_0$.
+
+We also note that we can add powers of $z$ greater than $z^p$ at any stage of taking the Dunkl operator, since those will not affect the final result.
+
+\subsection{Dunkl operators}
+
+We note $z^2 \mid g-1$ since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$.
+Therefore when $p > 2$ we see that $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$.
+Therefore we can add multiples of $(g-1)^{p-1}$ at any stage, since even when multipled by other power series it cannot contribute anything to the coefficient of $z^p$.
+
+Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$ for all $0 \le i < n-1$.
+Let $F=f_0(1-x_1z)=\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+Note that $F$ is symmetric.
+Then we see that for all $0 \le i < n-1$:
+
+\begin{align*}
+\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
+&\text{(We see that for }k=1,\dots,p-1\text{ we have }\binom{c-1}{k}+\binom{c-1}{k-1}=\binom{c}{k},\text{ that }\binom{c-1}{0}=\binom{c}{0}\\&\text{ as a polynomial, and that we can add a multiple of }(g-1)^{p-1}).\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F\\
+\end{align*}
+
+We also see that:
+
+\begin{align*}
+\frac{\partial f_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
+&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F\\
+&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)f_0\\
+\end{align*}
+
+and that:
+
+\begin{align*}
+\frac{\partial f_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+&=\frac{z}{(1-x_0z)^2}F+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
+&=\frac{z}{1-x_0z}f_0+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F\\
+&=\frac{z}{1-x_0z}f_0+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)f_0\\
+&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)f_0\\
+\end{align*}
+
+We note that $f_0$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$.
+
+\begin{align*}
+\frac{1-s_{0i}}{x_0-x_i}(f_0)&=\frac{1}{x_0-x_i}\left(\frac{F}{1-x_0z}-\frac{F}{1-x_iz}\right)\\
+&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F\\
+&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F\\
+&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F\\
+&=\frac{z}{(1-x_iz)(1-x_0z)}F\\
+&=\frac{z}{1-x_iz}f_0\\
+\end{align*}
+
+We recall that we need only consider the action of $D_1-D_0$ on $f_0$.
+We consider $D_0f_0, D_1f_0$ separately first.
+We see that $D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$ since $f_0$ is invariant under $s_{ij}$ where $0 < i,j$.
+
+\begin{align*}
+D_0f_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(f_0)\\
+&=\frac{\partial f_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(f_0)\\
+&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)f_0-\sum_{j > 0} \frac{zc}{1-x_jz}f_0\\
+\end{align*}
+\begin{align*}
+D_1f_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(f_0)\\
+&=\frac{\partial f_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(f_0)\\
+&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)f_0+\frac{zc}{1-x_1z}f_0\\
+&=\frac{zc}{1-x_{n-1}z}f_0\\
+\end{align*}
+
+It is then easy to see that $(D_1-D_0)(f_0)=\frac{z(c-1)}{1-x_0z}f_0+\sum_{j>0} \frac{zc}{1-x_jz}f_0$.
+
+In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial f_0}{\partial z}$.
+
+We see easily that $\frac{\partial g}{\partial z} = g \sum_j \frac{-x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$:
+
+\begin{align*}
+\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
+&\text{Note that above we showed that }\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g=\left(\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\&\text{ up to the addition of multiples of }z^{p+1}.\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F
+\end{align*}
+
+From this it follows that:
+
+\begin{align*}
+\frac{\partial f_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F}{1-x_0z}\right)\\
+&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F\\
+&=\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\frac{x_0}{(1-x_0z)^2} F\\
+&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)f_0+\frac{x_0}{1-x_0z} f_0\\
+\end{align*}
+
+We now again consider $(D_1-D_0)(f_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $f_1$ since that is $0$ in characteristic $p$.
+
+\begin{align*}
+(D_1-D_0)(f_0)&=\frac{z(c-1)}{1-x_0z}f_0+\sum_{j>0} \frac{zc}{1-x_jz}f_0\\
+&=-\frac{z}{1-x_0z}f_0+\sum_{j} \frac{zc}{1-x_jz}f_0\\
+&=-\frac{z}{1-x_0z}f_0++\left(\sum_{j} \frac{zc}{1-x_jz}f_0\right)-nzcf_0\\
+&=-zf_0+zf_0-\frac{z}{1-x_0z}f_0+\left(\sum_{j} -zcf_0+\frac{zc}{1-x_jz}f_0\right)\\
+&=-zf_0+\frac{z-x_0z^2}{1-x_0z}f_0-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}f_0+\frac{zc}{1-x_jz}f_0\right)\\
+&=-zf_0+\frac{-x_0z^2}{1-x_0z}f_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}f_0\right)\\
+&=-zf_0-z^2\left(\frac{x_0}{1-x_0z}f_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}f_0\right)\right)\\
+&=-zf_0-z^2\frac{\partial f_0}{\partial z}
+\end{align*}
+
+Let $b$ be the coefficient of $z^{p-1}$ in $f_0$.
+We see that the coefficient of $z^p$ in $-zf_0$ is $-b$.
+Then the coefficient of $z^{p-2}$ in $\frac{\partial f_0}{\partial z}$ is $(p-1)b=-b$, so the coefficient of $z^p$ in $-z^2\frac{\partial f_0}{\partial z}$ is $b$.
+Therefore the coefficient of $z^p$ in $-zf_0-z^2\frac{\partial f_0}{\partial z}$ is $-b+b=0$, so the coefficient of $z^p$ in $(D_1-D_0)(f_0)$ is $0$.
+Then if $B$ is the coefficient of $z^p$ in $f_0$, it is clear that $(D_1-D_0)(B)=0$ as desired.
+By the symmetry of the $f_a$, this is the only Dunkl operator we need consider; it is clear that the coefficients of $z^p$ in all the $f_a$ are killed by the Dunkl operators.
+
+\subsection{Complete intersection}
+
+Let $B_a$ be the coefficient of $z^p$ in $f_a$.
+We see that $f_a=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+It is then clear that $B_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since the coefficient of $z^k$ for any $k$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands).
+
+We also note that:
+
+\begin{align*}
+\sum_{a=0}^{n-1} f_a&=\left(\sum_a \frac{1}{1-x_az}\right)F\\
+&=\left(\sum_a \frac{1}{1-x_az}\right)F-nF\\
+&=\left(\sum_a\frac{x_az-1}{1-x_az}+ \frac{1}{1-x_az}\right)F\\
+&=\left(\frac{-x_az}{1-x_az}\right)F\\
+&=z\frac{\partial F}{\partial z}
+\end{align*}
+
+Then the coefficient of $z^p$ in this sum is the coefficient of $z^{p-1}$ in $\frac{\partial F}{\partial z}$, which is $p$ times the coefficient of $z^p$ in $F$, which must be $0$ since we are in characteristic $p$.
+The coefficient of $z^p$ in this sum is also $\sum_a B_a$, so we have $\sum_a B_a=0$.
+
 \end{document}

### 2015-04-10 proofs.tex
complete intersection

@@
 
+We note that we can write the $B_a$ as polynomials in $c$ with coefficients from the polynomial ring $\mathbb{F}_p[x_i]$.
+Recall that $B_a$ is the coefficient of $z^p$ in $\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+Then as polynomials it is clear that $c \mid \binom{c}{k}$ for all $k > 0$; therefore when trying to find the constant term of the coefficient of $z^p$, we can ignore the terms with $k > 0$ in the second multiplicand.
+The term for $k=0$ is just $1$; it is then clear that the constant term (the coefficient of $c^0$) of the coefficient of $z^p$ is $x_a^p$.
+
+If $\sum_{a=0}^{n-2} \lambda_aB_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$.
+Then the constant term of this sum is $\sum_{a=0}^{n-2} C(\lambda_a)x_a^p$ where $C(\lambda_a)$ represents the constant term of $\lambda_a$.
+Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $C(\lambda_a)$ must be $0$ for $a=0,\dots,n-2$.
+Then we can factor out $c$ from all of the $\lambda_a$, since if $\sum_{a=0}^{n-2} \lambda_aB_a=0$, we have $\sum_{a=0}^{n-2}\frac{1}{c}\lambda_aB_a=0$ as well.
+We can then apply the same logic again to see that the coefficient of $c$ in all of the $\lambda_a$ is $0$.
+If $e=\max_a\deg \lambda_a$, we need only apply this logic $e$ times to show that the coefficients of $e=1,c,\dots,c^e$ in all of the $\lambda_a$ are $0$, meaning all of the $\lambda_a$ are $0$.
+
+Therefore $B_a$ for $a=0,\dots,n-2$ are linearly independent, and $B_{n-1}=-\sum_{a=0}^{n-2} B_a$. 
+Then we need only consider $B_a$ for $a=0,\dots,n-2$, since $B_{n-1}$ is linearly dependent on the others.
+We will show these generate a complete intersection.
+Let $I$ be the ideal generated by $B_a$ for $a=0,\dots,n-2$.
+We see that if $J$ is the kernel of the $\beta$ form, then the since the $B_a$ are killed by the Dunkl operators, we have $I \subseteq J$.
+
+We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $\mathbb{F}_p$.
+Then we can consider $B_a$ as a function on these vectors $x$ for all $a$.
+For any rational function $u( c)$, we let $u(c )x=\langle u(c )x_0,\dots, u(c )x_{n-2}\rangle$.
+
+To show that $A/I$ is a complete intersection (where $A=k[x_0,\dots,x_{n-2}]$, we will show that if $B_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$.
+
+We showed that for all $a$, $B_a$ is a homogeneous polynomial in the $x_i$ of degree $p$.
+Then for any rational function $u(c )$, we see that $B_a(u(c )x)=u(c )^pB_a(x)$.
+In particular, if $B_a(x)=0$, then for any rational function $u(c )$ we have $B_a(u(c )x)=0$ as well.
+Therefore if $B_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial for all $i=0,\dots,n-2$ (a least common denominator), we see that since $B_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$.
+
+For any $a$, we can then consider $B_a(x)$ to be a polynomial in $c$.
+Since this is zero, we can in particular consider the constant term, which must be $0$.
+Recall that the constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power.
+If this is zero, then the constant term of $x_a$ must be $0$.
+
+Then if $B_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$.
+Since the $x_a$ are polynomials in $c$, we can divide through by $c$ again (since $B_a(x)=0$ means $B_a(1/c\cdot x)=0$) and apply the same logic to show that the coefficient of $c$ in all of the $x_a$ must be $0$.
+Let $d=\max_a \deg x_a$.
+Then we can just apply this logic $d$ times to show that the coefficients of $1,c,\dots,c^d$ in all of the $x_a$ must be $0$, meaning all of the $x_a$ are $0$ as desired.
+
+Therefore $B_0(x) = \dots = B_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection; it then must have Hilbet polynomial $h_{A/I}(t)=(t^p+t^{p-1}+\dots+t+1)^{n-1}$.
+
+By Proposition 3.4 in http://arxiv.org/abs/1107.0504, we see that the Hilbert polynomial of $A/J$ is $(t^p+t^{p-1}+\dots+t+1)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
+Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal.
+
 \end{document}

### 2015-04-27 formalwriteup.tex
beginnings of writeup

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb,amsthm}
\usepackage{color}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{verbatim}

\numberwithin{equation}{section}
\newtheorem{theorem}[equation]{Theorem}
\newtheorem{proposition}[equation]{Proposition}
\newtheorem{lemma}[equation]{Lemma}
\newtheorem{corollary}[equation]{Corollary}
\newtheorem{conjecture}[equation]{Conjecture}
\newtheorem{problem}[equation]{Problem}
\newtheorem{remark}[equation]{Remark}
\newtheorem{definition}[equation]{Definition}
\newenvironment{defn}[1][]{%
    \begin{definition}[#1]\pushQED{\qed}}{\popQED \end{definition}}
\parindent=0in
\parskip=0.15in

\newcommand{\xx}[1]{\textcolor{blue}{#1}}
\newcommand{\zb}{\overline{z}}
\newcommand{\cc}[1]{\overline{#1}}
\newcommand{\m}[1]{\left|#1\right|}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\p}[1]{\left(#1\right)}
\newcommand{\cis}{\text{cis}\,}
\newcommand{\sgn}{\text{sgn}}
\newcommand{\D}{\triangle}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\f}[1]{\sum_{n=-\infty}^\infty #1_ne^{inx}}
\newcommand{\fn}[1]{\sum_{n=-\infty}^\infty #1e^{inx}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\mm}[1]{\m{\m{#1}}}
\newcommand{\ang}[1]{\left\langle #1 \right\rangle}

\begin{document}

%\section{Outline of write-up}

%Define all notation - $\Sigma_n, x \in \mathfrak{h}^*, y \in \mathfrak{h}, D_y, \tau, M_c(\tau), J, A=k[x_1,\dots,x_n]$, etc.

%Define $\mathfrak{h}$ as the span of $y_i-y_j$ for $i \ne j$; define $\mathfrak{h}^*$ as the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$.

%Define Hilbert series. Set stage - $p \mid n$. We are using $(n-1)$-dimensional representation. Note $p>2$ but $p=2$ characterized already (though for $n$-dimensional representation).

We let $g=\prod_{j=0}^{n-1} (1-x_jz)$. Let $F_a$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$. We note that the coefficients of this power series lie in $A$; we will get the generators of the ideal $J$ from these coefficients.

\begin{proposition} Let $f_a$ be the coefficient of $z^p$ in the power series $F_a$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
\end{proposition}

\begin{proof}
Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations. We see that this means we can apply the Dunkl operators to $F_a$ and check that the coefficient of $z^p$ in the result is $0$ to show that the Dunkl operators annihilate the $f_a$.

We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$. Therefore we need only consider the action of the Dunkl operators on $F_0$. We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; if the Dunkl operator corresponding to $y_j$ is $D_j$, then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators.

We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$. In particular, we note that since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$, we have $z^2 \mid g-1$. Then since $p>2$, we note that $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$. Therefore we can add multiples of $(g-1)^{p-1}$ when taking the Dunkl operator's action on $F_0$, since even when multipled by another power series it cannot contribute anything to the coefficient of $z^p$. We also note that we can add $n$ times any multiple of $F_0$ since $n \equiv 0 \bmod p$.

Using the allowed manipulations and the fact that $x_{n-1}=-x_0+\dots-x_{n-2}$, we see that $\frac{\partial F_0}{\partial x_1}=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0$ and $\frac{\partial F_0}{\partial x_0}=\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0$ up to the $z^p$ coefficient, which is all that we need.

We note that when $0 < i,j$ we have $\frac{1-s_{ij}}{x_i-x_j}\left(F_0\right)=0$. We also see that for $0 < i \le n-1$ we have $\frac{1-s_{ij}}{x_i-x_j}\left(F_0\right)=\frac{z}{1-x_iz}F_0$.

We also consider $\frac{\partial F_0}{\partial z}$; up to the addition of some multiple of $(g-1)^{p-1}$, this is equal to $\frac{x_0}{1-x_0z}F_0-\sum_{j \ge 0} \frac{-x_jc}{1-x_jz}F_0$.

Then we see that:

\begin{align*}
(D_1-D_0)(F_0)&=\frac{\partial F_0}{\partial x_1}-\frac{\partial F_0}{\partial x_0}-c\frac{1-s_{01}}{x_1-x_0}(F_0)+c\sum_{j>0}\frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0-\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0+\frac{zc}{1-x_1z}F_0+\sum_{j>0}\frac{zc}{1-x_jz}F_0\\
&=\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0}\frac{zc}{1-x_jz}F_0\\
&=-\frac{z}{1-x_0z}f_0+\sum_{j} \frac{zc}{1-x_jz}f_0\\
&=-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{zc}{1-x_jz}f_0\right)-nzcf_0\\
&=-zf_0+\frac{z-x_0z^2}{1-x_0z}f_0-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}f_0+\frac{zc}{1-x_jz}f_0\right)\\
&=-zf_0+\frac{-x_0z^2}{1-x_0z}f_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}f_0\right)\\
&=-zf_0-z^2\frac{\partial f_0}{\partial z}
\end{align*}

Then if $b$ is the coefficient of $z^{p-1}$ in $f_0$, we see that the coefficient of $z^p$ in $-zf_0$ is $-b$, and the coefficient of $z^p$ in $-z^2\frac{\partial f_0}{\partial z}$ is $-(p-1)b=b$. Therefore the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is $-b+b=0$; this means that $(D_1-D_0)(f_0)=0$.

Then as we discussed above, the symmetry of the $f_a$ means that all the $f_a$ are annihilated by the Dunkl operators, as desired.

\end{proof}

\begin{proposition} The $f_a$ for $a=0,\dots,n-2$ are linearly independent, with $f_{n-1}=-\sum_{a=0}^{n-2} f_a$. 
\end{proposition}

\begin{proof} 
We recall that $F_a=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since the coefficient of $z^k$ for any $k$ in $F_a$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).

We also note that:

\begin{align*}
\sum_{a=0}^{n-1} F_a&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)-n\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_a\frac{x_az-1}{1-x_az}+ \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\frac{-x_az}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\frac{z}{c}\frac{\partial g}{\partial z}\left(\sum_{k=0}^{p-1} c\binom{c}{k} (g-1)^k\right)\\
&=z\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)
\end{align*}

This equality only holds up to the $z^p$ coefficient, since we implicitly add a multiple of $(g-1)^{p-1}$ in the last step.

Then the coefficient of $z^p$ in this sum is the coefficient of $z^{p-1}$ in $\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$, which is $p$ times the coefficient of $z^p$ in $\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k$, which must be $0$ since we are in characteristic $p$. The coefficient of $z^p$ in this sum is also $\sum_{a=0}^{n-1} f_a$, so we have $\sum_{a=0}^{n-1} f_a=0$, and $f_{n-1}=-\sum_{a=0}^{n-2} f_a$.

We note that we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $\mathbb{F}_p[x_i]$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$. Recall that $f_a$ is the coefficient of $z^p$ in $F_a=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. Then as polynomials it is clear that $c \mid \binom{c}{k}$ for all $k > 0$; therefore when trying to find the constant term of the coefficient of $z^p$, we can ignore the terms with $k > 0$ in the second multiplicand. The term for $k=0$ is just $1$; it is then clear that the constant term (the coefficient of $c^0$) of $f_a$ is $x_a^p$.

If $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$. Then the constant term of this sum is $\sum_{a=0}^{n-2} C(\lambda_a)x_a^p$ where $C(\lambda_a)$ represents the constant term of $\lambda_a$. Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $C(\lambda_a)$ must be $0$ for $a=0,\dots,n-2$. Then we can factor out $c$ from all of the $\lambda_a$, since if $\sum_{a=0}^{n-2} \lambda_af_a=0$, we have $\sum_{a=0}^{n-2}\frac{1}{c}\lambda_af_a=0$ as well; we have that $\frac{1}{c}\lambda_a$ is a polynomial since the constant terms in all the $\lambda_a$ are $0$. Then we see that by the same logic, the constant terms of $\lambda_a/c$ for all $a$ are 0, so the coefficient of $c$ in all of the $\lambda_a$ is $0$. This means that $c^2 \mid \lambda_a$ for all $a$, so we can perform the same calculation again to get that the coefficient of $c^2$ is $0$ and so forth. If $e=\max_a\deg \lambda_a$, we need only apply this logic $e$ times to show that the coefficients of $e=1,c,\dots,c^e$ in all of the $\lambda_a$ are $0$, meaning all of the $\lambda_a$ are $0$.

Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$ means all the $\lambda_a$ are $0$, we see that $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.

\end{proof}

let $I$ the ideal generated by $f_a$

\begin{proposition} $A/I$ is a complete intersection. 
\end{proposition}

\begin{theorem} The $f_a$ generate the ideal $J$; $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. 
\end{theorem}

\end{document}

### 2015-04-27 formalwriteup.tex
full (not final) draft

@@
 \newcommand{\p}[1]{\left(#1\right)}
-\newcommand{\cis}{\text{cis}\,}
-\newcommand{\sgn}{\text{sgn}}
+\newcommand{\rank}{\operatorname{rank}}
+\newcommand{\sgn}{\operatorname{sgn}}
 \newcommand{\D}{\triangle}
@@
 \newcommand{\ang}[1]{\left\langle #1 \right\rangle}
+\newcommand{\h}{\mathfrak{h}}
+\newcommand{\GL}{{\rm GL}}
+\newcommand{\HH}{{\rm H}}
+\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{{\tt arXiv:#1}}}
+\newcommand{\Sym}{\operatorname{Sym}}
 
@@
 
+\section{Introduction and Definitions}
+
+In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$.
+
+%motivation, history, etc.
+
+Given a vector space $\h$, an element $s \in \GL(\h)$ is an {\it reflection} if it has finite order and $\rank(1-s)=1$.
+A finite subgroup of $\GL(\h)$ that is generated by reflections is a {\it reflection group}.
+In particular the symmetric group $\Sigma_n$ in $n$ variables is a reflection group (the reflections are the transpositions).
+
+Given a reflection group $G \subset \GL(\h)$ and a vector space $\h$ over a field $k$, we let $\mathcal{S}$ be the set of reflections in $G$.
+For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.
+We choose $\hbar \in k$ a number and $c: \mathcal{S} \to k$ a function so that $c(s)=c(s')$ whenever $s,s'$ are conjugate.
+Let $\overline{c}$ be the function defined by $\overline{c}(s)=c(s^{-1})$.
+Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$.
+Then we define the {\it rational Cherednik algebra $\HH_{\hbar,c}(G,\h)$} as the quotient of $k[G] \ltimes T(\h \oplus \h^*)$ by the following relations for all $x,x' \in \h^*, y,y' \in \h$:
+
+\begin{align*}
+[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c(s)\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s.
+\end{align*}
+
+We can give $\HH_{\hbar,c}(G,\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
+We get the PBW-type decomposition $\HH_{\hbar,c}(G,\h)=\Sym(\h) \otimes_k k[G] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).
+
+In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(G,\h)\simeq \HH_{\alpha\hbar,\alpha c}(G,\h)$. Then we can assume $\hbar=0$ or $\hbar = 1$.
+
+Let $\tau$ be a representation of $G$.
+The {\it Verma module} $M_{\hbar,c}(G,\h,\tau)$ is defined as $\HH_{\hbar,c}(G,\h) \otimes_{k[G] \ltimes \Sym(\h)} \tau$.
+Using the PBW decomposition of the Cherednik algebra, we see that $M_{\hbar,c}(G,\h,\tau)=\Sym(\h^*) \otimes_k \tau$ as a $k$-vector space; we can give this a $\mathbb{Z}$-grading in an obvious way.
+
+As described in section 2.5 of \cite{BC1}, $M_{\hbar,c}(G,\h,\tau)$ has a unique maximal graded proper submodule $J_{\hbar,c}(G,\h,\tau)$ which can be realized as the kernel of the contravariant form $\beta_c: M_{\hbar,c}(G,\h,\tau) \times M_{\hbar,\overline{c}}(G,\h^*,\tau^*) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in M_{\hbar,c}(G,\h,\tau), g \in  M_{\hbar,\overline{c}}(G,\h^*,\tau^*), v \in \tau, w \in \tau^*$:
+
+\begin{align*}
+\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(v,w) = \langle v,w\rangle.
+\end{align*}
+
+The quotient $L_{\hbar,c}(G,\h,\tau) = M_{\hbar,c}(G,\h,\tau)/J_{\hbar,c}(G,\h,\tau)$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(G,\h)$.
+
+To understand the action of $\HH_{\hbar,c}(G,\h)$ on $M_{\hbar,c}(G,\h,\tau)$, we can use the PBW decompositions.
+The action of $\Sym(\h^*)$ on $M_{\hbar,c}(G,\h,\tau)=\Sym(h^*)\otimes_k \tau$ is by left multiplication; $k[G]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
+For $y \in \h$, the Dunkl operator $D_y$ acts on $M_{\hbar,c}(G,\h,\tau)$ by:
+
+\begin{align*}
+D_y(f \otimes v) = \hbar \partial_y f \otimes v - \sum_{s \in \mathcal{S}} c(s) \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f \otimes s.v.
+\end{align*}
+
+Throughout the paper we let $G=\Sigma_n$ and $\tau$ the trivial representation.
+There is only one conjugacy class of reflections in $\Sigma_n$, so $c$ is an element of $k$ for our purposes.
+We call $c$ {\it generic} if we do not specify a value for $c$.
+We will be concerned with the case $\hbar=1$ and $c$ generic in this paper.
+(Note that in particular this case means that $\overline{c}=c$, since there is only one conjugacy class of reflections.) The characteristic of the field $k$ is $p>0$.
+We let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $\Sigma_n$ acts by permuting indices.
+Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.
+
+In this case, since $\tau$ is trivial, $M_{\hbar,c}(G,\h,\tau)$ is a polynomial ring $k[x_0,\dots,x_{n-2}]$; we call this polynomial ring $A$.
+Similarly we refer to $J_{\hbar,c}(G,\h,\tau)$ as $J$, which is an ideal in $A$, and $A/J$ is the irreducible representation of the Cherednik algebra we desire to find.
+Because of the definition of the contravariant form $\beta_c$, showing that an element $f$ of $A$ is in the kernel of $\beta_c$ is equivalent to showing that the Dunkl operators corresponding to the basis elements of $\h$ annihilate $f$.
+If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.
+
+For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
+
+\section{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic $p \mid n$}
+
+In this paper we consider the case where the characteristic $p$ of $k$ divides $n$.
+This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.
+In that case the generators of the ideal $J$ were the residues of some function in $z$.
+To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$.
+
 We let $g=\prod_{j=0}^{n-1} (1-x_jz)$.
 Let $F_a$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.
-We note that the coefficients of this power series lie in $A$; we will get the generators of the ideal $J$ from these coefficients.
 
@@
 
-\begin{proposition} The $f_a$ for $a=0,\dots,n-2$ are linearly independent, with $f_{n-1}=-\sum_{a=0}^{n-2} f_a$. 
+\begin{proposition} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$, with $f_{n-1}=-\sum_{a=0}^{n-2} f_a$. 
 \end{proposition}
@@
 If $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$.
-Then the constant term of this sum is $\sum_{a=0}^{n-2} C(\lambda_a)x_a^p$ where $C(\lambda_a)$ represents the constant term of $\lambda_a$.
-Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $C(\lambda_a)$ must be $0$ for $a=0,\dots,n-2$.
-Then we can factor out $c$ from all of the $\lambda_a$, since if $\sum_{a=0}^{n-2} \lambda_af_a=0$, we have $\sum_{a=0}^{n-2}\frac{1}{c}\lambda_af_a=0$ as well; we have that $\frac{1}{c}\lambda_a$ is a polynomial since the constant terms in all the $\lambda_a$ are $0$.
-Then we see that by the same logic, the constant terms of $\lambda_a/c$ for all $a$ are 0, so the coefficient of $c$ in all of the $\lambda_a$ is $0$.
-This means that $c^2 \mid \lambda_a$ for all $a$, so we can perform the same calculation again to get that the coefficient of $c^2$ is $0$ and so forth.
-If $e=\max_a\deg \lambda_a$, we need only apply this logic $e$ times to show that the coefficients of $e=1,c,\dots,c^e$ in all of the $\lambda_a$ are $0$, meaning all of the $\lambda_a$ are $0$.
+We assume that not all of the $\lambda_a$ are $0$.
+Then we can let $e$ be the smallest nonnegative integer such that there exists an $b$ with the coefficient of $c^e$ in $\lambda_b$ nonzero.
+We can divide all of the $\lambda_a$ by $c^e$, so that $\lambda_b$ for some $b$ must have nonzero constant term.
+
+The constant term of the sum is $\sum_{a=0}^{n-2} C(\lambda_a)x_a^p$ where $C(\lambda_a)$ represents the constant term of $\lambda_a$.
+Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $C(\lambda_a)$ must be $0$ for $a=0,\dots,n-2$ .
+Then in particular the constant term of $\lambda_b$ is $0$, a contradiction.
+This means that our assumption that not all of the $\lambda_a$ were $0$ is false, so $\lambda_a=0$ for all $a$.
 
@@
 
-let $I$ the ideal generated by $f_a$
+\begin{proposition} Let $I \subseteq A$ be the ideal generated by $f_a$ for $a=0,\dots,n-2$. $A/I$ is a complete intersection. 
+\end{proposition}
 
-\begin{proposition} $A/I$ is a complete intersection. 
-\end{proposition}
+\begin{proof}
+
+We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $\mathbb{F}_p$.
+Then we can consider $f_a$ as a function on these vectors $x$ for all $a$.
+For any rational function $u( c)$, we let $u(c )x=\langle u(c )x_0,\dots, u(c )x_{n-2}\rangle$.
+
+To show that $A/I$ is a complete intersection, we will show that if $f_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$, which is an equivalent condition.
+
+We showed that for all $a$, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$.
+Then for any rational function $u(c )$, we see that $f_a(u(c )x)=u(c )^pf_a(x)$.
+In particular, if $f_a(x)=0$, then for any rational function $u(c )$ we have $f_a(u(c )x)=0$ as well.
+Therefore if $f_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial for all $i=0,\dots,n-2$ (a least common denominator), we see that since $f_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$.
+We assume that not all of the $x_a$ are $0$.
+Then we can let $e$ be the smallest nonnegative integer such that there exists an $b$ with the coefficient of $c^e$ in $x_b$ nonzero.
+Then since $f_a(\frac{1}{c^e}x)=0$ and $x_a/c^e$ is still a polynomial for any $a$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero.
+
+For any $a$, we can then consider $f_a(x)$ to be a polynomial in $c$.
+Since this is zero, we can in particular consider the constant term, which must be $0$.
+Recall that the constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power.
+If this is zero, then the constant term of $x_a$ must be $0$.
+
+Then if $f_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$.
+In particular, $x_b$ has zero constant term, a contradiction.
+This means that our assumption that not all of the $x_a$ were $0$ is false, so $x_a=0$ for all $a$.
+
+Therefore $f_0(x) = \dots = f_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection.
+\end{proof}
 
@@
 
+\begin{proof} We note that $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
+It then must have Hilbet polynomial $h_{A/I}(t)=(t^p+t^{p-1}+\dots+t+1)^{n-1}$.
+Since the generators of $I$ are annihilated by the Dunkl operators, we must have $I \subseteq J$.
+
+By Proposition 3.4 in \cite{BC1}, we see that the Hilbert polynomial of $A/J$ is $(t^p+t^{p-1}+\dots+t+1)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
+Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal $J$.
+
+\end{proof}
+
+\begin{thebibliography}{2}
+
+\setlength{\itemsep}{-1mm}
+\small
+
+\bibitem{BC1} Martina Balagovi\'c, Harrison Chen, Representations of rational Cherednik algebras in positive characteristic, {\it J.
+Pure Appl.
+Algebra} {\bf 217} (2013), no.~4, 716--740, \arxiv{1107.0504v2}.
+
+\bibitem{CE} Tatyana Chmutova, Pavel Etingof, On some representations of the rational Cherednik algebra, {\it Representation Theory of the American Mathematical Society} {\bf 7.24} (2003), 641--650, \arxiv{0303194v2}
+
+\bibitem{DS} Sheela Devadas, Steven V.
+Sam, Representations of rational Cherednik algebras of G(m,r,n) in positive characteristic, {\it Journal of Commutative Algebra} {\bf 6.4} (2014), 525--559, \arxiv{1304.0856v2}
+
+\bibitem{EM} Pavel Etingof, Xiaoguang Ma, Lecture notes on Cherednik algebras, \arxiv{1001.0432v4}.
+
+\bibitem{L} Carl Lian, Representations of Cherednik algebras associated to symmetric and dihedral groups in positive characteristic, \arxiv{1207.0182v1}.
+
+\end{thebibliography}
+
 \end{document}

### 2015-04-27 formalwriteup.tex
some math edits

@@
 Let $\overline{c}$ be the function defined by $\overline{c}(s)=c(s^{-1})$.
+
 Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$.
 Then we define the {\it rational Cherednik algebra $\HH_{\hbar,c}(G,\h)$} as the quotient of $k[G] \ltimes T(\h \oplus \h^*)$ by the following relations for all $x,x' \in \h^*, y,y' \in \h$:
-
 \begin{align*}
@@
 \end{align*}
-
 We can give $\HH_{\hbar,c}(G,\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
@@
 As described in section 2.5 of \cite{BC1}, $M_{\hbar,c}(G,\h,\tau)$ has a unique maximal graded proper submodule $J_{\hbar,c}(G,\h,\tau)$ which can be realized as the kernel of the contravariant form $\beta_c: M_{\hbar,c}(G,\h,\tau) \times M_{\hbar,\overline{c}}(G,\h^*,\tau^*) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in M_{\hbar,c}(G,\h,\tau), g \in  M_{\hbar,\overline{c}}(G,\h^*,\tau^*), v \in \tau, w \in \tau^*$:
-
 \begin{align*}
@@
 \end{align*}
-
 The quotient $L_{\hbar,c}(G,\h,\tau) = M_{\hbar,c}(G,\h,\tau)/J_{\hbar,c}(G,\h,\tau)$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(G,\h)$.
@@
 For $y \in \h$, the Dunkl operator $D_y$ acts on $M_{\hbar,c}(G,\h,\tau)$ by:
-
 \begin{align*}
@@
 \end{align*}
-
 Throughout the paper we let $G=\Sigma_n$ and $\tau$ the trivial representation.
 There is only one conjugacy class of reflections in $\Sigma_n$, so $c$ is an element of $k$ for our purposes.
-We call $c$ {\it generic} if we do not specify a value for $c$.
+We call $c$ {\it generic} if we do not specify its value.
 We will be concerned with the case $\hbar=1$ and $c$ generic in this paper.
@@
 Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.
+For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
 
@@
 
-For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
+We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
 
@@
 
-\begin{proposition} Let $f_a$ be the coefficient of $z^p$ in the power series $F_a$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
+\begin{proposition}\label{prop:ann} Let $f_a$ be the coefficient of $z^p$ in the power series $F_a$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
 \end{proposition}
@@
 Therefore we need only consider the action of the Dunkl operators on $F_0$.
-We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; if the Dunkl operator corresponding to $y_j$ is $D_j$, then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators.
+We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators.
 
@@
 
-Using the allowed manipulations and the fact that $x_{n-1}=-x_0+\dots-x_{n-2}$, we see that $\frac{\partial F_0}{\partial x_1}=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0$ and $\frac{\partial F_0}{\partial x_0}=\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0$ up to the $z^p$ coefficient, which is all that we need.
+Using the allowed manipulations and the fact that $x_{n-1}=-x_0+\dots-x_{n-2}$, we see that up to the $z^p$ coefficient,
+
+\begin{align*}
+\frac{\partial F_0}{\partial x_1}=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0, \quad \frac{\partial F_0}{\partial x_0}=\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0.
+\end{align*}
 
@@
 &=-zf_0+\frac{-x_0z^2}{1-x_0z}f_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}f_0\right)\\
-&=-zf_0-z^2\frac{\partial f_0}{\partial z}
+&=-zf_0-z^2\frac{\partial f_0}{\partial z}.
 \end{align*}
@@
 
-\begin{proposition} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$, with $f_{n-1}=-\sum_{a=0}^{n-2} f_a$. 
+\begin{proposition}\label{prop:linind} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.%, with $f_{n-1}=-\sum_{a=0}^{n-2} f_a$. 
 \end{proposition}
@@
 
-We also note that:
+%We also note that $\frac{\partial g}{\partial z} = g\left(\sum_a\frac{-x_az}{1-x_az}\right)$. Then
 
-\begin{align*}
-\sum_{a=0}^{n-1} F_a&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)-n\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\sum_a\frac{x_az-1}{1-x_az}+ \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\frac{-x_az}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\frac{z}{c}\frac{\partial g}{\partial z}\left(\sum_{k=0}^{p-1} c\binom{c}{k} (g-1)^k\right)\\
-&=z\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)
-\end{align*}
+%\begin{align*}
+%\sum_{a=0}^{n-1} F_a&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+%&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)-n\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+%&=\left(\sum_a\frac{x_az-1}{1-x_az}+ \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+%&=\left(\sum_a\frac{-x_az}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+%&=\frac{z}{cg}\frac{\partial g}{\partial z}\left(\sum_{k=0}^{p-1} c\binom{c}{k} (g-1)^k\right)\\
+%&=\frac{z}{c}\frac{\partial g}{\partial z}\left(\sum_{k=1}^{p-1} k\binom{c}{k} (g-1)^{k-1}\right)\\
+%&=\frac{z}{c}\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)
+%\end{align*}
 
-This equality only holds up to the $z^p$ coefficient, since we implicitly add a multiple of $(g-1)^{p-1}$ in the last step.
+%This equality only holds up to the $z^p$ coefficient, since we implicitly add a multiple of $(g-1)^{p-1}$ in the second-to-last step.
 
-Then the coefficient of $z^p$ in this sum is the coefficient of $z^{p-1}$ in $\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$, which is $p$ times the coefficient of $z^p$ in $\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k$, which must be $0$ since we are in characteristic $p$.
+%Then the coefficient of $z^p$ in this sum is $1/c$ times the coefficient of $z^{p-1}$ in $\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$, which is $p$ times the coefficient of $z^p$ in $\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k$, which must be $0$ since we are in characteristic $p$.
 The coefficient of $z^p$ in this sum is also $\sum_{a=0}^{n-1} f_a$, so we have $\sum_{a=0}^{n-1} f_a=0$, and $f_{n-1}=-\sum_{a=0}^{n-2} f_a$.
 
-We note that we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $\mathbb{F}_p[x_i]$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$.
+Since $c$ is generic, we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $A$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$.
 Recall that $f_a$ is the coefficient of $z^p$ in $F_a=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
@@
 We assume that not all of the $\lambda_a$ are $0$.
-Then we can let $e$ be the smallest nonnegative integer such that there exists an $b$ with the coefficient of $c^e$ in $\lambda_b$ nonzero.
+Then we can let $e$ be the smallest nonnegative integer such that there exists an index $b$ with the coefficient of $c^e$ in $\lambda_b$ nonzero.
 We can divide all of the $\lambda_a$ by $c^e$, so that $\lambda_b$ for some $b$ must have nonzero constant term.
 
-The constant term of the sum is $\sum_{a=0}^{n-2} C(\lambda_a)x_a^p$ where $C(\lambda_a)$ represents the constant term of $\lambda_a$.
-Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $C(\lambda_a)$ must be $0$ for $a=0,\dots,n-2$ .
-Then in particular the constant term of $\lambda_b$ is $0$, a contradiction.
+The constant term of the sum is $\sum_{a=0}^{n-2}\mu_ax_a^p$ where $\mu_a$ is the constant term of $\lambda_a$.
+Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $\mu_a$ must be $0$ for $a=0,\dots,n-2$ .
+Then in particular the constant term $\mu_b$ of $\lambda_b$ is $0$, a contradiction.
 This means that our assumption that not all of the $\lambda_a$ were $0$ is false, so $\lambda_a=0$ for all $a$.
@@
 
-\begin{proposition} Let $I \subseteq A$ be the ideal generated by $f_a$ for $a=0,\dots,n-2$. $A/I$ is a complete intersection. 
+\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_a$ for $a=0,\dots,n-2$. $A/I$ is a complete intersection. 
 \end{proposition}
@@
 
-We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $\mathbb{F}_p$.
+We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $k$.
 Then we can consider $f_a$ as a function on these vectors $x$ for all $a$.
@@
 We assume that not all of the $x_a$ are $0$.
-Then we can let $e$ be the smallest nonnegative integer such that there exists an $b$ with the coefficient of $c^e$ in $x_b$ nonzero.
+Then we can find the smallest nonnegative integer $e$ such that there exists an $b$ with the coefficient of $c^e$ in $x_b$ nonzero.
 Then since $f_a(\frac{1}{c^e}x)=0$ and $x_a/c^e$ is still a polynomial for any $a$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero.
@@
 Since this is zero, we can in particular consider the constant term, which must be $0$.
-Recall that the constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power.
+The constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power.
 If this is zero, then the constant term of $x_a$ must be $0$.
@@
 
-\begin{proof} We note that $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
-It then must have Hilbet polynomial $h_{A/I}(t)=(t^p+t^{p-1}+\dots+t+1)^{n-1}$.
-Since the generators of $I$ are annihilated by the Dunkl operators, we must have $I \subseteq J$.
+\begin{proof} By Propositions~\ref{prop:linind}, \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
+It then must have Hilbert series $h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+By Proposition~\ref{prop:ann}, the generators of $I$ are annihilated by the Dunkl operators, so $I \subseteq J$.
 
-By Proposition 3.4 in \cite{BC1}, we see that the Hilbert polynomial of $A/J$ is $(t^p+t^{p-1}+\dots+t+1)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
+By Proposition 3.4 in \cite{BC1}, we see that the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
 Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal $J$.
@@
 \end{proof}
+
+%something about how it's a model problem
 

### 2015-04-27 formalwriteup.tex
more math edits

@@
 
+\title{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic}
+
+\author{Sheela Devadas}
+
+\date{\today}
+
 \begin{document}
 
-%\section{Outline of write-up}
+\maketitle
 
-%Define all notation - $\Sigma_n, x \in \mathfrak{h}^*, y \in \mathfrak{h}, D_y, \tau, M_c(\tau), J, A=k[x_1,\dots,x_n]$, etc.
-
-%Define $\mathfrak{h}$ as the span of $y_i-y_j$ for $i \ne j$; define $\mathfrak{h}^*$ as the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$.
-
-%Define Hilbert series. Set stage - $p \mid n$. We are using $(n-1)$-dimensional representation. Note $p>2$ but $p=2$ characterized already (though for $n$-dimensional representation).
+\begin{abstract}
+We study lowest-weight irreducible representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ when $p$ divides $n$, $\tau$ is trivial, $\hbar=1$, and $c$ is generic.
+We describe the generators of kernel of the contravariant bilinear form on the Verma module in terms of a formal power series that is related to the residues that generate the kernel in the characteristic $0$ case; we give a formula for the Hilbert series of the irreducible representation.
+\end{abstract}
 
@@
 This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.
-In that case the generators of the ideal $J$ were the residues of some function in $z$.
+In that case the generators of the ideal $J$ were the residues at infinity of $\frac{1}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c$ for each $a$.
 To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$.
+The formal power series would be $\frac{1}{z^{p+1}}\frac{1}{1-x_az}\prod_{j=0}^{n-1} (1-x_jz)^c$, with the corresponding generator as the coefficient of $1/z$.
+We simplify and truncate the formal power series so we can define it in positive characteristic.
 
@@
 
-We showed that for all $a$, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$.
+By Proposition~\ref{prop:linind}, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$ for all $a$.
 Then for any rational function $u(c )$, we see that $f_a(u(c )x)=u(c )^pf_a(x)$.
 In particular, if $f_a(x)=0$, then for any rational function $u(c )$ we have $f_a(u(c )x)=0$ as well.
-Therefore if $f_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial for all $i=0,\dots,n-2$ (a least common denominator), we see that since $f_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$.
+Therefore if $f_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial in $c$ for all $i=0,\dots,n-2$ (a least common denominator), we see that since $f_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$.
 We assume that not all of the $x_a$ are $0$.
 Then we can find the smallest nonnegative integer $e$ such that there exists an $b$ with the coefficient of $c^e$ in $x_b$ nonzero.
-Then since $f_a(\frac{1}{c^e}x)=0$ and $x_a/c^e$ is still a polynomial for any $a$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero.
+Then since $f_a(\frac{1}{c^e}x)=0$ and $x_i/c^e$ is still a polynomial for any $i$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero by dividing through by $c^e$.
 
@@
 
-\begin{theorem} The $f_a$ generate the ideal $J$; $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. 
+\begin{theorem}\label{thm:main} The $f_a$ generate the ideal $J$; $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. 
 \end{theorem}

### 2015-05-03 formalwriteup.tex
paper draft

@@
 
-\section{Introduction and Definitions}
+\section{Introduction}
 
@@
 
-%motivation, history, etc.
+This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic.
+Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}.
+The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type A (associated to the symmetric group $\Sigma_n$).
+In general new techniques are required to study positive characteristc as opposed to characteristic 0.
+In this paper we directly connect the characteristc 0 case to the positive characteristic case; instead of taking complex residues, we consider the coefficients of formal power series in positive characteristic.
+While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups.
 
-Given a vector space $\h$, an element $s \in \GL(\h)$ is an {\it reflection} if it has finite order and $\rank(1-s)=1$.
-A finite subgroup of $\GL(\h)$ that is generated by reflections is a {\it reflection group}.
-In particular the symmetric group $\Sigma_n$ in $n$ variables is a reflection group (the reflections are the transpositions).
-
-Given a reflection group $G \subset \GL(\h)$ and a vector space $\h$ over a field $k$, we let $\mathcal{S}$ be the set of reflections in $G$.
+Given the symmetric group $\Sigma_n$ and a representation $\h$ of $\Sigma_n$ over a field $K$, we let $\mathcal{S}$ be the set of transpositions in $\Sigma_n$.
 For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.
-We choose $\hbar \in k$ a number and $c: \mathcal{S} \to k$ a function so that $c(s)=c(s')$ whenever $s,s'$ are conjugate.
-Let $\overline{c}$ be the function defined by $\overline{c}(s)=c(s^{-1})$.
 
 Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$.
-Then we define the {\it rational Cherednik algebra $\HH_{\hbar,c}(G,\h)$} as the quotient of $k[G] \ltimes T(\h \oplus \h^*)$ by the following relations for all $x,x' \in \h^*, y,y' \in \h$:
+We choose $\hbar,c \in K$.
+Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $K[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the following relations for all $x,x' \in \h^*, y,y' \in \h$:
 \begin{align*}
-[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c(s)\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s.
+[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s.
 \end{align*}
-We can give $\HH_{\hbar,c}(G,\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
-We get the PBW-type decomposition $\HH_{\hbar,c}(G,\h)=\Sym(\h) \otimes_k k[G] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).
+We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in K[G]$.
+We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_K K[\Sigma_n] \otimes_K \Sym(\h^*)$ (\cite{EM}, section 3.2).
 
-In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(G,\h)\simeq \HH_{\alpha\hbar,\alpha c}(G,\h)$. Then we can assume $\hbar=0$ or $\hbar = 1$.
+In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$. Then we can assume $\hbar=0$ or $\hbar = 1$.
 
 Let $\tau$ be a representation of $G$.
-The {\it Verma module} $M_{\hbar,c}(G,\h,\tau)$ is defined as $\HH_{\hbar,c}(G,\h) \otimes_{k[G] \ltimes \Sym(\h)} \tau$.
-Using the PBW decomposition of the Cherednik algebra, we see that $M_{\hbar,c}(G,\h,\tau)=\Sym(\h^*) \otimes_k \tau$ as a $k$-vector space; we can give this a $\mathbb{Z}$-grading in an obvious way.
+The {\it Verma module} $M_{\hbar,c}(\h,\tau)$ is defined as $\HH_{\hbar,c}(\h) \otimes_{K[\Sigma_n] \ltimes \Sym(\h)} \tau$.
+Using the PBW decomposition of the Cherednik algebra, we see that $M_{\hbar,c}(\h,\tau)=\Sym(\h^*) \otimes_K \tau$ as a $K$-vector space; we can give this a $\mathbb{Z}$-grading in an obvious way.
+We are concerned with the case $\tau$ trivial, or the {\it polynomial representation} $\Sym(\h^*)$, which is a polynomial ring.
+We refer to the polynomial representation as $A$.
 
-As described in section 2.5 of \cite{BC1}, $M_{\hbar,c}(G,\h,\tau)$ has a unique maximal graded proper submodule $J_{\hbar,c}(G,\h,\tau)$ which can be realized as the kernel of the contravariant form $\beta_c: M_{\hbar,c}(G,\h,\tau) \times M_{\hbar,\overline{c}}(G,\h^*,\tau^*) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in M_{\hbar,c}(G,\h,\tau), g \in  M_{\hbar,\overline{c}}(G,\h^*,\tau^*), v \in \tau, w \in \tau^*$:
+As described in section 2.5 of \cite{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
 \begin{align*}
-\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(v,w) = \langle v,w\rangle.
+\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(1,1) = 1.
 \end{align*}
-The quotient $L_{\hbar,c}(G,\h,\tau) = M_{\hbar,c}(G,\h,\tau)/J_{\hbar,c}(G,\h,\tau)$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(G,\h)$.
+The quotient $A/J$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(\h)$.
+The {\it Hilbert series} $h_{A/J}(t)$ of $A/J$ is $\sum_{j=0}^\infty (\dim_k L_j)t^k$ where $L_j$ is the $j$-graded factor of $A/J$.
 
-To understand the action of $\HH_{\hbar,c}(G,\h)$ on $M_{\hbar,c}(G,\h,\tau)$, we can use the PBW decompositions.
-The action of $\Sym(\h^*)$ on $M_{\hbar,c}(G,\h,\tau)=\Sym(h^*)\otimes_k \tau$ is by left multiplication; $k[G]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
-For $y \in \h$, the Dunkl operator $D_y$ acts on $M_{\hbar,c}(G,\h,\tau)$ by:
-\begin{align*}
-D_y(f \otimes v) = \hbar \partial_y f \otimes v - \sum_{s \in \mathcal{S}} c(s) \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f \otimes s.v.
-\end{align*}
-Throughout the paper we let $G=\Sigma_n$ and $\tau$ the trivial representation.
-There is only one conjugacy class of reflections in $\Sigma_n$, so $c$ is an element of $k$ for our purposes.
  We call $c$ {\it generic} if we do not specify its value.
-We will be concerned with the case $\hbar=1$ and $c$ generic in this paper.
-(Note that in particular this case means that $\overline{c}=c$, since there is only one conjugacy class of reflections.) The characteristic of the field $k$ is $p>0$.
-We let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $\Sigma_n$ acts by permuting indices.
-Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.
-For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
+We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $K$ dividing $n$.
+We also have $\dim \h = n-1$, so $\h$ is an irreducible representation of the symmetric group.
+We state our result for this case below:
 
-In this case, since $\tau$ is trivial, $M_{\hbar,c}(G,\h,\tau)$ is a polynomial ring $k[x_0,\dots,x_{n-2}]$; we call this polynomial ring $A$.
-Similarly we refer to $J_{\hbar,c}(G,\h,\tau)$ as $J$, which is an ideal in $A$, and $A/J$ is the irreducible representation of the Cherednik algebra we desire to find.
-Because of the definition of the contravariant form $\beta_c$, showing that an element $f$ of $A$ is in the kernel of $\beta_c$ is equivalent to showing that the Dunkl operators corresponding to the basis elements of $\h$ annihilate $f$.
-If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.
+ \newtheorem*{thm:main}{Theorem \ref{thm:main}}
+\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection; it has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+$J$ is generated by the coefficients of $z^p$ in the formal power series \\
+$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$ for $a=0,\dots,n-2$. 
+\end{thm:main}
 
-We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
-
-\section{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic $p \mid n$}
-
-In this paper we consider the case where the characteristic $p$ of $k$ divides $n$.
+In this paper we consider the case where the characteristic of $K$ divides $n$.
 This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.
@@
 
+\paragraph{Acknowledgements} This project was done with the support of the Undergraduate Research Opportunities Program (UROP) at MIT.
+The author thanks Pavel Etingof and Yi Sun for supervising this project.
+The computer algebra system SAGE was used for obtaining data.
+
+ \subsection{Definitions}
+
+To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions.
+The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $K[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
+For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
+\begin{align*}
+D_y(f) = \hbar \partial_y f  - \sum_{s \in \mathcal{S}} c \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f.
+\end{align*}
+
+We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $\Sigma_n$ acts by permuting indices.
+Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.
+If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.
+
+For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
+
+The characteristic of the field $K$ is $p>0$. We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
+
+\section{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic $p \mid n$}
+
 We let $g=\prod_{j=0}^{n-1} (1-x_jz)$.
 Let $F_a$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.
+
+Because of the definition of the contravariant form $\beta_c$, showing that an element $f$ of $A$ is in the kernel of $\beta_c$ is equivalent to showing that the Dunkl operators corresponding to the basis elements of $\h$ annihilate $f$.
 
@@
 
-\begin{proposition}\label{prop:linind} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.%, with $f_{n-1}=-\sum_{a=0}^{n-2} f_a$. 
+\begin{proposition}\label{prop:linind} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.
 \end{proposition}
@@
 It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since the coefficient of $z^k$ for any $k$ in $F_a$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).
-
-%We also note that $\frac{\partial g}{\partial z} = g\left(\sum_a\frac{-x_az}{1-x_az}\right)$. Then
-
-%\begin{align*}
-%\sum_{a=0}^{n-1} F_a&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-%&=\left(\sum_a \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)-n\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-%&=\left(\sum_a\frac{x_az-1}{1-x_az}+ \frac{1}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-%&=\left(\sum_a\frac{-x_az}{1-x_az}\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-%&=\frac{z}{cg}\frac{\partial g}{\partial z}\left(\sum_{k=0}^{p-1} c\binom{c}{k} (g-1)^k\right)\\
-%&=\frac{z}{c}\frac{\partial g}{\partial z}\left(\sum_{k=1}^{p-1} k\binom{c}{k} (g-1)^{k-1}\right)\\
-%&=\frac{z}{c}\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)
-%\end{align*}
-
-%This equality only holds up to the $z^p$ coefficient, since we implicitly add a multiple of $(g-1)^{p-1}$ in the second-to-last step.
-
-%Then the coefficient of $z^p$ in this sum is $1/c$ times the coefficient of $z^{p-1}$ in $\frac{\partial }{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$, which is $p$ times the coefficient of $z^p$ in $\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k$, which must be $0$ since we are in characteristic $p$.
-The coefficient of $z^p$ in this sum is also $\sum_{a=0}^{n-1} f_a$, so we have $\sum_{a=0}^{n-1} f_a=0$, and $f_{n-1}=-\sum_{a=0}^{n-2} f_a$.
 
@@
 
-We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $k$.
+We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $K$.
 Then we can consider $f_a$ as a function on these vectors $x$ for all $a$.
@@
 
-\begin{theorem}\label{thm:main} The $f_a$ generate the ideal $J$; $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. 
+Using these propositions, we are able to prove the main theorem.
+
+\begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection; it has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+$J$ is generated by the coefficients of $z^p$ in the formal power series
+\\$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$ for $a=0,\dots,n-2$. 
 \end{theorem}
 
-\begin{proof} By Propositions~\ref{prop:linind}, \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
+\begin{proof} It suffices to show that the $f_a$ generate the ideal $J$ and that $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+
+By Propositions~\ref{prop:linind}, \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
 It then must have Hilbert series $h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
@@
 \end{proof}
-
-%something about how it's a model problem
 

### 2015-05-05 formalwriteup.tex
modified dunkl operators proposition

@@
 \newcommand{\GL}{{\rm GL}}
-\newcommand{\HH}{{\rm H}}
+\newcommand{\HH}{\mathcal{H}}
 \newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{{\tt arXiv:#1}}}
@@
 
-\title{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic}
+\title{Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$}
 
@@
 \begin{abstract}
-We study lowest-weight irreducible representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ when $p$ divides $n$, $\tau$ is trivial, $\hbar=1$, and $c$ is generic.
-We describe the generators of kernel of the contravariant bilinear form on the Verma module in terms of a formal power series that is related to the residues that generate the kernel in the characteristic $0$ case; we give a formula for the Hilbert series of the irreducible representation.
+We study the polynomial representation of the ratioal Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$.
+We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient.
+Our methods are motivated by generalizing from characteristic $0$ to characteristic $p$.
 \end{abstract}
@@
 In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$.
-
 This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic.
 Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}.
-The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type A (associated to the symmetric group $\Sigma_n$).
+The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$).
 In general new techniques are required to study positive characteristc as opposed to characteristic 0.
@@
 While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups.
+%this bit needs revisions
 
-Given the symmetric group $\Sigma_n$ and a representation $\h$ of $\Sigma_n$ over a field $K$, we let $\mathcal{S}$ be the set of transpositions in $\Sigma_n$.
+%mention previous results [BEG],[CE],[GLOR]? ask
+%deformation of DAHAs introduced by Etingof-Ginzburg in 2001
+
+\subsection{Definitions}
+
+Given the symmetric group $\Sigma_n$, we let $\mathcal{S}$ be the set of reflections in $\Sigma_n$.
+Let $\h$ be the irreducible $(n-1)$-dimensional representation of $\Sigma_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$.
 For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.
@@
 Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$.
-We choose $\hbar,c \in K$.
-Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $K[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the following relations for all $x,x' \in \h^*, y,y' \in \h$:
+We choose $\hbar,c \in k$.
+Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the relations
 \begin{align*}
-[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s.
+[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s
 \end{align*}
-We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in K[G]$.
-We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_K K[\Sigma_n] \otimes_K \Sym(\h^*)$ (\cite{EM}, section 3.2).
+ for all $x,x' \in \h^*, y,y' \in \h$.
+We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
+We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[\Sigma_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).
 
-In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$. Then we can assume $\hbar=0$ or $\hbar = 1$.
+In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$, so we restrict to $\hbar=0$ or $\hbar = 1$.
 
-Let $\tau$ be a representation of $G$.
-The {\it Verma module} $M_{\hbar,c}(\h,\tau)$ is defined as $\HH_{\hbar,c}(\h) \otimes_{K[\Sigma_n] \ltimes \Sym(\h)} \tau$.
-Using the PBW decomposition of the Cherednik algebra, we see that $M_{\hbar,c}(\h,\tau)=\Sym(\h^*) \otimes_K \tau$ as a $K$-vector space; we can give this a $\mathbb{Z}$-grading in an obvious way.
-We are concerned with the case $\tau$ trivial, or the {\it polynomial representation} $\Sym(\h^*)$, which is a polynomial ring.
-We refer to the polynomial representation as $A$.
+\subsection{Representations of rational Cherednik algebras}
 
-As described in section 2.5 of \cite{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
+We are concerned with the {\it polynomial representation} $\Sym(\h^*)$ of $\HH_{\hbar,c}$, which is a polynomial ring.
+We refer to the polynomial representation as $A$; we can give this a $\mathbb{Z}$-grading in an obvious way.
+
+As described in Section 2.5 of \cite{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
 \begin{align*}
@@
 
+\subsection{Main results}
+
  We call $c$ {\it generic} if we do not specify its value.
-We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $K$ dividing $n$.
-We also have $\dim \h = n-1$, so $\h$ is an irreducible representation of the symmetric group.
+We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$.
+We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $\Sigma_n$ of dimension $n-1$.
 We state our result for this case below:
@@
  \newtheorem*{thm:main}{Theorem \ref{thm:main}}
-\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection; it has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-$J$ is generated by the coefficients of $z^p$ in the formal power series \\
-$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$ for $a=0,\dots,n-2$. 
+\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+The maximal ideal $J$ is generated by the coefficients of $z^p$ in the formal power series \\
+$$F_a=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. 
 \end{thm:main}
+
+We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
+
+\subsection{Connection to characteristic $0$ results}
 
@@
 In that case the generators of the ideal $J$ were the residues at infinity of $\frac{1}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c$ for each $a$.
+%write as proposition
 To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$.
@@
 We simplify and truncate the formal power series so we can define it in positive characteristic.
+
+\subsection{Relation to previous work}
+
+%fill in?
 
@@
 
- \subsection{Definitions}
+ \section{The rational Cherednik algebra}
+
+ \subsection{Dunkl operators}
 
 To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions.
-The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $K[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
+The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
 For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
@@
 
-The characteristic of the field $K$ is $p>0$. We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
-
-\section{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic $p \mid n$}
+\section{Proof of the main result}
 
@@
 \begin{proof}
-Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations.
+%Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations.
 We see that this means we can apply the Dunkl operators to $F_a$ and check that the coefficient of $z^p$ in the result is $0$ to show that the Dunkl operators annihilate the $f_a$.
-
-We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$.
+%
+%We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$.
 Therefore we need only consider the action of the Dunkl operators on $F_0$.
 We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators.
-
-We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$.
+%
+%We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$.
 In particular, we note that since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$, we have $z^2 \mid g-1$.
@@
 
-Using the allowed manipulations and the fact that $x_{n-1}=-x_0+\dots-x_{n-2}$, we see that up to the $z^p$ coefficient,
+Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$ for all $0 \le i < n-1$.
+Let $F =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+Note that $F$ is symmetric and $F_a=\frac{F}{1-x_az}$ for all $a$.
+Then we see that for all $0 \le i < n-1$:
 
 \begin{align*}
-\frac{\partial F_0}{\partial x_1}=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0, \quad \frac{\partial F_0}{\partial x_0}=\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0.
+\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F\right)\\
+\end{align*}
+%\begin{align*}
+%&=V_i\frac{\partial}{\partial x_i}\left(\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\right)\\
+%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{i}^kz^k\right)\\
+%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} -k\binom{c}{k}(-1)^kx_{n-1}^{k-1}z^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-1} k\binom{c}{k}(-1)^kx_{i}^{k-1}z^k\right)\\
+%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{n-1}^{k-1}z^k\right)-V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{i}^{k-1}z^k\right)\\
+%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
+%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)(1-x_{n-1}z)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)(1-x_iz)\\
+%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{n-1}^{k+1}z^{k+2}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{i}^{k+1}z^{k+2}\right)\\
+%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k}\right)\\
+%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k}\right)\\
+%&=F\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)+\\&\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\\&\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)
+%\end{align*}
+%
+%Let $U=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$; clearly $z^p \mid U$ so all coefficients before that are $0$.
+The $z^p$ term is $\binom{c}{0}(-1)^0 $
+
+Let $G_i=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right)$.
+Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.
+
+We also see that:
+
+\begin{align*}
+\frac{\partial F_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
+&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_1}{1-x_0z}\\
+&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_1}{1-x_0z}\\
 \end{align*}
 
-We note that when $0 < i,j$ we have $\frac{1-s_{ij}}{x_i-x_j}\left(F_0\right)=0$. We also see that for $0 < i \le n-1$ we have $\frac{1-s_{ij}}{x_i-x_j}\left(F_0\right)=\frac{z}{1-x_iz}F_0$.
-
-We also consider $\frac{\partial F_0}{\partial z}$; up to the addition of some multiple of $(g-1)^{p-1}$, this is equal to $\frac{x_0}{1-x_0z}F_0-\sum_{j \ge 0} \frac{-x_jc}{1-x_jz}F_0$.
-
-Then we see that:
+and that:
 
 \begin{align*}
-(D_1-D_0)(F_0)&=\frac{\partial F_0}{\partial x_1}-\frac{\partial F_0}{\partial x_0}-c\frac{1-s_{01}}{x_1-x_0}(F_0)+c\sum_{j>0}\frac{1-s_{0j}}{x_0-x_j}(F_0)\\
-&=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0-\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0+\frac{zc}{1-x_1z}F_0+\sum_{j>0}\frac{zc}{1-x_jz}F_0\\
-&=\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0}\frac{zc}{1-x_jz}F_0\\
-&=-\frac{z}{1-x_0z}f_0+\sum_{j} \frac{zc}{1-x_jz}f_0\\
-&=-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{zc}{1-x_jz}f_0\right)-nzcf_0\\
-&=-zf_0+\frac{z-x_0z^2}{1-x_0z}f_0-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}f_0+\frac{zc}{1-x_jz}f_0\right)\\
-&=-zf_0+\frac{-x_0z^2}{1-x_0z}f_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}f_0\right)\\
-&=-zf_0-z^2\frac{\partial f_0}{\partial z}.
+\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+&=\frac{z}{(1-x_0z)^2}F+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
+&=\frac{z}{1-x_0z}F_0+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_0}{1-x_0z}\\
+&=\frac{z}{1-x_0z}F_0+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
+&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
 \end{align*}
 
-Then if $b$ is the coefficient of $z^{p-1}$ in $f_0$, we see that the coefficient of $z^p$ in $-zf_0$ is $-b$, and the coefficient of $z^p$ in $-z^2\frac{\partial f_0}{\partial z}$ is $-(p-1)b=b$.
-Therefore the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is $-b+b=0$; this means that $(D_1-D_0)(f_0)=0$.
+We note that $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$.
 
-Then as we discussed above, the symmetry of the $f_a$ means that all the $f_a$ are annihilated by the Dunkl operators, as desired.
+\begin{align*}
+\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F}{1-x_0z}-\frac{F}{1-x_iz}\right)\\
+&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F\\
+&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F\\
+&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F\\
+&=\frac{z}{(1-x_iz)(1-x_0z)}F\\
+&=\frac{z}{1-x_iz}F_0\\
+\end{align*}
 
+We recall that we need only consider the action of $D_1-D_0$ on $F_0$.
+We consider $D_0F_0, D_1F_0$ separately first.
+We see that $D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.
+
+\begin{align*}
+D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
+&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
+&=\frac{G_0}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0-\sum_{j > 0} \frac{zc}{1-x_jz}F_0\\
+\end{align*}
+\begin{align*}
+D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
+&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
+&=\frac{G_1}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{zc}{1-x_1z}F_0\\
+&=\frac{G_1}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0\\
+\end{align*}
+
+It is then easy to see that $(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0$.
+
+In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.
+
+We see easily that $\frac{\partial g}{\partial z} = g \sum_j \frac{-x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$:
+
+\begin{align*}
+\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right)
+\end{align*}
+
+Let $V=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right)$. Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$.
+
+From this it follows that:
+
+\begin{align*}
+\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F}{1-x_0z}\right)\\
+&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F\\
+&=\frac{V}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\frac{x_0}{(1-x_0z)^2} F\\
+&=\frac{V}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0+\frac{x_0}{1-x_0z} F_0\\
+\end{align*}
+
+We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$.
+
+\begin{align*}
+(D_1-D_0)(F_0)&=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
+&=\frac{G_1-G_0}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
+&=\frac{G_1-G_0}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
+&=\frac{G_1-G_0}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
+&=\frac{G_1-G_0}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
+&=\frac{G_1-G_0}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
+&=\frac{G_1-G_0}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
+&=\frac{G_1-G_0}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V}{1-x_0z}\\
+&=\frac{G_1-G_0+z^2V}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}\\
+\end{align*}
+
+We consider $V,G_1,G_0$; since $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$ and $(g-1)^{p-1}$ divides $V,G_1,G_0$, we see that for $\ell=0,1,\dots,p$, the coefficient of $z^\ell$ in $G_1-G_0+z^2V$ is $0$.
+Then in particular the coefficient of $z^p$ in $\frac{G_1-G_0+z^2V}{1-x_0z}$ is $0$, so the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is equal to the coefficient of $z^p$ in $-zF_0-z^2\frac{\partial F_0}{\partial z}$.
+
+Let $b$ be the coefficient of $z^{p-1}$ in $F_0$.
+We see that the coefficient of $z^p$ in $-zF_0$ is $-b$.
+Then the coefficient of $z^{p-2}$ in $\frac{\partial F_0}{\partial z}$ is $(p-1)b=-b$, so the coefficient of $z^p$ in $-z^2\frac{\partial F_0}{\partial z}$ is $b$.
+Therefore the coefficient of $z^p$ in $-zF_0-z^2\frac{\partial F_0}{\partial z}$ is $-b+b=0$, so the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is $0$.
+Then if $f_0$ is the coefficient of $z^p$ in $F_0$, it is clear that $(D_1-D_0)(f_0)=0$ as desired.
+By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
 \end{proof}
@@
 \begin{proof} 
-We recall that $F_a=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+%We recall that $F_a=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
 It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since the coefficient of $z^k$ for any $k$ in $F_a$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).
-
-Since $c$ is generic, we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $A$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$.
+%
+%Since $c$ is generic, we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $A$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$.
 Recall that $f_a$ is the coefficient of $z^p$ in $F_a=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
@@
 The term for $k=0$ is just $1$; it is then clear that the constant term (the coefficient of $c^0$) of $f_a$ is $x_a^p$.
-
-If $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$.
+%
+%If $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$.
 We assume that not all of the $\lambda_a$ are $0$.
@@
 We can divide all of the $\lambda_a$ by $c^e$, so that $\lambda_b$ for some $b$ must have nonzero constant term.
-
-The constant term of the sum is $\sum_{a=0}^{n-2}\mu_ax_a^p$ where $\mu_a$ is the constant term of $\lambda_a$.
+%
+%The constant term of the sum is $\sum_{a=0}^{n-2}\mu_ax_a^p$ where $\mu_a$ is the constant term of $\lambda_a$.
 Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $\mu_a$ must be $0$ for $a=0,\dots,n-2$ .
@@
 This means that our assumption that not all of the $\lambda_a$ were $0$ is false, so $\lambda_a=0$ for all $a$.
-
-Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$ means all the $\lambda_a$ are $0$, we see that $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
+%
+%Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$ means all the $\lambda_a$ are $0$, we see that $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
 
@@
 
-We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $K$.
+%We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $K$.
 Then we can consider $f_a$ as a function on these vectors $x$ for all $a$.
 For any rational function $u( c)$, we let $u(c )x=\langle u(c )x_0,\dots, u(c )x_{n-2}\rangle$.
-
-To show that $A/I$ is a complete intersection, we will show that if $f_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$, which is an equivalent condition.
-
-By Proposition~\ref{prop:linind}, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$ for all $a$.
+%
+%To show that $A/I$ is a complete intersection, we will show that if $f_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$, which is an equivalent condition. 
+%
+%By Proposition~\ref{prop:linind}, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$ for all $a$.
 Then for any rational function $u(c )$, we see that $f_a(u(c )x)=u(c )^pf_a(x)$.
@@
 Then since $f_a(\frac{1}{c^e}x)=0$ and $x_i/c^e$ is still a polynomial for any $i$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero by dividing through by $c^e$.
-
-For any $a$, we can then consider $f_a(x)$ to be a polynomial in $c$.
+%
+%For any $a$, we can then consider $f_a(x)$ to be a polynomial in $c$.
 Since this is zero, we can in particular consider the constant term, which must be $0$.
@@
 If this is zero, then the constant term of $x_a$ must be $0$.
-
-Then if $f_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$.
+%
+%Then if $f_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$.
 In particular, $x_b$ has zero constant term, a contradiction.
 This means that our assumption that not all of the $x_a$ were $0$ is false, so $x_a=0$ for all $a$.
-
-Therefore $f_0(x) = \dots = f_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection.
+%
+%Therefore $f_0(x) = \dots = f_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection.
 \end{proof}
@@
 
-\begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection; it has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-$J$ is generated by the coefficients of $z^p$ in the formal power series
-\\$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$ for $a=0,\dots,n-2$. 
-\end{theorem}
+\begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+The maximal ideal $J$ is generated by the coefficients of $z^p$ in the formal power series \\
+$$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. \end{theorem}
 

### 2015-05-07 ci.tex
draft of complete intersection

\documentclass{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{amsthm, amssymb}

\newcommand{\ZZ}{\mathbb{Z}}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lemma}[thm]{Lemma}

\begin{document}

\section{Showing $A/J$ is a complete intersection}

We work over an algebraically closed field $k$ of characteristic $p > 0$.  Fix an element $c \in k$, and define the polynomial
\[
g(z) = \prod_{i = 0}^{n - 1} \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} x_i^k z^k\right).
\]
Consider the elements 
\[
f_i = [z^p] \frac{1}{1 - x_i z} g(z)
\]
in $k[x_0, \ldots, x_{n-1}]$, where we consider $\frac{1}{1 - x_i z} g(z)$ as a formal power series in $z$ and denote the coefficient of $z^p$ in $r$ by $[z^p] r(z, x_0, \ldots, x_{n - 1})$.

\begin{lemma} \label{lem:lin-indep}
Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
\end{lemma}
\begin{proof} %this is a sketch

Assume that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$. We can consider $b_i(z)$ as power series in $z$. Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)=0$ as power series. Therefore since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$. Then in particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$. This is just the product of the $\lambda$ vector with the Vandermonde matrix for the $y_i$, which will have nonzero determinant since they are distinct. Therefore the $\lambda$ vector must be $0$.
\end{proof}

\begin{prop} 
For $c$ generic, if $x_0, \ldots, x_{n - i} \in k$ satisfy $f_i(x_0, \ldots, x_{n - 1}) = 0$ for all $i$, then $x_0 = \cdots = x_{n - 1} = 0$.
\end{prop}
\begin{proof}
Suppose that the distinct elements of $\{x_0, \ldots, x_{n - 1}\}$ are $\{y_0, \ldots, y_{r - 1}\}$ and that $y_i$ occurs with multiplicity $m_i$ so that 
\[
\sum_i m_i y_i = 0.
\]
Then we see that 
\[
g(z) = \prod_{i = 0}^{r - 1} \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i}.
\]

If $r=1$, then $g(z)= \left(\sum_{k=0}^{p-1} (-1)^k \binom{c}{k} y_0^kz^k\right)^n$ and $f_0(z)=\frac{1}{1-y_0z}\left(\sum_{k=0}^{p-1} (-1)^k \binom{c}{k} y_0^kz^k\right)^n$. We note that $[z^p]f_0(z)=\sum_{k=0}^p y_0^{p-k}[z^k]g(z)$. For $k=1,\dots,p-1$ we note that the term $[z^k]g(z)$ is a linear combination of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_1-\dots-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}^{\ell_1}\dots\binom{c}{k_s}^{\ell_s}y_0^k$ where $\ell_1,\dots,\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=k$ - this represents the product of $\ell_i$ terms $ (-1)^{k_i}\binom{c}{k_i} y_0^{k_i} z^{k_i}$.

. In particular this means that $0 < \ell_1 < p$, so $\binom{n}{\ell_1}$ is $0$ in characteristic $p$, so all of these terms are $0$. This means that $[z^p]f_0(z)=y_0^p[z^0]g(z)+[z^p]g(z)=y_0^p+[z^p]g(z)$. Note that $[z^p]g(z)$ is the sum of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}\dots\binom{c}{k_s}y_0^k$ where $\ell_1,\dots,\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=p$; this term is $0$ unless $\ell_1=p$, so $[z^p]g(z)=\binom{n}{p}(-1)^p\binom{c}{1}^py_0^p=\binom{n}{p}(-c)^py_0^p$. Therefore $[z^p]f_0(z)=\left(1+\binom{n}{p}(-c)^p\right)y_0^p$; if this is $0$ but $y_0 \ne 0$, then $1+\binom{n}{p}(-c)^p=0$; this is false since $c$ is generic. Therefore $y_0=0$. This completes the case $r=1$. We now assume $r>1$.

Define the associated function
\[
a(z) = \prod_{i = 0}^{r - 1} \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 1}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right).
\]

%my sketch goes here

Then for $i=0,\dots,r-1$ we let $a_i(z)=\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 1}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)$ so $a(z)=\prod_{i=0}^{r-1} a_i(z)$.

\begin{align*}
a_i'(z)&=\frac{\partial}{\partial z}\left(\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 1}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\right)\\
&=\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\frac{\partial}{\partial z}\left(\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 1}\right)+\\
&\;\;\;\;\;\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 1}\frac{\partial}{\partial z}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\\
&=\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)(m_i-1)\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 1}^{p - 1}k (-1)^k\binom{c}{k} y_i^k z^{k-1}\right)+\\
&\;\;\;\;\;\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 1}\left(\sum_{k = 1}^{p - 1}k (-1)^k\binom{c - 1}{k} y_i^k z^{k-1}\right)\\
&=(m_i-1)\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\left(\sum_{k = 1}^{p - 1} c(-1)^k\binom{c-1}{k-1} y_i^k z^{k-1}\right)+\\
&\;\;\;\;\;\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\left(\sum_{k = 1}^{p - 1}(c-1) (-1)^k\binom{c - 2}{k-1} y_i^k z^{k-1}\right)\\
&=(m_i-1)\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\left(\sum_{k = 0}^{p - 2} c(-1)^{k+1}\binom{c-1}{k} y_i^{k+1} z^{k}\right)+\\
&\;\;\;\;\;\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\left(\sum_{k = 0}^{p - 2}(c-1) (-1)^{k+1}\binom{c - 2}{k} y_i^{k+1} z^{k}\right)\\
&=\frac{-(m_i-1)y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\left(\sum_{k = 0}^{p - 2} c(-1)^{k}\binom{c-1}{k} y_i^{k} z^{k}\right)(1-y_iz)+\\
&\;\;\;\;\;\frac{-y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\left(\sum_{k = 0}^{p - 2}(c-1) (-1)^{k}\binom{c - 2}{k} y_i^{k} z^{k}\right)(1-y_iz)\\
&=\frac{-(m_i-1)y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\\&\left(\sum_{k = 0}^{p - 2} c(-1)^{k+1}\binom{c-1}{k} y_i^{k+1} z^{k+1}+\sum_{k = 0}^{p - 2} c(-1)^{k}\binom{c-1}{k} y_i^{k} z^{k}\right)+\\
&\;\;\;\;\;\frac{-y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\\&\left(\sum_{k = 0}^{p - 2}(c-1) (-1)^{k+1}\binom{c - 2}{k} y_i^{k+1} z^{k+1}+\sum_{k = 0}^{p - 2}(c-1) (-1)^{k}\binom{c - 2}{k} y_i^{k} z^{k}\right)\\
\end{align*}
\begin{align*}
&=\frac{-(m_i-1)y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\\&\left(\sum_{k = 1}^{p - 1} c(-1)^{k}\binom{c-1}{k-1} y_i^{k} z^{k}+\sum_{k = 0}^{p - 2} c(-1)^{k}\binom{c-1}{k} y_i^{k} z^{k}\right)+\\
&\;\;\;\;\;\frac{-y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\\&\left(\sum_{k = 1}^{p - 1}(c-1) (-1)^{k}\binom{c - 2}{k-1} y_i^{k} z^{k}+\sum_{k = 0}^{p - 2}(c-1) (-1)^{k}\binom{c - 2}{k} y_i^{k} z^{k}\right)\\
&=\frac{-(m_i-1)y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\\&\left(c(-1)^{p-1}\binom{c-1}{p-1}y_i^{p-1}z^{p-1}+\sum_{k = 0}^{p - 1} c(-1)^{k}\binom{c-1}{k} y_i^{k} z^{k}\right)+\\
&\;\;\;\;\;\frac{-y_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\\&\left(-(c-1)(-1)^{p-1}\binom{c-2}{p-1}y_i^{p-1}z^{p-1}+\sum_{k = 0}^{p - 1}(c-1) (-1)^{k}\binom{c - 1}{k} y_i^{k} z^{k}\right)\\
&=\frac{-(m_i-1)cy_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\\&\left(-(-1)^{p-1}\binom{c-1}{p-1}y_i^{p-1}z^{p-1}+\sum_{k = 0}^{p - 1} (-1)^{k}\binom{c-1}{k} y_i^{k} z^{k}\right)+\\
&\;\;\;\;\;\frac{-y_i(c-1)}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\\&\left(-(-1)^{p-1}\binom{c-2}{p-1}y_i^{p-1}z^{p-1}+\sum_{k = 0}^{p - 1} (-1)^{k}\binom{c - 1}{k} y_i^{k} z^{k}\right)\\
&=\frac{-(m_i-1)cy_i-y_i(c-1)}{1-y_iz}a_i(z)\\&+\frac{-(m_i-1)cy_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\left(-(-1)^{p-1}\binom{c-1}{p-1}y_i^{p-1}z^{p-1}\right)\\&+\frac{-y_i(c-1)}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\left(-(-1)^{p-1}\binom{c-2}{p-1}y_i^{p-1}z^{p-1}\right)\\
&=\frac{y_i(1-m_ic)}{1-y_iz}a_i(z)+v_i(z)\\
\end{align*}

where $v_i(z)=\frac{-(m_i-1)cy_i}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_i^k z^k\right)\left(-(-1)^{p-1}\binom{c-1}{p-1}y_i^{p-1}z^{p-1}\right)+\frac{-y_i(c-1)}{1-y_iz}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)^{m_i - 2}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_i^k z^k\right)\left(-(-1)^{p-1}\binom{c-2}{p-1}y_i^{p-1}z^{p-1}\right)$. Obviously $z^{p-1}$ divides this as a power series. Then $z^{p-1} \mid \sum_i v_i(z)$.  Note that since the $m_i$ are integers and $\sum m_iy_i=0$ that $\sum m_iy_i^p=0$.

Also note that $(c-1)\binom{c-2}{p-1}=\frac{(c-1)(c-2)\dots(c-2-(p-3))(c-2-(p-2))}{(p-1)!}=\frac{(c-1)(c-2)\dots(c-2-(p-3))c)}{(p-1)!}=c\binom{c-1}{p-1}$.

\begin{align*}
\sum_i [z^{p-1}]v_i(z)&=\sum_i -(m_i-1)cy_i(-1)^p\binom{c-1}{p-1}y_i^{p-1}-y_i(c-1)(-1)^p\binom{c-2}{p-1}y_i^{p-1}\\
&=\sum_i -cm_iy_i^p(-1)^p\binom{c-1}{p-1}+cy_i^p(-1)^p\binom{c-1}{p-1}-(c-1)y_i^p(-1)^p\binom{c-2}{p-1}\\
&=\sum_i cy_i^p(-1)^p\binom{c-1}{p-1}-(c-1)y_i^p(-1)^p\binom{c-2}{p-1}\\
&=\sum_i cy_i^p(-1)^p\binom{c-1}{p-1}-cy_i^p(-1)^p\binom{c-1}{p-1}\\
&=0
\end{align*}

Then

\begin{align*}
a'(z)&=\frac{\partial}{\partial z}\left(\prod_{i=0}^{r-1} a_i(z)\right)\\
&=\sum_{i=0}^{r-1} a_i'(z)\frac{a(z)}{a_i(z)}\\
&=\sum_{i=0}^{r-1} \left(\frac{y_i(1-m_ic)}{1-y_iz}a_i(z)+v_i(z)\right)\frac{a(z)}{a_i(z)}\\
&=-\sum_{i = 0}^{r - 1} \frac{(m_i c - 1)y_i}{1 - y_i z} a(z) +\sum_{i=0}^{r-1} v_i(z)\frac{a(z)}{a_i(z)}\\
\end{align*}

Recall that $a(z)/a_i(z)$ is a polynomial with constant term $1$ for all $i$ and $z^{p-1} \mid b_i(z)$ for all $i$. Therefore $[z^{p-1}]\sum_{i=0}^{r-1} b_i(z)\frac{a(z)}{a_i(z)}=[z^{p-1}]\sum_{i=0}^{r-1}b_i(z)=0$. Then we can write $\sum_{i=0}^{r-1} b_i(z)\frac{a(z)}{a_i(z)}$ as $z^pb(z)$ for some power series $b$.

%end sketch for first bullet; sketch for second bullet

We write

\begin{align*}
a(z) \prod_{j}(1 - y_j z)&= \prod_{j} \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_j^k z^k\right)^{m_j - 1}\left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_j^k z^k\right)(1-y_jz)\\
&= \prod_{j} \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_j^k z^k\right)^{m_j - 1}\left(\sum_{k = 0}^{p - 1} (-1)^{k+1}\binom{c - 1}{k} y_j^{k+1} z^{k+1}+\sum_{k = 0}^{p - 1} (-1)^k\binom{c - 1}{k} y_j^k z^k\right)\\
&= \prod_{j } \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_j^k z^k\right)^{m_j - 1}\left((-1)^{p}\binom{c - 1}{p-1} y_j^{p} z^{p}+\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_j^k z^k\right)\\
&= g(z)+\prod_{j } \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_j^k z^k\right)^{m_j - 1}\left((-1)^{p}\binom{c - 1}{p-1} y_j^{p} z^{p}\right)\\
\end{align*}

Then let $u(z)=\prod_{j } \left(\sum_{k = 0}^{p - 1} (-1)^k\binom{c}{k} y_j^k z^k\right)^{m_j - 1}\left((-1)^{p}\binom{c - 1}{p-1} y_j^{p} z^{p}\right)$. Note that $z^{pr} \mid u(z)$.

%r=1???

Otherwise, we see that for all $i$, $a(z) \prod_{j \neq i}(1 - y_j z) = \frac{1}{1-y_iz}g(z)+\frac{u(z)}{1-y_iz}$. Then since $u(z)$ is divisible by $z^{pr}$, $[z^p]\frac{u(z)}{1-y_iz}=0$. Therefore $[z^p] a(z) \prod_{j \neq i} (1 - y_j z) = [z^p] \frac{1}{1 - y_i z} g(z) = [z^p]f_0(z)=0$.

We write
%my sketch ends here

We claim that $a(z)$ satisfies
\begin{itemize}

\item $a'(z) = -\sum_{i = 0}^{r - 1} \frac{(m_i c - 1)y_i}{1 - y_i z} a(z) + z^p b(z)$ for some polynomial $b(z)$; %note: b(z) is actually a power series

\item for any $i$, we have
\[
[z^p] a(z) \prod_{j \neq i} (1 - y_j z) = [z^p] \frac{1}{1 - y_i z} g(z) = 0.
\]
\end{itemize}
This implies that for any $\lambda_i \in k$, we have
\begin{equation} \label{eq:lin-comb}
[z^p] a(z) \sum_{i = 0}^{r - 1} \lambda_i \prod_{j \neq i} (1 - y_j z) = 0.
\end{equation}
Note that the $r$ polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ have degree at most $r - 1$ and are linearly independent by Lemma \ref{lem:lin-indep}.  Therefore for $0 \leq k \leq r - 1$, there exist $\{\lambda_i^k\}$ so that
\[
\sum_i \lambda_i^k b_i(z) = z^k.
\]
Substituting these choices of $\{\lambda_i^k\}$ into (\ref{eq:lin-comb}), we find that for $0 \leq k \leq r - 1$, we have
\[
[z^p] a(z) z^k = 0
\]
and therefore that $[z^k] a(z) = 0$ for $p - r + 1 \leq k \leq p$.

For each $l \in \ZZ$, consider now the Laurent polynomial
\[
h_l(z) = z^{-l - r} \prod_i (1 - y_i z)
\]
and notice that 
\begin{align*}
\frac{d}{dz} h_l(z) a(z) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_l(z) a(z) + h_l(z) a'(z) \\
&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_l(z) a(z) - h_l(z) \sum_i \frac{(m_i c - 1)y_i}{1 - y_i z} a(z)  + z^ph_l(z) b(z)\\
&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_im_i c}{1 - y_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
&= -\Big((l + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\Big) h_l(z) a(z) + z^ph_l(z) b(z).
\end{align*}
Notice that 
\[
 -\Big((l + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\Big) h_l(z)
\]
is a Laurent polynomial with lowest degree term 
\[
- z^{-l-r-1} \Big(l + r + \sum_i y_i m_i c\Big) = - z^{-l-r-1}(l + r)
\]
and highest degree term 
\[
- z^{-l - 1} (-1)^r  \prod_i y_i\Big((l + r) - \sum_i m_i c\Big).
\]
%this thing has to be nonzero. why? because we can assume c \notin \Fp?
Further, the lowest degree term of $z^p h_l(z) b(z)$ has degree at least $p - l - r$.  Now, we see that $[z^{- 1}]\frac{d}{dz} h_l(z) a(z) = 0$, so if $p - l - r > -1$ then $[z^{l}] a(z)$ is a linear combination of $[z^{l + r}] a(z), \ldots, [z^{l + 1}]a(z)$.  If all $y_i$ are not equal to $0$, then inducting down from $l = p - r$ to $l = 0$, we find
\[
[z^0] a(z) = 0, 
\]
which is a contradiction. We conclude that one of the $y_i$ has value $0$.

Assume without loss of generality that $y_0 = 0$.  Since $r > 1$, we may then run the entire argument again with $y_1, \ldots, y_{r - 1}$ to conclude that one of $y_1, \ldots, y_{r - 1}$ must be $0$, which is a contradiction.
\end{proof}

\end{document}

### 2015-05-07 ci.tex
fixed r=1 argument

@@
 We note that $[z^p]f_0(z)=\sum_{k=0}^p y_0^{p-k}[z^k]g(z)$.
-For $k=1,\dots,p-1$ we note that the term $[z^k]g(z)$ is a linear combination of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_1-\dots-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}^{\ell_1}\dots\binom{c}{k_s}^{\ell_s}y_0^k$ where $\ell_1,\dots,\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=k$ - this represents the product of $\ell_i$ terms $ (-1)^{k_i}\binom{c}{k_i} y_0^{k_i} z^{k_i}$.
-
-.
-In particular this means that $0 < \ell_1 < p$, so $\binom{n}{\ell_1}$ is $0$ in characteristic $p$, so all of these terms are $0$.
-This means that $[z^p]f_0(z)=y_0^p[z^0]g(z)+[z^p]g(z)=y_0^p+[z^p]g(z)$.
-Note that $[z^p]g(z)$ is the sum of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}\dots\binom{c}{k_s}y_0^k$ where $\ell_1,\dots,\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=p$; this term is $0$ unless $\ell_1=p$, so $[z^p]g(z)=\binom{n}{p}(-1)^p\binom{c}{1}^py_0^p=\binom{n}{p}(-c)^py_0^p$.
-Therefore $[z^p]f_0(z)=\left(1+\binom{n}{p}(-c)^p\right)y_0^p$; if this is $0$ but $y_0 \ne 0$, then $1+\binom{n}{p}(-c)^p=0$; this is false since $c$ is generic.
+For $k=1,\dots,p$ we note that the term $[z^k]g(z)$ is a linear combination of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_1-\dots-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}^{\ell_1}\dots\binom{c}{k_s}^{\ell_s}y_0^k$ where $\ell_1\ge\dots\ge\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=k$ - this represents the product of $\ell_i$ terms $ (-1)^{k_i}\binom{c}{k_i} y_0^{k_i} z^{k_i}$.
+In particular the coefficients of these terms are polynomials in $c$ that are divisible by $c$.
+Therefore $[z^p]f_0(z)=y_0^p+cs(c )y_0^p$ where $s(c )$ is a polynomial in $c$.
+If this is $0$ but $y_0^p$ is nonzero, then $cs(c )+1$ is $0$ as a polynomial of $c$ since $c$ is generic; this is false since it has constant term $1$.
 Therefore $y_0=0$.

### 2015-05-08 formalwriteup.tex
revised complete intersection argument

@@
 
-%mention previous results [BEG],[CE],[GLOR]? ask
+%mention previous results [BEG],[CE],[GGOR]? ask
 %deformation of DAHAs introduced by Etingof-Ginzburg in 2001
@@
 
+For a formal power series or Laurent series $r(z)$, we write the coefficient of $z^\ell$ in $r$ as $[z^\ell]r(z)$.
+
  We call $c$ {\it generic} if we do not specify its value.
@@
 \begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by the coefficients of $z^p$ in the formal power series \\
-$$F_a=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. 
+The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series $$F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$.
 \end{thm:main}
@@
 
-In this paper we consider the case where the characteristic of $K$ divides $n$.
-This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.
-In that case the generators of the ideal $J$ were the residues at infinity of $\frac{1}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c$ for each $a$.
-%write as proposition
+In this paper we consider the case where the characteristic of $k$ divides $n$. This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.
+
+\begin{proposition}[\cite{CE}, Proposition 3.1] Let the characteristic of $k$ be $0$ and set $c=p/n$.
+The ideal $J \subseteq A$ where $A$ is the polynomial representation of $\HH_{\hbar,c}(\h)$ is generated by $\Res_\infty\left[\frac{dz}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c\right]$ for $a=0,\dots,n-2$.
+\end{proposition}
+
 To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$.
@@
 %fill in?
-
-\paragraph{Acknowledgements} This project was done with the support of the Undergraduate Research Opportunities Program (UROP) at MIT.
-The author thanks Pavel Etingof and Yi Sun for supervising this project.
-The computer algebra system SAGE was used for obtaining data.
 
@@
 
-We let $g=\prod_{j=0}^{n-1} (1-x_jz)$.
-Let $F_a$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.
+We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$.
+Let $F_a(z)$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a(z)=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.
 
@@
 
-\begin{proposition}\label{prop:ann} Let $f_a$ be the coefficient of $z^p$ in the power series $F_a$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
+\begin{proposition}\label{prop:ann} Let $f_a=[z^p]F_a(z)$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
 \end{proposition}
@@
 
-Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$ for all $0 \le i < n-1$.
-Let $F =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
-Note that $F$ is symmetric and $F_a=\frac{F}{1-x_az}$ for all $a$.
-Then we see that for all $0 \le i < n-1$:
+Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $$\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$$ for all $0 \le i < n-1$.
+Let $$F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).$$ Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$.
+Then we see that for all $0 \le i < n-1$ we have
 
@@
 &=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F\right)\\
+&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
 \end{align*}
+%
 %\begin{align*}
@@
 %&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{n-1}^{k+1}z^{k+2}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{i}^{k+1}z^{k+2}\right)\\
-%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k}\right)\\
-%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k}\right)\\
-%&=F\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)+\\&\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\\&\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)
+%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
+%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
+%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
+%\end{align*}
+%\begin{align*}
+%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
 %\end{align*}
 %
-%Let $U=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$; clearly $z^p \mid U$ so all coefficients before that are $0$.
-The $z^p$ term is $\binom{c}{0}(-1)^0 $
-
-Let $G_i=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right)$.
+%Let $G_i=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$.
 Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.
 
-We also see that:
+We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$
+
+We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$.
 
@@
 &=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
-&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_1}{1-x_0z}\\
-&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_1}{1-x_0z}\\
+&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
+&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
+\end{align*}
+\begin{align*}
+\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
+&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
+&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
+&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.\\
 \end{align*}
 
-and that:
+We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that
 
 \begin{align*}
-\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
-&=\frac{z}{(1-x_0z)^2}F+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
-&=\frac{z}{1-x_0z}F_0+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_0}{1-x_0z}\\
-&=\frac{z}{1-x_0z}F_0+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
-&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
+\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
+&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
+&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
+&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
+&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
+&=\frac{z}{1-x_iz}F_0(z).\\
 \end{align*}
 
-We note that $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$.
-
-\begin{align*}
-\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F}{1-x_0z}-\frac{F}{1-x_iz}\right)\\
-&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F\\
-&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F\\
-&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F\\
-&=\frac{z}{(1-x_iz)(1-x_0z)}F\\
-&=\frac{z}{1-x_iz}F_0\\
-\end{align*}
-
-We recall that we need only consider the action of $D_1-D_0$ on $F_0$.
+We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$.
 We consider $D_0F_0, D_1F_0$ separately first.
-We see that $D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.
+We see that $$D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.
 
@@
 &=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
-&=\frac{G_0}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0-\sum_{j > 0} \frac{zc}{1-x_jz}F_0\\
+&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
 \end{align*}
@@
 &=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
-&=\frac{G_1}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{zc}{1-x_1z}F_0\\
-&=\frac{G_1}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0\\
+&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
+&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).\\
 \end{align*}
 
-It is then easy to see that $(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0$.
+It is then easy to see that $$(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.$$
 
@@
 
-We see easily that $\frac{\partial g}{\partial z} = g \sum_j \frac{-x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$:
+We see easily that $$\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.$$ We now consider $\frac{\partial F}{\partial z}$.
 
@@
 &=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
 &=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
@@
 &=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right)
+&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
 \end{align*}
 
-Let $V=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right)$. Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$.
+%\begin{align*}
+%\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\prod_{i=0}^{n-1} \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\\
+%&=\sum_{i=0}^{n-1}\left(\left(\sum_{k=1}^{p-1} k\binom{c}{k}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
+%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left((1-x_iz)\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
+%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
+%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
+%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
+%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} -cx_i\binom{c}{k}(-1)^{k}x_i^{k}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
+%&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\\
+%\end{align*}
+%
+%Let $V=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)$.
+Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$.
+%
 
-From this it follows that:
+We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$
+
+From this it follows that
 
 \begin{align*}
-\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F}{1-x_0z}\right)\\
-&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F\\
-&=\frac{V}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\frac{x_0}{(1-x_0z)^2} F\\
-&=\frac{V}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0+\frac{x_0}{1-x_0z} F_0\\
+\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
+&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
+&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
+&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
 \end{align*}
@@
 \begin{align*}
-(D_1-D_0)(F_0)&=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
-&=\frac{G_1-G_0}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
-&=\frac{G_1-G_0}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
-&=\frac{G_1-G_0}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
-&=\frac{G_1-G_0}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
-&=\frac{G_1-G_0}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
-&=\frac{G_1-G_0}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
-&=\frac{G_1-G_0}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V}{1-x_0z}\\
-&=\frac{G_1-G_0+z^2V}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}\\
+(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
+&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
+&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.\\
 \end{align*}
 
-We consider $V,G_1,G_0$; since $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$ and $(g-1)^{p-1}$ divides $V,G_1,G_0$, we see that for $\ell=0,1,\dots,p$, the coefficient of $z^\ell$ in $G_1-G_0+z^2V$ is $0$.
-Then in particular the coefficient of $z^p$ in $\frac{G_1-G_0+z^2V}{1-x_0z}$ is $0$, so the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is equal to the coefficient of $z^p$ in $-zF_0-z^2\frac{\partial F_0}{\partial z}$.
+We consider $V(z),G_1(z),G_0(z)$; since $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$ and $(g-1)^{p-1}$ divides $V(z),G_1(z),G_0(z)$, we see that for $0 \le \ell \le p$ that $$[z^\ell]V(z)=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.$$
 
-Let $b$ be the coefficient of $z^{p-1}$ in $F_0$.
-We see that the coefficient of $z^p$ in $-zF_0$ is $-b$.
-Then the coefficient of $z^{p-2}$ in $\frac{\partial F_0}{\partial z}$ is $(p-1)b=-b$, so the coefficient of $z^p$ in $-z^2\frac{\partial F_0}{\partial z}$ is $b$.
-Therefore the coefficient of $z^p$ in $-zF_0-z^2\frac{\partial F_0}{\partial z}$ is $-b+b=0$, so the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is $0$.
-Then if $f_0$ is the coefficient of $z^p$ in $F_0$, it is clear that $(D_1-D_0)(f_0)=0$ as desired.
-By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
+Then we also have
+ $$[z^\ell](G_1(z)-G_0(z)+z^2V(z))=0.$$ Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^\ell](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le \ell \le p$, so $$[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).$$
+
+Let $b=[z^{p-1}](F_0)$.
+We see that $[z^p](-zF_0)=-b$.
+Then $[z^{p-2}]\left(\frac{\partial F_0}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_0}{\partial z}\right)=b$.
+Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so $$[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.$$ By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
 \end{proof}
@@
 \begin{proof} 
-%We recall that $F_a=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
-It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since the coefficient of $z^k$ for any $k$ in $F_a$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).
+We recall that $F_a(z)=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since $[z^k]F_a(z)$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).
+
+Assume $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a \in k$.
+Then in particular this must be true when we set $x_a=1$ and $x_i=0$ for $i \ne a,i < n-1$.
+(We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so $$F_a(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)$$ and $$F_i(z)=\left(\sum_{k=0}^\infty 0^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k$$ for $n-1>i \ne a$.
+
+Therefore we have $[z^p]F_a(z)=f_a=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne a$ (since $p > 2$).
+Since $c$ is generic, we can assume $\binom{c-1}{(p-1)/2} \ne 0$.
+Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$, we see that $\lambda_a\binom{c-1}{(p-1)/2}=0$; then we must have $\lambda_a=0$.
+
+By setting $x_a=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne a, i \ne n-1$ for all $a=0,\dots,n-1$ in succession, we find that $\lambda_a=0$ for all $a$.
+Therefore the $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
+
 %
@@
 
+\begin{proposition}\label{prop:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
+\end{proposition}
+
+\begin{proof}
+
+Assume that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
+Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series.
+Therefore since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$.
+Then in particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.
+
+This implies that the product of the Vandermonde matrix $$\left(\begin{smallmatrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{smallmatrix}\right)$$ with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.
+
+Therefore the polynomials $b_i(z)$ are linearly independent as desired.
+
+\end{proof}
+
 \begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_a$ for $a=0,\dots,n-2$. $A/I$ is a complete intersection. 
@@
 \begin{proof}
+
+We will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
+
+We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$; then since $\sum_{i=0}^{n-1} x_i=0$ we have $\sum_{i=0}^{r-1} m_iy_i=0$.
+
+Then $g(z)=(1-y_iz)^{m_i}$. Recall $$F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.$$
+
+We assume that $y_i \ne 0$ for all $i$.
+
+Define $$a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).$$ Recall that we showed $$F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)$$ where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$.
+We then see that
+
+\begin{align*}
+a'(z)&=\frac{d}{dz}\left(\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z)\right)\\
+&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F'(z)+\sum_{j=0}^{r-1}\frac{y_j}{(1-y_jz)\prod_{i=0}^{r-1}(1-y_iz)}F(z)\\
+&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}\left(V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
+&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}a(z)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
+&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\left(\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)\right)\\\end{align*}
+
+Since $[z^\ell]V(z)=0$ for $0 \le \ell \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$.
+Therefore $$a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)$$ for some power series $b(z)$.
+
+Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Proposition~\ref{prop:vand} we see that the polynomials $b_i(z)$ are linearly independent.
+
+Note that for any $i$, $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$.
+Then in particular, $$[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0.$$ Therefore for any $\lambda_i \in k$, \begin{equation}\label{eq:lincomb}\sum_{i=0}^{r-1} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=0}^{r-1}\lambda_ib_i(z)\right)=0.\end{equation}
+
+Recall that the $b_i(z)$ are linearly independent; they also have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ such that $$\sum_i\lambda_i^kb_i(z)=z^k.$$
+
+Then if we use the $\lambda_i^k$ in Equation~\ref{eq:lincomb}, we see that $[z^p](a(z)z^k)=[z^{p-k}]a(z)=0$ for $k=0,\dots,r-1$.
+
+For any integer $\ell$ we define the Laurent polynomial $$h_\ell(z)=z^{-\ell-r}\prod_i(1-y_iz).$$ Then
+
+\begin{align*}
+\frac{d}{dz}( h_\ell(z) a(z)) &= -(l + r)z^{-1} h_\ell(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_\ell(z) a(z) + h_\ell(z) a'(z) \\
+&=  -(\ell + r)z^{-1} h_\ell(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_\ell(z) a(z) - h_\ell(z) \sum_j \frac{(m_j c - 1)y_i}{1 - y_ijz} a(z)  + z^ph_\ell(z) b(z)\\
+&= -(\ell + r)z^{-1} h_\ell(z) a(z) - \sum_i \frac{y_im_i c}{1 - y_iz} h_\ell(z) a(z) + z^ph_\ell(z) b(z)\\
+&= -\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z) a(z) + z^ph_\ell(z) b(z).
+\end{align*}
+
+We note that $$-\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z) $$ is a Laurent polynomial with lowest degree term $$- z^{-l-r-1} \left(\ell + r + \sum_i y_i m_i c\right) = - z^{-\ell-r-1}(\ell+ r)$$ and highest degree term
+$$- z^{-\ell - 1} (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right).$$
+
+The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-l-r$.
+We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$.
+Therefore we have a linear dependence relation between $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$ - we can assume this is nonzero since $c$ is generic and none of the $y_i$ are $0$.
+Therefore we can write $[z^\ell]a(z)$ as a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$.
+
+We see that since $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$, we can use induction starting with $\ell=p-r$ to show that $[z^\ell]a(z)=0$ for $\ell=p-r,p-r-1,\dots,0$.
+Therefore $[z^0]a(z)=0$; however, it is clear from the definition of $a(z)$ that this is not the case.
+Therefore we have a contradiction, so one of the $y_i$ is $0$.
+
+We can assume without loss of generality that $y_{r-1}=0$.
+Then if $r>1$, we can go through the same argument again with $y_0,\dots,y_{r-2}$ and find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
+Therefore we must have $r=1$ and $y_0=0$.
 
@@
 \begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by the coefficients of $z^p$ in the formal power series \\
-$$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. \end{theorem}
+The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series $$F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$.
+\end{theorem}
 
@@
 \end{proof}
+
+\paragraph{Acknowledgements} This project was done with the support of the Undergraduate Research Opportunities Program (UROP) at MIT.
+The author thanks Pavel Etingof and Yi Sun for supervising this project.
+The computer algebra system SAGE was used for obtaining data.
 

### 2015-05-08 formalwriteup.tex
revisions to intro + ci argument

@@
 \begin{abstract}
-We study the polynomial representation of the ratioal Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$.
+We study the polynomial representation of the rational Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$.
 We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient.
@@
 The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$).
-In general new techniques are required to study positive characteristc as opposed to characteristic 0.
-In this paper we directly connect the characteristc 0 case to the positive characteristic case; instead of taking complex residues, we consider the coefficients of formal power series in positive characteristic.
-While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups.
-%this bit needs revisions
+In general new techniques are required to study positive characteristic as opposed to characteristic 0.
+In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues.
+In the positive characteristic case, we instead let the generators be the coefficients of formal power series.
+In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic.
+We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $\Sigma_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.
+
+While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions
 
@@
 
-We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
+%We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
 
@@
 \begin{proof}
-%Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations.
-We see that this means we can apply the Dunkl operators to $F_a$ and check that the coefficient of $z^p$ in the result is $0$ to show that the Dunkl operators annihilate the $f_a$.
-%
-%We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$.
-Therefore we need only consider the action of the Dunkl operators on $F_0$.
-We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators.
-%
-%We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$.
-In particular, we note that since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$, we have $z^2 \mid g-1$.
-Then since $p>2$, we note that $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$.
-Therefore we can add multiples of $(g-1)^{p-1}$ when taking the Dunkl operator's action on $F_0$, since even when multipled by another power series it cannot contribute anything to the coefficient of $z^p$.
-We also note that we can add $n$ times any multiple of $F_0$ since $n \equiv 0 \bmod p$.
 
@@
 \end{align*}
-%
-%\begin{align*}
-%&=V_i\frac{\partial}{\partial x_i}\left(\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\right)\\
-%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{i}^kz^k\right)\\
-%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} -k\binom{c}{k}(-1)^kx_{n-1}^{k-1}z^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-1} k\binom{c}{k}(-1)^kx_{i}^{k-1}z^k\right)\\
-%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{n-1}^{k-1}z^k\right)-V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{i}^{k-1}z^k\right)\\
-%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
-%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)(1-x_{n-1}z)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)(1-x_iz)\\
-%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{n-1}^{k+1}z^{k+2}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{i}^{k+1}z^{k+2}\right)\\
-%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
-%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
-%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
-%\end{align*}
-%\begin{align*}
-%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
-%\end{align*}
-%
-%Let $G_i=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$.
-Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.
-
 We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$
@@
 \end{align*}
-
-%\begin{align*}
-%\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\prod_{i=0}^{n-1} \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\\
-%&=\sum_{i=0}^{n-1}\left(\left(\sum_{k=1}^{p-1} k\binom{c}{k}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
-%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left((1-x_iz)\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
-%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
-%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
-%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
-%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} -cx_i\binom{c}{k}(-1)^{k}x_i^{k}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
-%&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\\
-%\end{align*}
-%
-%Let $V=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)$.
-Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$.
-%
-
 We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$
@@
 
-We consider $V(z),G_1(z),G_0(z)$; since $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$ and $(g-1)^{p-1}$ divides $V(z),G_1(z),G_0(z)$, we see that for $0 \le \ell \le p$ that $$[z^\ell]V(z)=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.$$
+We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$.
+We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$.
+Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$.
+Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$.
+(We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)
+
+Then we see that for $0 \le \ell \le p$ we have $$[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.$$
 
@@
 
-%
-%Since $c$ is generic, we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $A$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$.
-Recall that $f_a$ is the coefficient of $z^p$ in $F_a=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
-Then as polynomials it is clear that $c \mid \binom{c}{k}$ for all $k > 0$; therefore when trying to find the constant term of the coefficient of $z^p$, we can ignore the terms with $k > 0$ in the second multiplicand.
-The term for $k=0$ is just $1$; it is then clear that the constant term (the coefficient of $c^0$) of $f_a$ is $x_a^p$.
-%
-%If $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$.
-We assume that not all of the $\lambda_a$ are $0$.
-Then we can let $e$ be the smallest nonnegative integer such that there exists an index $b$ with the coefficient of $c^e$ in $\lambda_b$ nonzero.
-We can divide all of the $\lambda_a$ by $c^e$, so that $\lambda_b$ for some $b$ must have nonzero constant term.
-%
-%The constant term of the sum is $\sum_{a=0}^{n-2}\mu_ax_a^p$ where $\mu_a$ is the constant term of $\lambda_a$.
-Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $\mu_a$ must be $0$ for $a=0,\dots,n-2$ .
-Then in particular the constant term $\mu_b$ of $\lambda_b$ is $0$, a contradiction.
-This means that our assumption that not all of the $\lambda_a$ were $0$ is false, so $\lambda_a=0$ for all $a$.
-%
-%Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$ means all the $\lambda_a$ are $0$, we see that $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
-
 \end{proof}
@@
 
-This implies that the product of the Vandermonde matrix $$\left(\begin{smallmatrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{smallmatrix}\right)$$ with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.
+This implies that the product of the Vandermonde matrix $$\left(\begin{matrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{matrix}\right)$$ with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.
 
@@
 
+We will show that we must have $[z^0]a(z)=0$, a contradiction. Note that if $r > p$ then we have already shown that; therefore we assume $r \le p$.
+
 For any integer $\ell$ we define the Laurent polynomial $$h_\ell(z)=z^{-\ell-r}\prod_i(1-y_iz).$$ Then
@@
 
-The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-l-r$.
-We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$.
-Therefore we have a linear dependence relation between $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$ - we can assume this is nonzero since $c$ is generic and none of the $y_i$ are $0$.
-Therefore we can write $[z^\ell]a(z)$ as a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$.
+The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-\ell-r$. We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$.
+
+Then as long as $p-\ell-r \ge 0$, which is true when $\ell \le p-r$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$ is a linear combination of $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$ - we can assume this is nonzero since $c$ is generic and none of the $y_i$ are $0$.
+Therefore we can write $[z^\ell]a(z)$ as a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ when $\ell \le p-r$.
 
@@
 We can assume without loss of generality that $y_{r-1}=0$.
-Then if $r>1$, we can go through the same argument again with $y_0,\dots,y_{r-2}$ and find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
+Then if $r>1$, we can go through the same argument again with $y_0,\dots,y_{r-2}$.
+We are able to do this because our calculation of $F'(z)$ and $V(z)$ so that $z^p \mid V(z)$ relies only on the fact that $\sum m_iy_i=0$, which will still be true if we leave out $y_{r-1}=0$.
+We will then find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
 Therefore we must have $r=1$ and $y_0=0$.
 
-%We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $K$.
-Then we can consider $f_a$ as a function on these vectors $x$ for all $a$.
-For any rational function $u( c)$, we let $u(c )x=\langle u(c )x_0,\dots, u(c )x_{n-2}\rangle$.
-%
-%To show that $A/I$ is a complete intersection, we will show that if $f_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$, which is an equivalent condition. 
-%
-%By Proposition~\ref{prop:linind}, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$ for all $a$.
-Then for any rational function $u(c )$, we see that $f_a(u(c )x)=u(c )^pf_a(x)$.
-In particular, if $f_a(x)=0$, then for any rational function $u(c )$ we have $f_a(u(c )x)=0$ as well.
-Therefore if $f_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial in $c$ for all $i=0,\dots,n-2$ (a least common denominator), we see that since $f_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$.
-We assume that not all of the $x_a$ are $0$.
-Then we can find the smallest nonnegative integer $e$ such that there exists an $b$ with the coefficient of $c^e$ in $x_b$ nonzero.
-Then since $f_a(\frac{1}{c^e}x)=0$ and $x_i/c^e$ is still a polynomial for any $i$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero by dividing through by $c^e$.
-%
-%For any $a$, we can then consider $f_a(x)$ to be a polynomial in $c$.
-Since this is zero, we can in particular consider the constant term, which must be $0$.
-The constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power.
-If this is zero, then the constant term of $x_a$ must be $0$.
-%
-%Then if $f_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$.
-In particular, $x_b$ has zero constant term, a contradiction.
-This means that our assumption that not all of the $x_a$ were $0$ is false, so $x_a=0$ for all $a$.
-%
-%Therefore $f_0(x) = \dots = f_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection.
 \end{proof}
@@
 
-By Proposition 3.4 in \cite{BC1}, we see that the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
+By Proposition 3.4 in \cite{BC1}, we see that the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
 Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal $J$.

### 2015-05-14 formalwriteup.tex
S_n notation, linebreak issue, shorter algebra

@@
 
-\author{Sheela Devadas}
+\author{Sheela Devadas and Yi Sun}
 
@@
 
-In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$.
+In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $S_n$ in characteristic $p$ dividing $n$.
 This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic.
 Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}.
-The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$).
+The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $S_n$).
 In general new techniques are required to study positive characteristic as opposed to characteristic 0.
@@
 In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic.
-We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $\Sigma_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.
+We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $S_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.
 
-While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions
+While we only consider the case of the symmetric group $S_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions
 
@@
 
-Given the symmetric group $\Sigma_n$, we let $\mathcal{S}$ be the set of reflections in $\Sigma_n$.
-Let $\h$ be the irreducible $(n-1)$-dimensional representation of $\Sigma_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$.
+Given the symmetric group $S_n$, we let $\mathcal{S}$ be the set of reflections in $S_n$.
+Let $\h$ be the irreducible $(n-1)$-dimensional representation of $S_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$.
 For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.
@@
 We choose $\hbar,c \in k$.
-Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the relations
+Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
 \begin{align*}
@@
 We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
-We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[\Sigma_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).
+We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).
 
@@
 We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$.
-We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $\Sigma_n$ of dimension $n-1$.
+We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $S_n$ of dimension $n-1$.
 We state our result for this case below:
@@
 To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions.
-The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
+The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[S_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
 For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
@@
 
-We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $\Sigma_n$ acts by permuting indices.
+We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $S_n$ acts by permuting indices.
 Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.
@@
 
-For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
+For a transposition $s_{ij} \in S_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
 
@@
 Then we see that for all $0 \le i < n-1$ we have
-
 \begin{align*}
-\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+\frac{\partial F}{\partial x_i}%&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
 &=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
 &=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
+%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
 &=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
+%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
 &=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
@@
 We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. 
-
 \begin{align*}
-\frac{\partial F_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+\frac{\partial F_0}{\partial x_1}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
 &=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
@@
 &=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
-\end{align*}
-\begin{align*}
-\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
+\frac{\partial F_0}{\partial x_0}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
 &=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
 &=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
-&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
+%&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
 &=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.\\
 \end{align*}
-
 We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that 
-
 \begin{align*}
-\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
+\frac{1-s_{0i}}{x_0-x_i}(F_0)%&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
 &=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
-&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
-&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
+%&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
+%&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
 &=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
@@
 \end{align*}
-
 We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$.
@@
 We see that $$D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.
-
 \begin{align*}
@@
 &=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
-\end{align*}
-\begin{align*}
 D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
@@
 \end{align*}
-
 It is then easy to see that $$(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.$$
@@
 We see easily that $$\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.$$ We now consider $\frac{\partial F}{\partial z}$.
-
 \begin{align*}
-\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
 &=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
 &=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
 &=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
@@
 From this it follows that
-
 \begin{align*}
@@
 \end{align*}
-
 We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
-
 \begin{align*}
 (D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
+%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
+%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
 &=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
+%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
 &=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
+%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
 &=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
@@
 \end{align*}
-
 We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$.
@@
 We then see that
-
 \begin{align*}
@@
 &=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\left(\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)\right)\\\end{align*}
-
 Since $[z^\ell]V(z)=0$ for $0 \le \ell \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$.
@@
 For any integer $\ell$ we define the Laurent polynomial $$h_\ell(z)=z^{-\ell-r}\prod_i(1-y_iz).$$ Then
-
 \begin{align*}

### 2015-05-14 formalwriteup.tex
Remove non .tex files, add .bib file, change acknowledgments

@@
 \usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
 \usepackage{graphicx}
 \usepackage{verbatim}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks,
+    citecolor=blue,
+    filecolor=black,
+    linkcolor=black,
+    urlcolor=black
+}
+
+\usepackage{todonotes}
 
@@
 %fill in?
+\subsection{Acknowledgements}
+
+This project was done with the support of the Undergraduate Research Opportunities Program (UROP) at MIT.
+The authors thank P.
+Etingof for suggesting the problem.
+Some exploratory computations were done using Sage.
+Y.~S.
+was supported by a NSF Graduate Research Fellowship (NSF Grant \#1122374).
+
+\todo[inline]{Ask Pavel for his grant number}
 
@@
 
-\paragraph{Acknowledgements} This project was done with the support of the Undergraduate Research Opportunities Program (UROP) at MIT.
-The author thanks Pavel Etingof and Yi Sun for supervising this project.
-The computer algebra system SAGE was used for obtaining data.
-
-\begin{thebibliography}{2}
-
-\setlength{\itemsep}{-1mm}
-\small
-
-\bibitem{BC1} Martina Balagovi\'c, Harrison Chen, Representations of rational Cherednik algebras in positive characteristic, {\it J.
-Pure Appl.
-Algebra} {\bf 217} (2013), no.~4, 716--740, \arxiv{1107.0504v2}.
-
-\bibitem{CE} Tatyana Chmutova, Pavel Etingof, On some representations of the rational Cherednik algebra, {\it Representation Theory of the American Mathematical Society} {\bf 7.24} (2003), 641--650, \arxiv{0303194v2}
-
-\bibitem{DS} Sheela Devadas, Steven V.
-Sam, Representations of rational Cherednik algebras of G(m,r,n) in positive characteristic, {\it Journal of Commutative Algebra} {\bf 6.4} (2014), 525--559, \arxiv{1304.0856v2}
-
-\bibitem{EM} Pavel Etingof, Xiaoguang Ma, Lecture notes on Cherednik algebras, \arxiv{1001.0432v4}.
-
-\bibitem{L} Carl Lian, Representations of Cherednik algebras associated to symmetric and dihedral groups in positive characteristic, \arxiv{1207.0182v1}.
-
-\end{thebibliography}
+\bibliographystyle{alpha}
+\bibliography{rca-bib}
 

### 2015-05-14 formalwriteup.tex
Add background section, add references

@@
-\documentclass{article}
+\documentclass{amsart}
 \usepackage{amsmath}
@@
 \numberwithin{equation}{section}
+\theoremstyle{definition}
 \newtheorem{theorem}[equation]{Theorem}
@@
     \begin{definition}[#1]\pushQED{\qed}}{\popQED \end{definition}}
-\parindent=0in
-\parskip=0.15in
 
@@
 \newcommand{\Sym}{\operatorname{Sym}}
-
-\title{Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$}
-
-\author{Sheela Devadas and Yi Sun}
-
-\date{\today}
+\renewcommand{\char}{\text{char}}
 
 \begin{document}
-
-\maketitle
+\title[Polynomial representation of type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$]{The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$}
+\author{Sheela Devadas}
+\email[S. Devadas]{sheelad@mit.edu}
+\author{Yi Sun}
+\email[Y. Sun]{yisun@math.mit.edu}
+\date{\today}
 
@@
 \end{abstract}
+
+\maketitle
 
@@
 We choose $\hbar,c \in k$.
-Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
+Then we define the {\it rational Cherednik algebra of type $A$} $\HH_{\hbar,c}(\h)$ as the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
 \begin{align*}
@@
 
-\subsection{Connection to characteristic $0$ results}
+\subsection{Connections to previous work}
 
-In this paper we consider the case where the characteristic of $k$ divides $n$. This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}.
+Our study is motivated by previous work on the representation theory of the type $A$ rational Cherednik algebra in both characteristic $0$ and $p$.
+In characteristic $p = 2$ with $p \mid n$, it was shown in \cite[Theorem 5.1]{L} that the irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection and that the corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and a single element of degree $4$.
+In particular, this implies that the Hilbert series is
+\[
+h(t) = (1 + t)^n (1 + t^2).
+\]
+It was conjectured by C.~Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
+Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.
+It would be interesting to extend our work to prove Lian's conjecture in full.
 
-\begin{proposition}[\cite{CE}, Proposition 3.1] Let the characteristic of $k$ be $0$ and set $c=p/n$.
-The ideal $J \subseteq A$ where $A$ is the polynomial representation of $\HH_{\hbar,c}(\h)$ is generated by $\Res_\infty\left[\frac{dz}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c\right]$ for $a=0,\dots,n-2$.
+In characteristic $0$, our results parallel the explicit decomposition of the polynomial representation of the type $A$ rational Cherednik algebra given in \cite{BEG, CE}.
+There, the polynomial representation is irreducible unless $c = \frac{r}{n}$ for some integer $r$, and an explicit set of generators of the maximal ideal is known.
+\begin{proposition}[{\cite[Proposition 3.1]{CE}}] \label{prop:ce}
+If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal ideal $J \subset A$ of the polynomial representation $A$ of $\HH_{\hbar,c}(\h)$ is generated by
+\[
+\Res_\infty\left[\frac{dz}{z-x_j} \prod_{i=0}^{n-1} (z-x_i)^c\right] \text{ for $j=0,\dots,n-2$}.
+\]
 \end{proposition}
+We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then taking $c = \frac{p}{n}$ should correspond to taking generic $c$.
+While this substitution is of course invalid, Proposition \ref{prop:ce} may be interpreted as a statement about certain formal power series.
+By using a power series version of this construction of generators which  makes sense in characteristic $p$, we are able to mimic the arguments of \cite{BEG, CE} to show that they cut out a complete intersection and generate the entire ideal.
+We believe that the philosophy of taking characteristic $p$ analogues of characteristic $0$ results for the rational Cherednik algebra should apply more generally and hope to explore this further in future work.
 
-To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$.
-The formal power series would be $\frac{1}{z^{p+1}}\frac{1}{1-x_az}\prod_{j=0}^{n-1} (1-x_jz)^c$, with the corresponding generator as the coefficient of $1/z$.
-We simplify and truncate the formal power series so we can define it in positive characteristic.
-
-\subsection{Relation to previous work}
-
-%fill in?
 \subsection{Acknowledgements}
 
-This project was done with the support of the Undergraduate Research Opportunities Program (UROP) at MIT.
 The authors thank P.
-Etingof for suggesting the problem.
+Etingof for suggesting the problem and for helpful discussions.
 Some exploratory computations were done using Sage.
+S.~D.
+was supported by the MIT Undergraduate Research Opportunities Program (UROP).
 Y.~S.

### 2015-05-14 formalwriteup.tex
Fix some formatting

@@
 We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
-We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).
+We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite[Section 3.2]{EM}).
 
@@
 \end{align*}
-
 We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $S_n$ acts by permuting indices.
@@
 \begin{proof}
-
 Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $$\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$$ for all $0 \le i < n-1$.
@@
 &=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}a(z)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\left(\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)\right)\\\end{align*}
+&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\left(\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)\right).
+\end{align*}
 Since $[z^\ell]V(z)=0$ for $0 \le \ell \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$.
@@
 \end{align*}
-
 We note that $$-\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z) $$ is a Laurent polynomial with lowest degree term $$- z^{-l-r-1} \left(\ell + r + \sum_i y_i m_i c\right) = - z^{-\ell-r-1}(\ell+ r)$$ and highest degree term
@@
 Therefore we must have $r=1$ and $y_0=0$.
-
 \end{proof}
@@
 Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal $J$.
-
 \end{proof}

### 2015-05-14 formalwriteup.tex
Change all 854 to \[ \]

@@
 \begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series $$F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$.
+The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series
+\[
+F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $a=0,\dots,n-2$}.
+\]
 \end{thm:main}
@@
 \begin{proof}
-Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $$\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$$ for all $0 \le i < n-1$.
-Let $$F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).$$ Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$.
-Then we see that for all $0 \le i < n-1$ we have
+Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that
+\[
+\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z} \text{ for all $0 \le i < n-1$}.
+\]
+Let 
+\[
+F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
+\]
+Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 
 \begin{align*}
@@
 \end{align*}
-We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$
-
+We define
+\[
+G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
+\]
+Then we see that 
+\[
+\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).
+\]
 We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. 
@@
 \end{align*}
-We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$.
-We consider $D_0F_0, D_1F_0$ separately first.
-We see that $$D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.
+We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that 
+\[
+D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)
+\]
+since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. 
 \begin{align*}
@@
 \end{align*}
-It is then easy to see that $$(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.$$
-
+It is then easy to see that 
+\[
+(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
+\]
 In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.
 
-We see easily that $$\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.$$ We now consider $\frac{\partial F}{\partial z}$.
+We see easily that 
+\[
+\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
+\]
+We now consider $\frac{\partial F}{\partial z}$.
 \begin{align*}
@@
 \end{align*}
-We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$
-
+We define 
+\[
+V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+\]
+Then we see that 
+\[
+\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).
+\]
 From this it follows that
@@
 
-Then we see that for $0 \le \ell \le p$ we have $$[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.$$
-
+Then we see that for $0 \le \ell \le p$ we have
+\[
+[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.
+\]
 Then we also have
- $$[z^\ell](G_1(z)-G_0(z)+z^2V(z))=0.$$ Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^\ell](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le \ell \le p$, so $$[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).$$
-
+\[
+[z^\ell](G_1(z)-G_0(z)+z^2V(z))=0.
+\]
+Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^\ell](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le \ell \le p$, so 
+\[
+[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).
+\]
 Let $b=[z^{p-1}](F_0)$.
@@
 Then $[z^{p-2}]\left(\frac{\partial F_0}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_0}{\partial z}\right)=b$.
-Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so $$[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.$$ By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
+Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so
+\[
+[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.
+\]
+By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
 \end{proof}
@@
 Then in particular this must be true when we set $x_a=1$ and $x_i=0$ for $i \ne a,i < n-1$.
-(We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so $$F_a(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)$$ and $$F_i(z)=\left(\sum_{k=0}^\infty 0^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k$$ for $n-1>i \ne a$.
+(We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so
+\[
+F_a(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)
+\]
+and 
+\[
+F_i(z)=\left(\sum_{k=0}^\infty 0^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k
+\]
+for $n-1>i \ne a$.
 
@@
 Therefore the $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
-
 \end{proof}
@@
 \end{proposition}
-
 \begin{proof} 
-
 Assume that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
@@
 
-This implies that the product of the Vandermonde matrix $$\left(\begin{matrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{matrix}\right)$$ with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.
+This implies that the product of the Vandermonde matrix 
+\[
+\left(\begin{matrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{matrix}\right)
+\]
+with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.
 
 Therefore the polynomials $b_i(z)$ are linearly independent as desired.
-
 \end{proof}
@@
 
-Then $g(z)=(1-y_iz)^{m_i}$. Recall $$F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.$$
+Then $g(z)=(1-y_iz)^{m_i}$. Recall that
+\[
+F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.
+\]
 
@@
 
-Define $$a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).$$ Recall that we showed $$F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)$$ where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$.
-We then see that
+Define
+\[
+a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).
+\]
+Recall that we showed
+\[
+F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
+\]
+where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$. We then see that
 \begin{align*}
@@
 \end{align*}
-Since $[z^\ell]V(z)=0$ for $0 \le \ell \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$.
-Therefore $$a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)$$ for some power series $b(z)$.
+Since $[z^\ell]V(z)=0$ for $0 \le \ell \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$. Therefore
+\[
+a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)
+\]
+for some power series $b(z)$.
 
@@
 
-Note that for any $i$, $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$.
-Then in particular, $$[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0.$$ Therefore for any $\lambda_i \in k$, \begin{equation}\label{eq:lincomb}\sum_{i=0}^{r-1} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=0}^{r-1}\lambda_ib_i(z)\right)=0.\end{equation}
-
-Recall that the $b_i(z)$ are linearly independent; they also have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ such that $$\sum_i\lambda_i^kb_i(z)=z^k.$$
-
+Note that for any $i$, $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$. Then in particular, we have 
+\[
+[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0
+\]
+Therefore for any $\lambda_i \in k$, we have
+\begin{equation}\label{eq:lincomb}
+\sum_{i=0}^{r-1} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=0}^{r-1}\lambda_ib_i(z)\right)=0.
+\end{equation}
+Recall that the $b_i(z)$ are linearly independent; they also have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
+\[
+\sum_i\lambda_i^kb_i(z)=z^k.
+\]
 Then if we use the $\lambda_i^k$ in Equation~\ref{eq:lincomb}, we see that $[z^p](a(z)z^k)=[z^{p-k}]a(z)=0$ for $k=0,\dots,r-1$.
@@
 
-For any integer $\ell$ we define the Laurent polynomial $$h_\ell(z)=z^{-\ell-r}\prod_i(1-y_iz).$$ Then
+For any integer $\ell$ we define the Laurent polynomial 
+\[
+h_\ell(z)=z^{-\ell-r}\prod_i(1-y_iz).
+\]
+Then we have
 \begin{align*}
@@
 \end{align*}
-We note that $$-\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z) $$ is a Laurent polynomial with lowest degree term $$- z^{-l-r-1} \left(\ell + r + \sum_i y_i m_i c\right) = - z^{-\ell-r-1}(\ell+ r)$$ and highest degree term
-$$- z^{-\ell - 1} (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right).$$
-
+We note that 
+\[
+-\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z)
+\]
+is a Laurent polynomial with lowest degree term 
+\[
+- z^{-l-r-1} \left(\ell + r + \sum_i y_i m_i c\right) = - z^{-\ell-r-1}(\ell+ r)
+\]
+and highest degree term 
+\[
+- z^{-\ell - 1} (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right).
+\]
 The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-\ell-r$. We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$.
@@
 \begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series $$F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$.
+The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series
+\[
+F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $a=0,\dots,n-2$}.
+\]
 \end{theorem}
+\begin{proof}
+It suffices to show that the $f_a$ generate the ideal $J$ and that $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
 
-\begin{proof} It suffices to show that the $f_a$ generate the ideal $J$ and that $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-
-By Propositions~\ref{prop:linind}, \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
+By Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
 It then must have Hilbert series $h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
@@
 
-By Proposition 3.4 in \cite{BC1}, we see that the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
+By \cite[Proposition 3.4]{BC1}, we see that the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
 Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal $J$.

### 2015-05-14 formalwriteup.tex
Add references

@@
 
-As described in Section 2.5 of \cite{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
+As described in \cite[Section 2.5]{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
 \begin{align*}
@@
 Our study is motivated by previous work on the representation theory of the type $A$ rational Cherednik algebra in both characteristic $0$ and $p$.
-In characteristic $p = 2$ with $p \mid n$, it was shown in \cite[Theorem 5.1]{L} that the irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection and that the corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and a single element of degree $4$.
+The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
+In the modular case $p \mid n$, for $p = 2$, it was shown in \cite[Theorem 5.1]{L} that the irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection and that the corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and a single element of degree $4$.
 In particular, this implies that the Hilbert series is
@@
 It would be interesting to extend our work to prove Lian's conjecture in full.
+For general $p \mid n$, a subideal of the maximal ideal was computed in \cite[Proposition 6.1]{DS}.
 

### 2015-05-14 formalwriteup.tex
propositions 3.1-3.3

@@
 
-In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $S_n$ in characteristic $p$ dividing $n$.
-This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic.
-Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}.
-The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $S_n$).
-In general new techniques are required to study positive characteristic as opposed to characteristic 0.
-In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues.
-In the positive characteristic case, we instead let the generators be the coefficients of formal power series.
-In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic.
-We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $S_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.
+The present work presents a detailed study of the polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra over a field of characteristic $p$ dividing $n$.
+Rational Cherednik algebras were introduced by Etingof-Ginzburg in \cite{EG} as a rational degeneration of the double affine Hecke algebra dependent on two parameters $\hbar$ and $c$.
+In characteristic $0$, their type $A$ representation theory has been the subject of extensive study.
+We refer the reader to \cite{EM} for a survey of these results.
 
-While we only consider the case of the symmetric group $S_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions
+In characteristic $p$ and especially in the modular case, much less is known about the representation theory of the rational Cherednik algebra.
+In this paper, we consider the modular case $p \mid n$.
+For $\hbar = 1$ and generic $c$, we provide a complete characterization of the irreducible quotient of the polynomial representation.
+We give explicit generators for the unique maximal ideal, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.
 
-%mention previous results [BEG],[CE],[GGOR]? ask
-%deformation of DAHAs introduced by Etingof-Ginzburg in 2001
+Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.
+In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
+While we restrict our present study to the polynomial representation in type $A$, we view this problem as a test case for this philosophy and believe it may admit wider application.
+
+In the remainder of this introduction, we give precise statements of our results and explain how they relate to other recent work.
 
@@
 
-\subsection{Main results}
+\subsection{Statement of the main results}
 
@@
 \]
-It was conjectured by C.~Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
+It was conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
 Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.
@@
 We believe that the philosophy of taking characteristic $p$ analogues of characteristic $0$ results for the rational Cherednik algebra should apply more generally and hope to explore this further in future work.
+
+\subsection{Outline of the paper}
+
+The remainder of this paper is organized as follows.
+In Section 2, we give some necessary background on rational Cherednik algebras and fix the form of the Dunkl operators which will be used in later computations.
+In Section 3, we check that our generators are singular vectors, show that they cut out a complete intersection, and finally deduce Theorem \ref{thm:main}.
 
@@
 
-We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$.
-Let $F_a(z)$ for $a=0,\dots,n-1$ be the formal power series in $z$ defined by $F_a(z)=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k\right)$ where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$.
+\subsection{An explicit construction of singular vectors}
+
+We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z)$ be the formal power series in $z$ defined by
+\[
+F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
+\]
+where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$. 
+Let $F_i(z)$ for $i=0,\dots,n-1$ be $\frac{F(z)}{1-x_iz}$ and $f_i=[z^p]F_i(z)$. The $f_i$ will be the generators of the maximal ideal $J$.
 
@@
 
-\begin{proposition}\label{prop:ann} Let $f_a=[z^p]F_a(z)$. Then $f_a$ for $a=0,\dots,n-1$ are annihilated by the Dunkl operators. 
+\begin{proposition}\label{prop:ann} The elements $f_i$ for $i=0,\dots,n-1$ are annihilated by $D_i-D_j$ for all $i \ne j$.
 \end{proposition}
@@
 \begin{proof}
+
+We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$.
+It therefore suffices to consider the action of the Dunkl operators on $f_0$.
+We note that the Dunkl operators $D_i-D_j$ for all $i \ne j$ are spanned by $D_i-D_0$ for $0<i \le n-1$; then because $f_0$ is symmetric in the $x_i$ with $i > 0$, we see that it suffices to consider the action of $D_1-D_0$ on $f_0$ to show that the $f_i$ are annihilated by $D_i \ne D_j$ for all $i \ne j$.
+
 Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that
@@
 \]
-Let 
-\[
-F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
-\]
-Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 
+We recall that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 
 \begin{align*}
@@
 \]
-since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. 
+since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. We now compute
 \begin{align*}
@@
 \]
-We now consider $\frac{\partial F}{\partial z}$.
+We now consider $\frac{\partial F}{\partial z}$. We compute
 \begin{align*}
@@
 \]
-By the symmetry of the $F_a$, this is the only Dunkl operator we need consider; it is clear that all the $f_a$ are killed by the Dunkl operators.
+By the symmetry of the $F_i$, this is the only Dunkl operator we need consider; it is clear that all the $f_i$ are killed by the Dunkl operators.
 \end{proof}
 
-\begin{proposition}\label{prop:linind} The $f_a$ for $a=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.
+\begin{proposition}\label{prop:linind} The $f_i$ for $i=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.
 \end{proposition}
@@
 \begin{proof} 
-We recall that $F_a(z)=\frac{1}{1-x_az}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
-It is then clear that $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$, since $[z^k]F_a(z)$ is a homogeneous polynomial in the $x_i$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_a$).
+We recall that $F_i(z)=\frac{1}{1-x_iz}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_i^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
+It is then clear that $f_i$ is a homogeneous polynomial in the $x_j$ of degree $p$, since $[z^k]F_i(z)$ is a homogeneous polynomial in the $x_j$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_i$).
 
-Assume $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a \in k$.
-Then in particular this must be true when we set $x_a=1$ and $x_i=0$ for $i \ne a,i < n-1$.
+Assume $\sum_{i=0}^{n-2} \lambda_if_i=0$ for some $\lambda_i \in k$.
+Then in particular this must be true when we set $x_j=1$ and $x_i=0$ for $i \ne j,i < n-1$.
 (We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so
 \[
-F_a(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)
+F_j(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)
 \]
@@
 \]
-for $n-1>i \ne a$.
+for $n-1>i \ne j$.
 
-Therefore we have $[z^p]F_a(z)=f_a=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne a$ (since $p > 2$).
+Therefore we have $[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne j$ (since $p > 2$).
 Since $c$ is generic, we can assume $\binom{c-1}{(p-1)/2} \ne 0$.
-Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$, we see that $\lambda_a\binom{c-1}{(p-1)/2}=0$; then we must have $\lambda_a=0$.
+Then since $\sum_{i=0}^{n-2} \lambda_if_i=0$, we see that $\lambda_j\binom{c-1}{(p-1)/2}=0$; then we must have $\lambda_j=0$.
 
-By setting $x_a=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne a, i \ne n-1$ for all $a=0,\dots,n-1$ in succession, we find that $\lambda_a=0$ for all $a$.
-Therefore the $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.
+By setting $x_j=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne j, i \ne n-1$ for all $j=0,\dots,n-1$ in succession, we find that $\lambda_j=0$ for all $j$.
+Therefore the $f_i$ for $i=0,\dots,n-2$ are linearly independent as desired.
 \end{proof}
+
+\subsection{Complete interesction properties}
 
@@
 \begin{proof} 
-Assume that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
+Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
 Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series.
-Therefore since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$.
-Then in particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.
+Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$.
+In particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.
 
-This implies that the product of the Vandermonde matrix 
-\[
-\left(\begin{matrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{matrix}\right)
-\]
-with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.
+However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$.
 
@@
 
-\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_a$ for $a=0,\dots,n-2$. $A/I$ is a complete intersection. 
+\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_i$ for $i=0,\dots,n-2$.  The $A/I$ is a complete intersection. 
 \end{proposition}

### 2015-05-15 formalwriteup.tex
Rewrite beginning of introduction

--- 2015-05-14 formalwriteup.tex
@@
 
-In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $S_n$ in characteristic $p$ dividing $n$.
-This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic.
-Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}.
-The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $S_n$).
-In general new techniques are required to study positive characteristic as opposed to characteristic 0.
-In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues.
-In the positive characteristic case, we instead let the generators be the coefficients of formal power series.
-In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic.
-We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $S_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.
+The present work presents a detailed study of the polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra over a field of characteristic $p$ dividing $n$.
+Rational Cherednik algebras were introduced by Etingof-Ginzburg in \cite{EG} as a rational degeneration of the double affine Hecke algebra dependent on two parameters $\hbar$ and $c$.
+In characteristic $0$, their type $A$ representation theory has been the subject of extensive study.
+We refer the reader to \cite{EM} for a survey of these results.
 
-While we only consider the case of the symmetric group $S_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions
+In characteristic $p$ and especially in the modular case, much less is known about the representation theory of the rational Cherednik algebra.
+In this paper, we consider the modular case $p \mid n$.
+For $\hbar = 1$ and generic $c$, we provide a complete characterization of the irreducible quotient of the polynomial representation.
+We give explicit generators for the unique maximal ideal, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.
 
-%mention previous results [BEG],[CE],[GGOR]? ask
-%deformation of DAHAs introduced by Etingof-Ginzburg in 2001
+Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.
+In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
+While we restrict our study to type $A$ in this paper, we view this problem as a test case this philosophy and believe it may admit wider application.
+
+In the remainder of this introduction, we give precise statements of our results and explain how they relate to other recent work.
 

### 2015-05-15 formalwriteup.tex
Change section title
Reword intro

@@
 In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
-While we restrict our study to type $A$ in this paper, we view this problem as a test case this philosophy and believe it may admit wider application.
+While we restrict our present study to the polynomial representation in type $A$, we view this problem as a test case for this philosophy and believe it may admit wider application.
 

### 2015-05-15 formalwriteup.tex
more section 3 edits

--- 2015-05-14 formalwriteup.tex
@@
 \begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series
+The maximal ideal $J$ is generated by $[z^p]F_i(z)$ for the formal power series
 \[
-F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $a=0,\dots,n-2$}.
+F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $i=0,\dots,n-2$}.
 \]
@@
 
-Therefore we have $[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne j$ (since $p > 2$).
+We first consider the case $p=2$.
+In this case $[z^2]F_j(z)=1-c$ and $[z^2]F_i(z)=-c$.
+By setting $x_j=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne j, i \ne n-1$ for all $j=0,\dots,n-1$ in succession, we find that
+\[
+\lambda_j-c\sum_{i=0}^{n-2} \lambda_i = 0 \text{ for all }j.
+\]
+Therefore for all $j$, $\lambda_j=c\sum_{i=0}^{n-2} \lambda_i$.
+Then in particular all of the $\lambda_i$ are equal to some $\lambda \in k$ with $(1-c(n-1))\lambda = 0$.
+Since $c$ is generic, we can assume $(1-c(n-1)) \ne 0$, so then $\lambda=0$.
+Therefore $\lambda_j=0$ for all $j$; then the $f_i$ for $i=0,\dots,n-2$ are linearly independent as desired.
+
+We now suppose $p>2$.
+Then we have $[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne j$ (since $p > 2$).
 Since $c$ is generic, we can assume $\binom{c-1}{(p-1)/2} \ne 0$.
@@
 
-\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_i$ for $i=0,\dots,n-2$.  The $A/I$ is a complete intersection. 
+\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_i$ for $i=0,\dots,n-2$.  Then $A/I$ is a complete intersection. 
 \end{proposition}
@@
 
-We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$; then since $\sum_{i=0}^{n-1} x_i=0$ we have $\sum_{i=0}^{r-1} m_iy_i=0$.
-
-Then $g(z)=(1-y_iz)^{m_i}$. Recall that
+We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$. Then $g(z)=(1-y_iz)^{m_i}$. Recall that
 \[
@@
 \]
+Then we assume that $[z^p]\left(\frac{1}{1-y_iz}F(z)\right)=0$ for all $i=0,\dots,r-1$. We wish to show that $r=1$ and $y_0=0$.
 
-We assume that $y_i \ne 0$ for all $i$.
+We will assume that $\prod_i y_i \ne 0$ in order to derive a contradiction and show that one of the $y_i$ is $0$.
+Since $\sum_{i=0}^{n-1} x_i=0$ we also have $\sum_{i=0}^{r-1} m_iy_i=0$; this enables us to compute the derivative $F'(z)$, which is
+\[
+F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
+\]
+where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$.
 
-Define
+We will use a `residues by parts' argument; using the fact that the residue of an exact differential is zero, we will relate the coefficients of a power series to the coefficients of the derivative of that power series and derive a contradiction.
+Let
 \[
@@
 \]
-Recall that we showed
-\[
-F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
-\]
-where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$. We then see that
+We then see that
 \begin{align*}
@@
 \end{equation}
-Recall that the $b_i(z)$ are linearly independent; they also have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
+Recall that the $b_i(z)$ are linearly independent and have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
 \[
@@
 \]
-Then if we use the $\lambda_i^k$ in Equation~\ref{eq:lincomb}, we see that $[z^p](a(z)z^k)=[z^{p-k}]a(z)=0$ for $k=0,\dots,r-1$.
+Choosing these $\lambda_i^k$ in (\ref{eq:lincomb}), we see that $[z^p](a(z)z^k)=[z^{p-k}]a(z)=0$ for $k=0,\dots,r-1$.
 
-We will show that we must have $[z^0]a(z)=0$, a contradiction. Note that if $r > p$ then we have already shown that; therefore we assume $r \le p$.
+We will now derive from this that $[z^0]a(z)=0$, a contradiction. If $r > p$ then this has already been established, so it suffices to assume $r \le p$.
 
-For any integer $\ell$ we define the Laurent polynomial 
+For any integer $\ell$, define the Laurent polynomial 
 \[
@@
 \]
-Then we have
+Notice that
 \begin{align*}
@@
 \]
-The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-\ell-r$. We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$.
+The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-\ell-r$.
+We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$, so for $p-\ell-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$ is a linear combination of $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$.
+The latter coefficient is nonzero since $c$ is generic and none of the $y_i$ are $0$.
+Therefore $[z^\ell]a(z)$ is a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ when $\ell \le p-r$.
 
-Then as long as $p-\ell-r \ge 0$, which is true when $\ell \le p-r$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$ is a linear combination of $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$ - we can assume this is nonzero since $c$ is generic and none of the $y_i$ are $0$.
-Therefore we can write $[z^\ell]a(z)$ as a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ when $\ell \le p-r$.
+Since $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$, by induction starting with $\ell=p-r$ we find that $[z^\ell]a(z)=0$ for $\ell=p-r,p-r-1,\dots,0$.
+Therefore, $[z^0]a(z)=0$; a contradiction.
+We conclude that $y_i=0$ for some $i$.
 
-We see that since $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$, we can use induction starting with $\ell=p-r$ to show that $[z^\ell]a(z)=0$ for $\ell=p-r,p-r-1,\dots,0$.
-Therefore $[z^0]a(z)=0$; however, it is clear from the definition of $a(z)$ that this is not the case.
-Therefore we have a contradiction, so one of the $y_i$ is $0$.
+Assume without loss of generality that $y_{r-1}=0$. If $r>1$, we can repeat the same argument again with $y_0,\dots,y_{r-2}$.
 
-We can assume without loss of generality that $y_{r-1}=0$.
-Then if $r>1$, we can go through the same argument again with $y_0,\dots,y_{r-2}$.
-We are able to do this because our calculation of $F'(z)$ and $V(z)$ so that $z^p \mid V(z)$ relies only on the fact that $\sum m_iy_i=0$, which will still be true if we leave out $y_{r-1}=0$.
+We are able to do this because our calculation of $F'(z)$ and $V(z)$ so that $z^p \mid V(z)$ relies only on the fact that $\sum m_iy_i=0$.
+Since $y_{r-1}=0$, we see that $\sum_{i=0}^{r-2}m_iy_i=\sum_{i=0}^{r-1}m_iy_i=0$.
+Then since the $y_i$ are distinct, $\prod_{i=0}^{r-2} y_i \ne 0$, so both necessary assumptions are true.
 We will then find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
@@
 
+\subsection{Completing the proof}
+
 Using these propositions, we are able to prove the main theorem.
@@
 \begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by $[z^p]F_a(z)$ for the formal power series
+The maximal ideal $J$ is generated by $[z^p]F_i(z)$ for the formal power series
 \[
-F_a(z)=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $a=0,\dots,n-2$}.
+F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $i=0,\dots,n-2$}.
 \]
@@
 \begin{proof}
-It suffices to show that the $f_a$ generate the ideal $J$ and that $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+It suffices to show that the $f_i$ generate the ideal $J$ and that $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
 
-By Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ generators of degree $p$.
-It then must have Hilbert series $h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+By Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ linearly independent generators $f_i$ in degree $p$, so then its Hilbert series is $h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
 By Proposition~\ref{prop:ann}, the generators of $I$ are annihilated by the Dunkl operators, so $I \subseteq J$.
 
-By \cite[Proposition 3.4]{BC1}, we see that the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$.
-Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal $J$.
+By \cite[Proposition 3.4]{BC1}, the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients.
+Since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise; hence $h(t)=1$.
+Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$, completing the proof.
 \end{proof}

### 2015-05-17 formalwriteup.tex
section 1,2 edits

@@
 
-Given the symmetric group $S_n$, we let $\mathcal{S}$ be the set of reflections in $S_n$.
-Let $\h$ be the irreducible $(n-1)$-dimensional representation of $S_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$.
-For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.
+Given the symmetric group $S_n$, we see that $V=k^n$ is a representation of $S_n$ in a natural way (permutation of coordinates).
+Let $s_{ij}$ be the transposition permuting indices $i$ and $j$.
+We let $y_0,\dots,y_{n-1}$ be a basis of $V$; we define an $(n-1)$-dimensional representation $\h$ of $S_n$ as the span of $y_i-y_j$ for $i \ne j$.
+We choose a dual basis $x_0,\dots,x_{n-1}$ for $V^*$; the dual representation $\h^*$ of $\h$ can be realized as the quotient of $V^*$ by $x_0+\dots+x_{n-1}$.
+$S_n$ acts on $\h,\h^*$ by permuting the basis vectors in the natural way.
 
@@
 \begin{align*}
-[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s
+[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{k=0}^{n-1}\sum_{\ell=0}^{n-1} c\langle y_i,x_k-x_\ell \rangle\langle y_k-y_\ell,x_j\rangle s_{k\ell}
 \end{align*}
- for all $x,x' \in \h^*, y,y' \in \h$.
-We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
-We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite[Section 3.2]{EM}).
-
-In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$, so we restrict to $\hbar=0$ or $\hbar = 1$.
-
-\subsection{Representations of rational Cherednik algebras}
+ for all $0 \le i,j \le n-1$.
 
@@
 We refer to the polynomial representation as $A$; we can give this a $\mathbb{Z}$-grading in an obvious way.
-
-As described in \cite[Section 2.5]{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
-\begin{align*}
-\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(1,1) = 1.
-\end{align*}
-The quotient $A/J$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(\h)$.
-The {\it Hilbert series} $h_{A/J}(t)$ of $A/J$ is $\sum_{j=0}^\infty (\dim_k L_j)t^k$ where $L_j$ is the $j$-graded factor of $A/J$.
 
@@
 
- We call $c$ {\it generic} if we do not specify its value.
-We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$.
-We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $S_n$ of dimension $n-1$.
-We state our result for this case below:
+A statement holds for $c$ {\it generic} if it holds away from countably many values for $c$. Suppose that $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$.
 
  \newtheorem*{thm:main}{Theorem \ref{thm:main}}
-\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by $[z^p]F_i(z)$ for the formal power series
+\begin{thm:main} The irreducible quotient $A/J$ of the polynomial representation for $\HH_{\hbar,c}(\h)$ is a complete intersection with Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+The maximal ideal $J$ is has linearly independent generators $f_i=[z^p]F_i(z)$ for $0 \le i \le n-2$ with
 \[
@@
 \end{thm:main}
-
-%We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.
 
@@
 
+\subsection{PBW decomposition}
+
+We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
+We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite[Section 3.2]{EM}).
+
+In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$, so we restrict to $\hbar=0$ or $\hbar = 1$.
+
+As described in \cite[Section 2.5]{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
+\begin{align*}
+\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(1,1) = 1.
+\end{align*}
+The quotient $A/J$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(\h)$.
+The {\it Hilbert series} $h_{A/J}(t)$ of $A/J$ is $\sum_{j=0}^\infty (\dim_k L_j)t^k$ where $L_j$ is the degree $j$ subspace of $L$.
+
 \subsection{Dunkl operators}
@@
 \begin{align*}
-D_y(f) = \hbar \partial_y f  - \sum_{s \in \mathcal{S}} c \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f.
+D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{\ell=0}^{n-1} c \frac{ \langle y, x_k-x_\ell \rangle}{x_k-x_\ell} (1-s_{k\ell}). f.
 \end{align*}
-We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $S_n$ acts by permuting indices.
-Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.
+
  If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.
-
-For a transposition $s_{ij} \in S_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.
 
@@
 
-\begin{theorem}\label{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is generated by $[z^p]F_i(z)$ for the formal power series
+\begin{theorem}\label{thm:main} The irreducible quotient $A/J$ of the polynomial representation for $\HH_{\hbar,c}(\h)$ is a complete intersection with Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
+The maximal ideal $J$ is has linearly independent generators $f_i=[z^p]F_i(z)$ for $0 \le i \le n-2$ with
 \[

### 2015-05-18 formalwriteup.tex
Restructure intro and sections

@@
 \theoremstyle{definition}
-\newtheorem{theorem}[equation]{Theorem}
-\newtheorem{proposition}[equation]{Proposition}
-\newtheorem{lemma}[equation]{Lemma}
-\newtheorem{corollary}[equation]{Corollary}
-\newtheorem{conjecture}[equation]{Conjecture}
-\newtheorem{problem}[equation]{Problem}
-\newtheorem{remark}[equation]{Remark}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{problem}[theorem]{Problem}
+\newtheorem*{remark}{Remark}
 \newtheorem{definition}[equation]{Definition}
@@
 \renewcommand{\char}{\text{char}}
+\newcommand{\sspan}{\text{span}}
 
@@
 
-\subsection{Definitions}
+\subsection{The rational Cherednik algebra in positive characteristic}
 
-Given the symmetric group $S_n$, we see that $V=k^n$ is a representation of $S_n$ in a natural way (permutation of coordinates).
-Let $s_{ij}$ be the transposition permuting indices $i$ and $j$.
-We let $y_0,\dots,y_{n-1}$ be a basis of $V$; we define an $(n-1)$-dimensional representation $\h$ of $S_n$ as the span of $y_i-y_j$ for $i \ne j$.
-We choose a dual basis $x_0,\dots,x_{n-1}$ for $V^*$; the dual representation $\h^*$ of $\h$ can be realized as the quotient of $V^*$ by $x_0+\dots+x_{n-1}$.
-$S_n$ acts on $\h,\h^*$ by permuting the basis vectors in the natural way.
+Throughout this paper, we work over an algebraically closed field $k$ of characteristic $p > 0$ and fix $n$ so that $p \mid n$.
+Let $S_n$ denote the symmetric group on $n$ elements, $V = k^n$ its permutation representation, and $s_{ij} \in S_n$ the transposition permuting $i$ and $j$.
+Fix a basis $y_0,\ldots,y_{n-1}$ for $V$ and a dual basis $x_0, \ldots, x_{n-1}$ for $V^*$.
+Let $\h$ and $\h^*$ be the dual $(n - 1)$-dimensional $S_n$-representations which are subrepresentation and quotient of $V$ and $V^*$, respectively given by
+\[
+\h = \sspan\{y_i - y_j \mid i \neq j\} \text{ and } \h^* = V^*/(x_0 + \cdots + x_{n - 1}).
+\]
+The action of $S_n$ on $\h$ and $\h^*$ is given explicitly by natural permutation of basis vectors.
 
-Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$.
-We choose $\hbar,c \in k$.
-Then we define the {\it rational Cherednik algebra of type $A$} $\HH_{\hbar,c}(\h)$ as the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
+Fix constants $\hbar$ and $c$ in $k$.
+Denoting the tensor algebra of $\h \oplus \h^*$ by $T(\h \oplus \h^*)$, the \textit{type $A_{n - 1}$ rational Cherednik algebra} $\HH_{\hbar, c}(\h)$ is the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
 \begin{align*}
-[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{k=0}^{n-1}\sum_{\ell=0}^{n-1} c\langle y_i,x_k-x_\ell \rangle\langle y_k-y_\ell,x_j\rangle s_{k\ell}
+[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{k=0}^{n-1}\sum_{l=0}^{n-1} c\langle y_i,x_k-x_l \rangle\langle y_k-y_l,x_j\rangle s_{kl}
 \end{align*}
 for all $0 \le i,j \le n-1$.
+There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.
+In addition, $\HH_{\hbar, c}(\h)$ admits a PBW decomposition
+\[
+\HH_{\hbar,c}(\h) = \Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*).
+\]
+For any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)$ and $\HH_{\alpha\hbar,\alpha c}(\h)$ are isomorphic as algebras, so only the cases $\hbar = 0$ or $\hbar = 1$ need be considered.
+In this paper, we restrict our attention to $\hbar = 1$.
 
-We are concerned with the {\it polynomial representation} $\Sym(\h^*)$ of $\HH_{\hbar,c}$, which is a polynomial ring.
-We refer to the polynomial representation as $A$; we can give this a $\mathbb{Z}$-grading in an obvious way.
+\subsection{Polynomial representation of the rational Cherednik algebra}
 
-\subsection{Statement of the main results}
+The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.
+The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.
+The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
+\begin{align*}
+D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
+\end{align*}
+where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. In explicit terms, we have
+\[
+D_{y_i - y_j} = .
+\]
 
-For a formal power series or Laurent series $r(z)$, we write the coefficient of $z^\ell$ in $r$ as $[z^\ell]r(z)$.
+\todo[inline]{Fill this in}
 
-A statement holds for $c$ {\it generic} if it holds away from countably many values for $c$. Suppose that $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$.
+\subsection{Maximal ideal and irreducible quotient of the polynomial representation}
 
- \newtheorem*{thm:main}{Theorem \ref{thm:main}}
-\begin{thm:main} The irreducible quotient $A/J$ of the polynomial representation for $\HH_{\hbar,c}(\h)$ is a complete intersection with Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is has linearly independent generators $f_i=[z^p]F_i(z)$ for $0 \le i \le n-2$ with
+As described in \cite[Section 2.5]{BC1}, there is a contravariant form 
 \[
-F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $i=0,\dots,n-2$}.
+\beta_c: \Sym(\h^*) \otimes \Sym(\h) \to k
+\]
+defined by setting $\beta_c(1, 1) = 1$ and imposing for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in \Sym(\h)$ that
+\[
+\beta_c(xf,g)=\beta_c(f,xg) \qquad \text{ and } \qquad \beta_c(f,yg) = \beta_c(yf,g).
+\]
+Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J = \ker(\beta_c)$, and the quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.
+It inherits a $\ZZ_{\geq 0}$-grading from $A$, and we recall that its Hilbert series is
+\[
+h_L(t) = \sum_{j \geq 0} \dim L_j t^j,
+\]
+where $L_j$ is the degree $j$ subspace of $L$.
+
+\subsection{Statement of the main result}
+
+For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.  For $i = 0, \ldots, n - 2$, define the formal power series
+\[
+F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
+\]
+and consider the coefficients $f_i = [z^p] F_i(z)$.
+
+\newtheorem*{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
+For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$, and the irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
+\[
+h_L(t) = \left(\frac{1-t^p}{1-t}\right)^{n-1}.
 \]
 \end{thm:main}
+\begin{remark}
+In Theorem \ref{thm:main}, by generic $c$ we mean $c$ avoiding countably many values.
+\end{remark}
 
@@
 The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
-In the modular case $p \mid n$, for $p = 2$, it was shown in \cite[Theorem 5.1]{L} that the irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection and that the corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and a single element of degree $4$.
-In particular, this implies that the Hilbert series is
+In the modular case $p \mid n$, for $p = 2$, the polynomial representation associated to the $n$-dimensional permutation representation was studied.
+\begin{theorem}[{\cite[Theorem 5.1]{L}}] \label{thm:lian}
+The irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection with Hilbert series
 \[
@@
 \]
-It was conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
+The corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and one element of degree $4$. 
+\end{theorem} 
+It was further conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
 Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.
@@
 The remainder of this paper is organized as follows.
-In Section 2, we give some necessary background on rational Cherednik algebras and fix the form of the Dunkl operators which will be used in later computations.
-In Section 3, we check that our generators are singular vectors, show that they cut out a complete intersection, and finally deduce Theorem \ref{thm:main}.
+In Section 2, we check that the generators $f_i$ are linearly independent singular vectors.
+In Section 3, we show that they cut out a complete intersection.
+In Section 4, we put these facts together to conclude Theorem \ref{thm:main}.
 
@@
 
-\section{The rational Cherednik algebra}
-
-\subsection{PBW decomposition}
-
-We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$.
-We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite[Section 3.2]{EM}).
-
-In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$, so we restrict to $\hbar=0$ or $\hbar = 1$.
-
-As described in \cite[Section 2.5]{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
-\begin{align*}
-\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(1,1) = 1.
-\end{align*}
-The quotient $A/J$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(\h)$.
-The {\it Hilbert series} $h_{A/J}(t)$ of $A/J$ is $\sum_{j=0}^\infty (\dim_k L_j)t^k$ where $L_j$ is the degree $j$ subspace of $L$.
-
-\subsection{Dunkl operators}
-
-To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions.
-The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[S_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}.
-For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
-\begin{align*}
-D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{\ell=0}^{n-1} c \frac{ \langle y, x_k-x_\ell \rangle}{x_k-x_\ell} (1-s_{k\ell}). f.
-\end{align*}
-
- If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.
-
-\section{Proof of the main result}
-
-\subsection{An explicit construction of singular vectors}
+\section{An explicit construction of singular vectors}
 
@@
 
-\subsection{Complete interesction properties}
+\section{Complete interesction properties}
 
@@
 
-\subsection{Completing the proof}
+\section{The proof of the main result}
 

### 2015-05-18 formalwriteup.tex
Propogate some changes

@@
 \end{align*}
-where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. In explicit terms, we have
+where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, for 
 \[
-D_{y_i - y_j} = .
+D_i = ,
 \]
+we have $D_{y_i - y_j} = D_i - D_j$.
 
-\todo[inline]{Fill this in}
+\todo[inline]{Fill this in, $D_{y_i}$ is not well-defined because $y_i$ is not in $\h$}
 
@@
 In particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.
-
-However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$.
-
-Therefore the polynomials $b_i(z)$ are linearly independent as desired.
+However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
 \end{proof}
@@
 
-Using these propositions, we are able to prove the main theorem.
-
-\begin{theorem}\label{thm:main} The irreducible quotient $A/J$ of the polynomial representation for $\HH_{\hbar,c}(\h)$ is a complete intersection with Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-The maximal ideal $J$ is has linearly independent generators $f_i=[z^p]F_i(z)$ for $0 \le i \le n-2$ with
+\begin{theorem}\label{thm:main}
+For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$, and the irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
 \[
-F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right) \text{ for $i=0,\dots,n-2$}.
+h_L(t) = \left(\frac{1-t^p}{1-t}\right)^{n-1}.
 \]

### 2015-05-18 formalwriteup.tex
Update intro

@@
 We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient.
-Our methods are motivated by generalizing from characteristic $0$ to characteristic $p$.
+Our methods are motivated by taking characteristic $p$ analogues of existing characteristic $0$ results.
 \end{abstract}
@@
 Our study is motivated by previous work on the representation theory of the type $A$ rational Cherednik algebra in both characteristic $0$ and $p$.
-The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
+The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and some properties of the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
 In the modular case $p \mid n$, for $p = 2$, the polynomial representation associated to the $n$-dimensional permutation representation was studied.

### 2015-05-18 formalwriteup.tex
Clean up proof of main result

@@
 \begin{proof}
-It suffices to show that the $f_i$ generate the ideal $J$ and that $A/J$ has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-
-By Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ linearly independent generators $f_i$ in degree $p$, so then its Hilbert series is $h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}$.
-By Proposition~\ref{prop:ann}, the generators of $I$ are annihilated by the Dunkl operators, so $I \subseteq J$.
-
-By \cite[Proposition 3.4]{BC1}, the Hilbert series of $A/J$ is $\left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients.
-Since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise; hence $h(t)=1$.
-Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$, completing the proof.
+By \cite[Proposition 3.4]{BC1}, the Hilbert series of $L$ is 
+\[
+h_L(t) = \left(\frac{1-t^p}{1-t}\right)^{n-1}h(t^p)
+\]
+for some polynomial $h(t)$ with nonnegative integer coefficients.
+On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ linearly independent generators $f_i$ in degree $p$.
+Therefore, its Hilbert series is
+\[
+h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}.
+\]
+By Proposition~\ref{prop:ann}, the generators $f_i$ of $I$ are singular vectors, so $I \subseteq J$, implying that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise.
+We conclude that $h(t) = 1$, hence $h_{A/I}(t)=h_{A/J}(t)$ and $I=J$, completing the proof.
 \end{proof}

### 2015-05-18 formalwriteup.tex
Move singular vector

@@
 \]
-Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J = \ker(\beta_c)$, and the quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.
-It inherits a $\ZZ_{\geq 0}$-grading from $A$, and we recall that its Hilbert series is
+Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J = \ker(\beta_c)$.
+By the definition of $\beta_c$, $J$ is generated by homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.
+Such $f$ are known as \textit{singular vectors}.
+
+The quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.  It inherits a $\ZZ_{\geq 0}$-grading from $A$, and we recall that its Hilbert series is 
 \[
@@
 \[
-F_i(z)=\frac{1}{1-x_iz} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
+F_i(z)=\frac{1}{1-x_iz} \left(\sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
 \]
-and consider the coefficients $f_i = [z^p] F_i(z)$.
+where $\binom{c}{k} = \frac{c (c - 1) \cdots (c - k + 1)}{k!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.
 
@@
 
-We let $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z)$ be the formal power series in $z$ defined by
-\[
-F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).
-\]
-where $\binom{c}{k}=\frac{c(c-1)\dots(c-k+1)}{k!}$. 
-Let $F_i(z)$ for $i=0,\dots,n-1$ be $\frac{F(z)}{1-x_iz}$ and $f_i=[z^p]F_i(z)$. The $f_i$ will be the generators of the maximal ideal $J$.
-
-Because of the definition of the contravariant form $\beta_c$, showing that an element $f$ of $A$ is in the kernel of $\beta_c$ is equivalent to showing that the Dunkl operators corresponding to the basis elements of $\h$ annihilate $f$.
-
-\begin{proposition}\label{prop:ann} The elements $f_i$ for $i=0,\dots,n-1$ are annihilated by $D_i-D_j$ for all $i \ne j$.
+Define $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right)$ so that $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.
+We now show that $f_i$ are singular vectors.
+\begin{proposition}\label{prop:ann} 
+The elements $f_i$ for $i=0,\dots,n-1$ singular vectors in $A$.
 \end{proposition}
-
 \begin{proof}
+We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.
 

### 2015-05-18 formalwriteup.tex
Convert vand to Lemma

@@
 
-\begin{proposition}\label{prop:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
-\end{proposition}
+\begin{lemma}\label{lem:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
+\end{lemma}
 \begin{proof} 
@@
 
-Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Proposition~\ref{prop:vand} we see that the polynomials $b_i(z)$ are linearly independent.
+Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Lemma~\ref{lem:vand} we see that the polynomials $b_i(z)$ are linearly independent.
 

### 2015-05-18 formalwriteup.tex
Define I, formatting

@@
 \maketitle
+\setcounter{tocdepth}{1}
+\tableofcontents
 
@@
 %&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
+&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
 \end{align*}
@@
 %&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
-&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.\\
+&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.
 \end{align*}
@@
 &=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
-&=\frac{z}{1-x_iz}F_0(z).\\
+&=\frac{z}{1-x_iz}F_0(z).
 \end{align*}
@@
 &=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
-&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).\\
+&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).
 \end{align*}
@@
 &=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
-&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
+&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).
 \end{align*}
@@
 &=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
-&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.\\
+&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
 \end{align*}
@@
 
-\begin{proposition}\label{prop:linind} The $f_i$ for $i=0,\dots,n-2$ are linearly independent homogeneous polynomials of degree $p$.
+\begin{proposition}\label{prop:linind} The $f_i$ for $i=0,\dots,n-2$ are linearly independent degree $p$ homogeneous polynomials.
 \end{proposition}
@@
 
-\section{Complete interesction properties}
+\section{Complete intersection properties}
+
+Let the vectors $f_i \in A$ generate an ideal $I \subset A$.  We will now show that $A/I$ is a complete intersection.
 
@@
 
-\begin{proposition}\label{prop:ci} Let $I \subseteq A$ be the ideal generated by $f_i$ for $i=0,\dots,n-2$.  Then $A/I$ is a complete intersection. 
+\begin{proposition}\label{prop:ci}
+The quotient $A/I$ is a complete intersection. 
 \end{proposition}
-
 \begin{proof} 
-
 We will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
@@
 
-\section{The proof of the main result}
+\section{Proof of the main result}
 

### 2015-05-18 formalwriteup.tex
\ell -> l

@@
 
-Then we see that for $0 \le \ell \le p$ we have
+Then we see that for $0 \le l \le p$ we have
 \[
-[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.
+[z^l](z^2V(z))=[z^l]G_0(z)=[z^l]G_1(z)=0.
 \]
@@
 \[
-[z^\ell](G_1(z)-G_0(z)+z^2V(z))=0.
+[z^l](G_1(z)-G_0(z)+z^2V(z))=0.
 \]
-Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^\ell](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le \ell \le p$, so 
+Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^l](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le l \le p$, so 
 \[
@@
 Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$.
-In particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.
+In particular for $l=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^l=0$.
 However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
@@
 \]
-where $[z^\ell]V(z)=0$ for $0 \le \ell \le p$.
+where $[z^l]V(z)=0$ for $0 \le l \le p$.
 
@@
 \end{align*}
-Since $[z^\ell]V(z)=0$ for $0 \le \ell \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$. Therefore
+Since $[z^l]V(z)=0$ for $0 \le l \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$. Therefore
 \[
@@
 
-For any integer $\ell$, define the Laurent polynomial 
+For any integer $l$, define the Laurent polynomial 
 \[
-h_\ell(z)=z^{-\ell-r}\prod_i(1-y_iz).
+h_l(z)=z^{-l-r}\prod_i(1-y_iz).
 \]
@@
 \begin{align*}
-\frac{d}{dz}( h_\ell(z) a(z)) &= -(l + r)z^{-1} h_\ell(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_\ell(z) a(z) + h_\ell(z) a'(z) \\
-&=  -(\ell + r)z^{-1} h_\ell(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_\ell(z) a(z) - h_\ell(z) \sum_j \frac{(m_j c - 1)y_i}{1 - y_ijz} a(z)  + z^ph_\ell(z) b(z)\\
-&= -(\ell + r)z^{-1} h_\ell(z) a(z) - \sum_i \frac{y_im_i c}{1 - y_iz} h_\ell(z) a(z) + z^ph_\ell(z) b(z)\\
-&= -\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z) a(z) + z^ph_\ell(z) b(z).
+\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_l(z) a(z) + h_l(z) a'(z) \\
+&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)y_i}{1 - y_ijz} a(z)  + z^ph_l(z) b(z)\\
+&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_im_i c}{1 - y_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
+&= -\left((l + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
 \end{align*}
@@
 \[
--\left((\ell + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_\ell(z)
+-\left((l + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_l(z)
 \]
@@
 \[
-- z^{-l-r-1} \left(\ell + r + \sum_i y_i m_i c\right) = - z^{-\ell-r-1}(\ell+ r)
+- z^{-l-r-1} \left(l + r + \sum_i y_i m_i c\right) = - z^{-l-r-1}(l+ r)
 \]
@@
 \[
-- z^{-\ell - 1} (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right).
+- z^{-l - 1} (-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right).
 \]
-The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-\ell-r$.
-We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$, so for $p-\ell-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$ is a linear combination of $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$.
+The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$.
+We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$, so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right)$.
 The latter coefficient is nonzero since $c$ is generic and none of the $y_i$ are $0$.
-Therefore $[z^\ell]a(z)$ is a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ when $\ell \le p-r$.
+Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ when $l \le p-r$.
 
-Since $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$, by induction starting with $\ell=p-r$ we find that $[z^\ell]a(z)=0$ for $\ell=p-r,p-r-1,\dots,0$.
+Since $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$, by induction starting with $l=p-r$ we find that $[z^l]a(z)=0$ for $l=p-r,p-r-1,\dots,0$.
 Therefore, $[z^0]a(z)=0$; a contradiction.

### 2015-05-18 formalwriteup.tex
Add todo

@@
 \[
-D_i = ,
+D_i = 
 \]
@@
 We now show that $f_i$ are singular vectors.
+
+\todo[inline]{Break up the proof into lemmas, e.g. for the value of $\frac{\partial F}{\partial z}$}
+
 \begin{proposition}\label{prop:ann} 
-The elements $f_i$ for $i=0,\dots,n-1$ singular vectors in $A$.
+The elements $f_i$ for $i=0,\dots,n-1$ are singular vectors in $A$.
 \end{proposition}
@@
 
+\todo[inline]{Split computations out into some lemmas on computations of $F'(z)$ and $V(z)$ which explicitly mention the hypotheses that $\sum_i m_i y_i = 0$.}
+
 \begin{proposition}\label{prop:ci}

### 2015-05-19 formalwriteup.tex
added lemmas in sections 2/3

@@
 The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.
+In particular, for any $f \in A$ we can take a partial derivative $\frac{\partial f}{\partial x_i}$ by noting that $A=k[x_0,\dots,x_{n-2}]$ with $x_{n-1}=-x_0-\dots-x_{n-2}$; then we can write $f$ as a polynomial and take its partial derivative by any $x_i$ with $0 \le i \le n-2$.
+
 The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.
@@
 \[
-D_i = 
+D_i = \hbar\frac{\partial f}{\partial x_i} -c \sum_{k \ne i} \frac{(1-s_{ki})f}{x_i-x_k}
 \]
@@
 
-\begin{proposition}\label{prop:ann} 
-The elements $f_i$ for $i=0,\dots,n-1$ are singular vectors in $A$.
-\end{proposition}
+We begin by computing some partial derivatives of $F$ which will be useful for computing the action of the Dunkl operators.
+
+\begin{lemma}\label{lem:dFdz} We have
+\[
+F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z)
+\]
+such that $V(z)$ is a power series with $[z^l]V(z)=0$ for $l=0,\dots,p-1$. 
+\end{lemma}
+
 \begin{proof}
-We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.
+We see easily that 
+\[
+\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
+\]
+We now consider $\frac{\partial F}{\partial z}$. We compute
+\begin{align*}
+\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
+&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+\end{align*}
+We define 
+\[
+V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+\]
+It is then clear that 
+\[
+F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z).
+\]
+Then it remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$. To show this, we need only show that $V(z)=z^pv(z)$ for some power series $v(z)$.
 
-We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$.
-It therefore suffices to consider the action of the Dunkl operators on $f_0$.
-We note that the Dunkl operators $D_i-D_j$ for all $i \ne j$ are spanned by $D_i-D_0$ for $0<i \le n-1$; then because $f_0$ is symmetric in the $x_i$ with $i > 0$, we see that it suffices to consider the action of $D_1-D_0$ on $f_0$ to show that the $f_i$ are annihilated by $D_i \ne D_j$ for all $i \ne j$.
+We consider the expansion of $g(z)$; this is $g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_i)+\dots+z^ne_n(x_i)$ where $e_2,\dots,e_n$ are polynomials in the $x_i$.
+In particular we note that $\sum_i x_i=0$ by hypothesis, so $z^2 \mid g(z)-1$.
+
+Then by the definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$.
+Since $p \ge 2$, it is clear that $z^p \mid V(z)$, so we can write $V(z)=z^pv(z)$ for some power series $v(z)$ as desired.
+\end{proof}
+
+\begin{lemma}\label{lem:dFdxi} For any $0 \le i < n-1$ we have 
+\[
+\frac{\partial F}{\partial x_i} = G_i(z) - \left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_iz}\right)F(z)
+\]
+such that $G_i(z)$ is a power series with $[z^l]G_i(z)=0$ for $l=0,\dots,p$. 
+\end{lemma}
+
+\begin{proof}
 
@@
 \]
-We recall that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 
+Then we see that for all $0 \le i < n-1$ we have 
 \begin{align*}
@@
 \]
-We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. 
+
+Then it remains only to show that $[z^l]G_i(z)=0$ for $l=0,\dots,p$. To show this, we need only show that $G_i(z)=z^{p+1}g_i(z)$ for some power series $v(z)$.
+
+We consider the expansion of $g(z)$; this is $g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_i)+\dots+z^ne_n(x_i)$ where $e_2,\dots,e_n$ are polynomials in the $x_i$.
+In particular we note that $x_{n-1}=-x_0-\dots-x_{n-2}$ by hypothesis, so $z^2 \mid g(z)-1$.
+
+Then by the definition of $G_i(z)$, we see that $z(g-1)^{p-1} \mid G_i(z)$, so $z^{2p-1} \mid V(z)$.
+Since $p \ge 2$, it is clear that $z^{p+1} \mid G_i(z)$, so we can write $G_i(z)=z^{p+1}g_i(z)$ for some power series $g_i(z)$ as desired.
+
+\end{proof}
+
+\begin{proposition}\label{prop:ann} 
+The elements $f_i$ for $i=0,\dots,n-1$ are singular vectors in $A$.
+\end{proposition}
+\begin{proof}
+We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.
+
+We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$.
+It therefore suffices to consider the action of the Dunkl operators on $f_0$.
+We note that the Dunkl operators $D_i-D_j$ for all $i \ne j$ are spanned by $D_i-D_0$ for $0<i \le n-1$; then because $f_0$ is symmetric in the $x_i$ with $i > 0$, we see that it suffices to consider the action of $D_1-D_0$ on $f_0$ to show that the $f_i$ are annihilated by $D_i \ne D_j$ for all $i \ne j$.
+
+By Lemma~\ref{lem:dFdxi} we note that for $i=0,1$ we have $\frac{\partial F}{\partial x_i} = G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z)$ for power series $G_i(z)$ with $[z^l]G_i(z)=0$ for $l=0,\dots,p$.
+
+We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. We compute
 \begin{align*}
@@
 
-We see easily that 
-\[
-\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
-\]
-We now consider $\frac{\partial F}{\partial z}$. We compute
-\begin{align*}
-\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
-\end{align*}
-We define 
-\[
-V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
-\]
-Then we see that 
+We recall by Lemma~\ref{lem:dFdz} that
 \[
@@
 \]
+where $[z^l]V(z)=0$ for $l=0,\dots,p-1$.
+
 From this it follows that
@@
 \end{align*}
-We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$.
-We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$.
-Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$.
-Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$.
-(We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)
 
-Then we see that for $0 \le l \le p$ we have
-\[
-[z^l](z^2V(z))=[z^l]G_0(z)=[z^l]G_1(z)=0.
-\]
-Then we also have
-\[
-[z^l](G_1(z)-G_0(z)+z^2V(z))=0.
-\]
-Then $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is $0$ since it is a linear combination of $[z^l](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le l \le p$, so 
+We note that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le l \le p$.
+This means that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l]G_0(z)$ for $0 \le l \le p$, $[z^l]G_1(z)$ for $0 \le l \le p$, and $[z^l]V(z)$ for $0 \le l \le p-2$.
+By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi} we recall that the coefficients of $G_i(z),V(z)$ under consideration are all $0$.
+This implies that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)=0$.
+Therefore
 \[
@@
 
-\begin{proposition}\label{prop:ci}
-The quotient $A/I$ is a complete intersection. 
-\end{proposition}
+To show that $A/I$ is a complete intersection, we will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
+We will use a `residues by parts' argument; using the fact that the residue of an exact differential is zero, we will relate the coefficients of a power series to the coefficients of the derivative of that power series and derive a contradiction.
+To show this we must consider the derivatives of some power series in $z$ (including $F(z)$) with coefficients from $k$ rather than coefficients from $A$.
+
+\begin{lemma}\label{lem:dFdz2}
+For any $y_0,\dots,y_{r-1}$ distinct elements of $k$ with $m_i$ positive integers such that $\sum_i m_iy_i=0$, if we let $g(z)=\prod_{i=0}^{r-1} (1-y_iz)^{m_i}$ and $F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k$, then
+\[
+F'(z)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
+\]
+where $[z^l]V(z)=0$ for $0 \le l \le p-1$. 
+\end{lemma}
 \begin{proof}
-We will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
+The computation proceeds essentially as it did for Lemma~\ref{lem:dFdz}.
 
-We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$. Then $g(z)=(1-y_iz)^{m_i}$. Recall that
+We see easily that 
 \[
-F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.
+\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-m_jy_j}{1-y_jz}.
 \]
-Then we assume that $[z^p]\left(\frac{1}{1-y_iz}F(z)\right)=0$ for all $i=0,\dots,r-1$. We wish to show that $r=1$ and $y_0=0$.
+We now consider $\frac{\partial F}{\partial z}$. We compute
+\begin{align*}
+\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
+&=\left(\sum_j\frac{-m_jy_j}{1-y_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+&=\left(\sum_j\frac{-m_jy_j}{1-y_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
+&=\left(\sum_j \frac{-m_jy_j}{1-y_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=\left(\sum_j \frac{-cm_jy_j}{1-y_jz}\right)F(z)+\left(\sum_j \frac{-m_jy_j}{1-y_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+\end{align*}
+We define 
+\[
+V(z)=\left(\sum_j \frac{-m_jy_j}{1-y_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+\]
+It is then clear that 
+\[
+F'(z)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right).
+\]
+Then it remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$. To show this, we need only show that $V(z)=z^pv(z)$ for some power series $v(z)$.
 
-We will assume that $\prod_i y_i \ne 0$ in order to derive a contradiction and show that one of the $y_i$ is $0$.
-Since $\sum_{i=0}^{n-1} x_i=0$ we also have $\sum_{i=0}^{r-1} m_iy_i=0$; this enables us to compute the derivative $F'(z)$, which is
-\[
-F'(z)=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}F(z)\right)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
-\]
-where $[z^l]V(z)=0$ for $0 \le l \le p$.
+We consider the expansion of $g(z)$; this is $g(z)=\prod_j (1-y_jz)^{m_j} = 1-z\left(\sum_i m_iy_i \right)+z^2e_2(y_i)+\dots+z^ne_n(y_i)$ where $e_2,\dots,e_n$ are polynomials in the $y_i$.
+In particular we note that $\sum_i m_iy_i=0$ by hypothesis, so $z^2 \mid g(z)-1$.
 
-We will use a `residues by parts' argument; using the fact that the residue of an exact differential is zero, we will relate the coefficients of a power series to the coefficients of the derivative of that power series and derive a contradiction.
-Let
+Then by the definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$.
+Since $p \ge 2$, it is clear that $z^p \mid V(z)$, so we can write $V(z)=z^pv(z)$ for some power series $v(z)$ as desired.
+\end{proof}
+
+\begin{lemma} \label{lem:resbyparts}
+For any $y_0,\dots,y_{r-1}$ distinct elements of $k$ such that $\prod_i y_i \ne 0$ and $m_i$ positive integers such that $\sum_i m_iy_i=0$, define $g(z), F(z)$ as in Lemma~\ref{lem:dFdz2}. Let 
 \[
 a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).
+\].
+Then we have
+\begin{enumerate}
+\item $a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)$ for some power series $b(z)$;
+\item For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$.\end{enumerate}
+
+\end{lemma}
+
+\begin{proof} We begin by computing $a'(z)$. By Lemma~\ref{lem:dFdz2} we have
+\[
+F'(z)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
 \]
-We then see that
+where $[z^l]V(z)=0$ for $0 \le l \le p-1$. 
+We now compute
 \begin{align*}
@@
 \end{align*}
-Since $[z^l]V(z)=0$ for $0 \le l \le p$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$. Therefore
+Since $[z^l]V(z)=0$ for $0 \le l \le p-1$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$. Therefore
 \[
@@
 for some power series $b(z)$.
-
-Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Lemma~\ref{lem:vand} we see that the polynomials $b_i(z)$ are linearly independent.
-
-Note that for any $i$, $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$. Then in particular, we have 
-\[
-[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0
-\]
-Therefore for any $\lambda_i \in k$, we have
-\begin{equation}\label{eq:lincomb}
-\sum_{i=0}^{r-1} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=0}^{r-1}\lambda_ib_i(z)\right)=0.
-\end{equation}
-Recall that the $b_i(z)$ are linearly independent and have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
-\[
-\sum_i\lambda_i^kb_i(z)=z^k.
-\]
-Choosing these $\lambda_i^k$ in (\ref{eq:lincomb}), we see that $[z^p](a(z)z^k)=[z^{p-k}]a(z)=0$ for $k=0,\dots,r-1$.
-
-We will now derive from this that $[z^0]a(z)=0$, a contradiction. If $r > p$ then this has already been established, so it suffices to assume $r \le p$.
 
@@
 We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$, so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right)$.
-The latter coefficient is nonzero since $c$ is generic and none of the $y_i$ are $0$.
+The latter coefficient is nonzero since $c$ is generic and $\prod_i y_i \ne 0$.
 Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ when $l \le p-r$.
 
-Since $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$, by induction starting with $l=p-r$ we find that $[z^l]a(z)=0$ for $l=p-r,p-r-1,\dots,0$.
+\end{proof}
+
+\begin{proposition}\label{prop:ci}
+The quotient $A/I$ is a complete intersection. 
+\end{proposition}
+\begin{proof} 
+We will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
+
+We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$. Then $g(z)=(1-y_iz)^{m_i}$. Recall that
+\[
+F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.
+\]
+Then we assume that $[z^p]\left(\frac{1}{1-y_iz}F(z)\right)=0$ for all $i=0,\dots,r-1$. We wish to show that $r=1$ and $y_0=0$.
+
+We will assume that $\prod_i y_i \ne 0$ in order to derive a contradiction and show that one of the $y_i$ is $0$. 
+Let
+\[
+a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z)
+\]
+as in Lemma~\ref{lem:resbyparts}.
+
+Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Lemma~\ref{lem:vand} we see that the polynomials $b_i(z)$ are linearly independent.
+
+Note that for any $i$, $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$. Then in particular, we have 
+\[
+[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0
+\]
+Therefore for any $\lambda_i \in k$, we have
+\begin{equation}\label{eq:lincomb}
+\sum_{i=0}^{r-1} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=0}^{r-1}\lambda_ib_i(z)\right)=0.
+\end{equation}
+Recall that the $b_i(z)$ are linearly independent and have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
+\[
+\sum_i\lambda_i^kb_i(z)=z^k.
+\]
+Choosing these $\lambda_i^k$ in (\ref{eq:lincomb}), we see that $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$.
+Then by repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$, we find that $[z^l]a(z)=0$ for $l=p-r,p-r-1,\dots,0$.
 Therefore, $[z^0]a(z)=0$; a contradiction.
@@
 
-Assume without loss of generality that $y_{r-1}=0$. If $r>1$, we can repeat the same argument again with $y_0,\dots,y_{r-2}$.
-
-We are able to do this because our calculation of $F'(z)$ and $V(z)$ so that $z^p \mid V(z)$ relies only on the fact that $\sum m_iy_i=0$.
-Since $y_{r-1}=0$, we see that $\sum_{i=0}^{r-2}m_iy_i=\sum_{i=0}^{r-1}m_iy_i=0$.
-Then since the $y_i$ are distinct, $\prod_{i=0}^{r-2} y_i \ne 0$, so both necessary assumptions are true.
-We will then find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
+Assume without loss of generality that $y_{r-1}=0$.
+If $r>1$, then we note that since the $y_i$ were distinct that $\prod_{i=0}^{r-2} y_i \ne 0$ and $\sum_{i=0}^{r-1} m_iy_i = \sum_{i=0}^{r-2} m_iy_i=0$; therefore we are still able to apply Lemma~\ref{lem:resbyparts} to $y_0,\dots,y_{r-2}$.
+By redefining the $b_i(z)$ appropriately and repeating the argument above, we find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
 Therefore we must have $r=1$ and $y_0=0$.

### 2015-05-19 formalwriteup.tex
Line edits, Dunkl

@@
 The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.
-In particular, for any $f \in A$ we can take a partial derivative $\frac{\partial f}{\partial x_i}$ by noting that $A=k[x_0,\dots,x_{n-2}]$ with $x_{n-1}=-x_0-\dots-x_{n-2}$; then we can write $f$ as a polynomial and take its partial derivative by any $x_i$ with $0 \le i \le n-2$.
-
 The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.
@@
 \end{align*}
-where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, for 
+where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, we have  
 \[
-D_i = \hbar\frac{\partial f}{\partial x_i} -c \sum_{k \ne i} \frac{(1-s_{ki})f}{x_i-x_k}
+D_{y_i - y_j} = 
 \]
-we have $D_{y_i - y_j} = D_i - D_j$.
 
-\todo[inline]{Fill this in, $D_{y_i}$ is not well-defined because $y_i$ is not in $\h$}
+\todo[inline]{Remove $D_i$ and replace the quantity above}
 
@@
 %&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
+&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\\
 %&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
@@
 \]
-
-Then it remains only to show that $[z^l]G_i(z)=0$ for $l=0,\dots,p$. To show this, we need only show that $G_i(z)=z^{p+1}g_i(z)$ for some power series $v(z)$.
-
-We consider the expansion of $g(z)$; this is $g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_i)+\dots+z^ne_n(x_i)$ where $e_2,\dots,e_n$ are polynomials in the $x_i$.
-In particular we note that $x_{n-1}=-x_0-\dots-x_{n-2}$ by hypothesis, so $z^2 \mid g(z)-1$.
-
-Then by the definition of $G_i(z)$, we see that $z(g-1)^{p-1} \mid G_i(z)$, so $z^{2p-1} \mid V(z)$.
-Since $p \ge 2$, it is clear that $z^{p+1} \mid G_i(z)$, so we can write $G_i(z)=z^{p+1}g_i(z)$ for some power series $g_i(z)$ as desired.
-
+It remains only to show that $[z^l]G_i(z)=0$ for $l=0,\dots,p$. To show this, we need only show that $G_i(z)=z^{p+1}g_i(z)$ for some power series $v(z)$.  Consider the expansion 
+\[
+g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_0, \ldots, x_{n-1})+\dots+z^ne_n(x_0, \ldots, x_{n - 1}).
+\]
+Recall that $\sum_i x_i = 0$, so $z^2 \mid g(z)-1$.
+By definition of $G_i(z)$, we see that $z(g-1)^{p-1} \mid G_i(z)$, so $z^{2p-1} \mid V(z)$.
+Since $p \ge 2$, this implies $z^{p+1} \mid G_i(z)$, giving the desired.
 \end{proof}
@@
 \item $a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)$ for some power series $b(z)$;
-\item For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$.\end{enumerate}
-
+\item For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$.
+\end{enumerate}
 \end{lemma}
-
 \begin{proof} We begin by computing $a'(z)$. By Lemma~\ref{lem:dFdz2} we have
@@
 Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ when $l \le p-r$.
-
 \end{proof}

### 2015-05-19 formalwriteup.tex
Line edits to CI

@@
 
-Let the vectors $f_i \in A$ generate an ideal $I \subset A$.  We will now show that $A/I$ is a complete intersection.
+Let the vectors $f_i \in A$ generate an ideal $I \subset A$.  We will now show that $A/I$ is a complete intersection.  For this, we require some preparatory computations.
+
+\subsection{Derivative computations}
 
@@
 \begin{lemma} \label{lem:resbyparts}
-For any $y_0,\dots,y_{r-1}$ distinct elements of $k$ such that $\prod_i y_i \ne 0$ and $m_i$ positive integers such that $\sum_i m_iy_i=0$, define $g(z), F(z)$ as in Lemma~\ref{lem:dFdz2}. Let 
+Let $y_0,\dots,y_{r-1}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_iy_i=0$.  For $F(z)$ as in Lemma \ref{lem:dFdz2}, let $a(z)$ be the formal power series
 \[
 a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).
-\].
-Then we have
-\begin{enumerate}
-\item $a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)$ for some power series $b(z)$;
-\item For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$.
-\end{enumerate}
+\]
+For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
 \end{lemma}
-\begin{proof} We begin by computing $a'(z)$. By Lemma~\ref{lem:dFdz2} we have
+\begin{proof} We begin by showing that 
+\[
+a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)
+\]
+for some formal power series $b(z)$. By Lemma~\ref{lem:dFdz2} we have
 \[
@@
 &=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F'(z)+\sum_{j=0}^{r-1}\frac{y_j}{(1-y_jz)\prod_{i=0}^{r-1}(1-y_iz)}F(z)\\
-&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}\left(V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}a(z)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\left(\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)\right).
+&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}\left(V(z)+\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
+&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}+\sum_j \frac{-cm_jy_j}{1-y_jz}a(z)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
+&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z).
 \end{align*}
-Since $[z^l]V(z)=0$ for $0 \le l \le p-1$ we see that $\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)$ for some power series $b(z)$. Therefore
+Since $[z^l]V(z)=0$ for $0 \le l \le p-1$ we see that 
 \[
-a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)
+\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)
 \]
-for some power series $b(z)$.
+for some power series $b(z)$, giving the claim.
 
-For any integer $l$, define the Laurent polynomial 
+Now, for any integer $l$, define the Laurent polynomial 
 \[
@@
 The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$.
-We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$, so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right)$.
-The latter coefficient is nonzero since $c$ is generic and $\prod_i y_i \ne 0$.
-Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ when $l \le p-r$.
+We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$, so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient
+\[
+(-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right),
+\]
+which is nonzero for $c$ generic and $\prod_i y_i \ne 0$. Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
 \end{proof}
+
+\subsection{Complete intersection property}
+
+We are now ready to show that $A/I$ is a complete intersection.
 
@@
 \begin{proof}
-We will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
+It suffices to show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
+Suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$, where $y_i$ occurs with multiplicity $m_i>0$ so that $g(z)=(1-y_iz)^{m_i}$.
+In these terms, we have that
+\[
+[z^p]\left(\frac{1}{1-y_iz}F(z)\right)= 0
+\]
+for $i = 0, \ldots, r - 1$ and wish to show that $r=1$ and $y_0=0$.
 
-We suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$ with multiplicity $m_i>0$. Then $g(z)=(1-y_iz)^{m_i}$. Recall that
-\[
-F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.
-\]
-Then we assume that $[z^p]\left(\frac{1}{1-y_iz}F(z)\right)=0$ for all $i=0,\dots,r-1$. We wish to show that $r=1$ and $y_0=0$.
-
-We will assume that $\prod_i y_i \ne 0$ in order to derive a contradiction and show that one of the $y_i$ is $0$. 
-Let
+We first claim that at least one $y_i$ is $0$. Suppose for the sake of contradiction that $\prod_i y_i \ne 0$.  Then let
 \[
@@
 \]
-as in Lemma~\ref{lem:resbyparts}.
-
-Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Lemma~\ref{lem:vand} we see that the polynomials $b_i(z)$ are linearly independent.
-
-Note that for any $i$, $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$. Then in particular, we have 
+as in Lemma~\ref{lem:resbyparts}.  Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$ so in particular 
 \[
-[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0
+[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0.
 \]
@@
 \end{equation}
-Recall that the $b_i(z)$ are linearly independent and have degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
+By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
 \[
@@
 \]
-Choosing these $\lambda_i^k$ in (\ref{eq:lincomb}), we see that $[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0$.
-Then by repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$, we find that $[z^l]a(z)=0$ for $l=p-r,p-r-1,\dots,0$.
-Therefore, $[z^0]a(z)=0$; a contradiction.
-We conclude that $y_i=0$ for some $i$.
+Choosing these $\lambda_i^k$ in (\ref{eq:lincomb}), we see that
+\[
+[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0.
+\]
+By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$, we find that 
+\[
+[z^l]a(z)=0 \text{ for $l=p-r,p-r-1,\dots,0$}.
+\]
+This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $y_i=0$ for some $i$.
 
-Assume without loss of generality that $y_{r-1}=0$.
-If $r>1$, then we note that since the $y_i$ were distinct that $\prod_{i=0}^{r-2} y_i \ne 0$ and $\sum_{i=0}^{r-1} m_iy_i = \sum_{i=0}^{r-2} m_iy_i=0$; therefore we are still able to apply Lemma~\ref{lem:resbyparts} to $y_0,\dots,y_{r-2}$.
-By redefining the $b_i(z)$ appropriately and repeating the argument above, we find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct.
-Therefore we must have $r=1$ and $y_0=0$.
+Now, suppose without loss of generality that $y_{r-1}=0$.
+If $r = 1$, we are done.
+Otherwise, we have $\sum_{i=0}^{r-2} m_iy_i = \sum_{i=0}^{r-1} m_iy_i = 0$ and because the $y_i$ are distinct we see that $\prod_{i=0}^{r-2} y_i \ne 0$.
+Therefore, we may apply Lemma~\ref{lem:resbyparts} and repeat the argument above with $y_0, \ldots, y_{r - 2}$.
+We find that at least one of the $y_i$ with $i < r-1$ is $0$, a contradiction since the $y_i$ are distinct.
+Therefore, we must have $r=1$ and $y_0=0$, concluding the proof.
 \end{proof}

### 2015-05-19 formalwriteup.tex
Add commentary for CI

@@
 
-Let the vectors $f_i \in A$ generate an ideal $I \subset A$.  We will now show that $A/I$ is a complete intersection.  For this, we require some preparatory computations.
+Consider the ideal
+\[
+I = \langle f_0, \ldots, f_{n - 2} \rangle \subset A
+\]
+generated by the $f_i$.  In this section, we will show that $A/I$ is a complete intersection, for which we require some preparatory computations.
 
-\subsection{Derivative computations}
+\subsection{Computations of derivatives}
+
+Our goal in this subsection is to establish Lemma \ref{lem:resbyparts}, which is a formal power series analogue of \cite[Lemma 3.4]{CE}.
+Our method will be an adaptation of the ``residues by parts'' argument which appears there.
+First, we require some direct computations of derivatives.
 
@@
 
-\todo[inline]{Split computations out into some lemmas on computations of $F'(z)$ and $V(z)$ which explicitly mention the hypotheses that $\sum_i m_i y_i = 0$.}
-
-To show that $A/I$ is a complete intersection, we will show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
-We will use a `residues by parts' argument; using the fact that the residue of an exact differential is zero, we will relate the coefficients of a power series to the coefficients of the derivative of that power series and derive a contradiction.
-To show this we must consider the derivatives of some power series in $z$ (including $F(z)$) with coefficients from $k$ rather than coefficients from $A$.
-
 \begin{lemma}\label{lem:dFdz2}
-For any $y_0,\dots,y_{r-1}$ distinct elements of $k$ with $m_i$ positive integers such that $\sum_i m_iy_i=0$, if we let $g(z)=\prod_{i=0}^{r-1} (1-y_iz)^{m_i}$ and $F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k$, then
+Let $y_0,\dots,y_{r-1}$ be distinct elements of $k$ and $m_i$ positive integers such that $\sum_i m_iy_i=0$.  Define 
 \[
-F'(z)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
+g(z)=\prod_{i=0}^{r-1} (1-y_iz)^{m_i} \text{  and } F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.
 \]
-where $[z^l]V(z)=0$ for $0 \le l \le p-1$. 
+For some $V(z)$ satisfying $[z^l]V(z)=0$ for $0 \le l \le p-1$, we have
+\[
+F'(z)=V(z) - \sum_j \frac{cm_jy_j}{1-y_jz}F(z).
+\]
 \end{lemma}
 \begin{proof}
-The computation proceeds essentially as it did for Lemma~\ref{lem:dFdz}.
-
-We see easily that 
+We compute as in the proof of Lemma~\ref{lem:dFdz}. We see easily that 
 \[
@@
 \frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
+&=\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\frac{\partial g}{\partial z}\\
 %&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
 %&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
-&=\left(\sum_j\frac{-m_jy_j}{1-y_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+&=- \sum_j\frac{m_jy_j}{1-y_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
 %&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
-&=\left(\sum_j\frac{-m_jy_j}{1-y_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
-&=\left(\sum_j \frac{-m_jy_j}{1-y_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(\sum_j \frac{-cm_jy_j}{1-y_jz}\right)F(z)+\left(\sum_j \frac{-m_jy_j}{1-y_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+&=-\sum_j\frac{m_jy_j}{1-y_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\\
+&=-\sum_j \frac{m_jy_j}{1-y_jz}\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=-\sum_j \frac{cm_jy_j}{1-y_jz}F(z) + \sum_j \frac{m_jy_j}{1-y_jz}c\binom{c-1}{p-1}(g-1)^{p-1}.
 \end{align*}
-We define 
+Defining the formal power series
 \[
-V(z)=\left(\sum_j \frac{-m_jy_j}{1-y_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+V(z)=\sum_j \frac{m_jy_j}{1-y_jz} c\binom{c-1}{p-1}(g-1)^{p-1},
 \]
-It is then clear that 
+we have shown that 
 \[
-F'(z)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right).
+F'(z)=V(z)- \sum_j \frac{cm_jy_j}{1-y_jz}F(z).
 \]
-Then it remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$. To show this, we need only show that $V(z)=z^pv(z)$ for some power series $v(z)$.
 
-We consider the expansion of $g(z)$; this is $g(z)=\prod_j (1-y_jz)^{m_j} = 1-z\left(\sum_i m_iy_i \right)+z^2e_2(y_i)+\dots+z^ne_n(y_i)$ where $e_2,\dots,e_n$ are polynomials in the $y_i$.
-In particular we note that $\sum_i m_iy_i=0$ by hypothesis, so $z^2 \mid g(z)-1$.
-
-Then by the definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$.
-Since $p \ge 2$, it is clear that $z^p \mid V(z)$, so we can write $V(z)=z^pv(z)$ for some power series $v(z)$ as desired.
+It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$, for which it suffices to show that $z^p \mid V(z)$.  Consider the expansion
+\[
+g(z)=\prod_j (1-y_jz)^{m_j} = 1-z\left(\sum_i m_iy_i \right)+z^2e_2(y_0, \ldots, y_{r - 1})+\dots+z^ne_n(y_0, \ldots, y_{r - 1})
+\]
+for some polynomials $e_2,\dots,e_n$.
+Since $\sum_i m_iy_i=0$ by hypothesis, we obtain $z^2 \mid g(z)-1$.
+By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$.
+Since $p \ge 2$, this implies $z^p \mid V(z)$, as needed.
 \end{proof}
@@
 \end{lemma}
-\begin{proof} We begin by showing that 
+\begin{proof} 
+We will use an analogue of ``residues by parts'' in a formal power series setting.   We begin by showing that 
 \[
@@
 \]
-The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$.
-We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$, so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient
+The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$. We always have 
+\[
+[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0,
+\]
+so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient
 \[
@@
 
-We are now ready to show that $A/I$ is a complete intersection.
+We now show that $A/I$ is a complete intersection.  Our technique is a translation of the idea of the proof of \cite[Theorem 3.2]{CE} to the formal power series context.
 

### 2015-05-19 formalwriteup.tex
Obtain dFdz2 from dFdz

@@
 
-Define $g(z)=\prod_{j=0}^{n-1} (1-x_jz)$ and $F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right)$ so that $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.
-We now show that $f_i$ are singular vectors.
+\subsection{Definition of the singular vectors}
 
-\todo[inline]{Break up the proof into lemmas, e.g. for the value of $\frac{\partial F}{\partial z}$}
+Define the polynomials 
+\[
+g(z)=\prod_{j=0}^{n-1} (1-x_jz) \qquad \text{ and } \qquad F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right).
+\]
+In terms of $g(z)$ and $F(z)$, we have $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We will show that $f_i$ are singular vectors.
+
+\subsection{Computation of some partial derivatives}
 
@@
 
-\begin{lemma}\label{lem:dFdz} We have
+\begin{lemma}\label{lem:dFdz}
+We have
 \[
@@
 \frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
+&=\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\frac{\partial g}{\partial z}\\
 %&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
 %&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
+&=-\sum_j \frac{x_j}{1-x_jz}\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}(g-1+1)\\
 %&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
-&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+&=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\\
+&=-\sum_j \frac{x_j}{1-x_jz}\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
+&=-\sum_j \frac{cx_j}{1-x_jz}F(z)+\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g-1)^{p-1}.
 \end{align*}
-We define 
+Defining the formal power series
 \[
-V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
+V(z)=\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g-1)^{p-1},
 \]
-It is then clear that 
+we see that 
 \[
@@
 \]
-Then it remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$. To show this, we need only show that $V(z)=z^pv(z)$ for some power series $v(z)$.
-
-We consider the expansion of $g(z)$; this is $g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_i)+\dots+z^ne_n(x_i)$ where $e_2,\dots,e_n$ are polynomials in the $x_i$.
-In particular we note that $\sum_i x_i=0$ by hypothesis, so $z^2 \mid g(z)-1$.
-
-Then by the definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$.
-Since $p \ge 2$, it is clear that $z^p \mid V(z)$, so we can write $V(z)=z^pv(z)$ for some power series $v(z)$ as desired.
+It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.  Consider the expansion 
+\[
+g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+z^ne_n(x_0, \ldots, x_{n - 1})
+\]
+for some polynomials $e_2, \ldots, e_n$.
+Recalling that $\sum_i x_i=0$ by hypothesis, we see that $z^2 \mid g(z)-1$.
+By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, hence $z^{2p-2} \mid V(z)$.
+Since $p \ge 2$, this implies $z^p \mid V(z)$, completing the proof.
 \end{proof}
@@
 \end{proof}
+
+\subsection{Proving $f_i$ are singular vectors}
 
@@
 
-\begin{lemma}\label{lem:dFdz2}
+\begin{corollary}\label{corr:dFdz2}
 Let $y_0,\dots,y_{r-1}$ be distinct elements of $k$ and $m_i$ positive integers such that $\sum_i m_iy_i=0$.  Define 
@@
 \]
-\end{lemma}
+\end{corollary}
 \begin{proof}
-We compute as in the proof of Lemma~\ref{lem:dFdz}. We see easily that 
-\[
-\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-m_jy_j}{1-y_jz}.
-\]
-We now consider $\frac{\partial F}{\partial z}$. We compute
-\begin{align*}
-\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\frac{\partial g}{\partial z}\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
-&=- \sum_j\frac{m_jy_j}{1-y_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
-&=-\sum_j\frac{m_jy_j}{1-y_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\\
-&=-\sum_j \frac{m_jy_j}{1-y_jz}\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=-\sum_j \frac{cm_jy_j}{1-y_jz}F(z) + \sum_j \frac{m_jy_j}{1-y_jz}c\binom{c-1}{p-1}(g-1)^{p-1}.
-\end{align*}
-Defining the formal power series
-\[
-V(z)=\sum_j \frac{m_jy_j}{1-y_jz} c\binom{c-1}{p-1}(g-1)^{p-1},
-\]
-we have shown that 
-\[
-F'(z)=V(z)- \sum_j \frac{cm_jy_j}{1-y_jz}F(z).
-\]
-
-It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$, for which it suffices to show that $z^p \mid V(z)$.  Consider the expansion
-\[
-g(z)=\prod_j (1-y_jz)^{m_j} = 1-z\left(\sum_i m_iy_i \right)+z^2e_2(y_0, \ldots, y_{r - 1})+\dots+z^ne_n(y_0, \ldots, y_{r - 1})
-\]
-for some polynomials $e_2,\dots,e_n$.
-Since $\sum_i m_iy_i=0$ by hypothesis, we obtain $z^2 \mid g(z)-1$.
-By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, so $z^{2p-2} \mid V(z)$.
-Since $p \ge 2$, this implies $z^p \mid V(z)$, as needed.
+Evaluate Lemma \ref{lem:dFdz} by substituting $m_i$ copies of $y_i$ for the $x_i$.
 \end{proof}
@@
 \begin{lemma} \label{lem:resbyparts}
-Let $y_0,\dots,y_{r-1}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_iy_i=0$.  For $F(z)$ as in Lemma \ref{lem:dFdz2}, let $a(z)$ be the formal power series
+Let $y_0,\dots,y_{r-1}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_iy_i=0$.
+For $F(z)$ as in Corollary \ref{corr:dFdz2}, let $a(z)$ be the formal power series
 \[
@@
 \]
-for some formal power series $b(z)$. By Lemma~\ref{lem:dFdz2} we have
+for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have
 \[

### 2015-05-19 formalwriteup.tex
Clean up linear independence, make generic c explicit

@@
 \[
-g(z)=\prod_{j=0}^{n-1} (1-x_jz) \qquad \text{ and } \qquad F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k\right).
+g(z)=\prod_{j=0}^{n-1} (1-x_jz) \qquad \text{ and } \qquad F(z) = \sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k.
 \]
@@
 \[
-g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+z^ne_n(x_0, \ldots, x_{n - 1})
+g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+z^ne_n(x_0, \ldots, x_{n - 1})
 \]
@@
 
-\begin{proposition}\label{prop:linind} The $f_i$ for $i=0,\dots,n-2$ are linearly independent degree $p$ homogeneous polynomials.
+\subsection{Proof of linear independence of $f_i$}
+
+\begin{proposition}\label{prop:linind} 
+For generic $c$, the $f_i$ for $i=0,\dots,n-2$ are linearly independent degree $p$ homogeneous polynomials.
 \end{proposition} 
+\begin{proof} 
+We have the expansion
+\[
+F_i(z)=\frac{1}{1-x_iz}\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k=\sum_{k=0}^\infty x_i^kz^k\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k.
+\]
+Because for any $l$ the coefficient of $z^l$ in each factor is a homogeneous polynomial of degree $l$, we see that $[z^p]F_i(z)$ is homogeneous of degree $p$.
 
-\begin{proof} 
-We recall that $F_i(z)=\frac{1}{1-x_iz}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)=\left(\sum_{k=0}^\infty x_i^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$.
-It is then clear that $f_i$ is a homogeneous polynomial in the $x_j$ of degree $p$, since $[z^k]F_i(z)$ is a homogeneous polynomial in the $x_j$ of degree $k$ for all $k$ (this follows from the fact that this is true in both multiplicands in $F_i$).
-
-Assume $\sum_{i=0}^{n-2} \lambda_if_i=0$ for some $\lambda_i \in k$.
-Then in particular this must be true when we set $x_j=1$ and $x_i=0$ for $i \ne j,i < n-1$.
-(We let $x_{n-1}=-1$ so that $\sum x_i=0$.) Note that if this is the case that $g(z)=(1-z)(1+z)=1-z^2$, so
+For linear independence, suppose that $\sum_{i=0}^{n-2} \lambda_if_i=0$ for some $\lambda_i \in k$.
+Substitute $x_{n-1} = -1$, $x_j=1$ and $x_i=0$ for $i \ne j,i < n-1$ so that $g(z)=(1-z)(1+z)=1-z^2$ and hence
 \[
-F_j(z)=\left(\sum_{k=0}^\infty z^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)
+F_j(z)=\sum_{k=0}^\infty z^k\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k
 \]
@@
 \[
-F_i(z)=\left(\sum_{k=0}^\infty 0^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k\right)=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k
+F_i(z)=\sum_{k=0}^\infty 0^kz^k\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k \text{ for $i < n - 1$, $i \neq j$}.
 \]
-for $n-1>i \ne j$.
+If $p = 2$, we see that $[z^2]F_j(z)=1-c$ and $[z^2]F_i(z)=-c$, so varying $j$ implies that
+\[
+\lambda_j = c\sum_{i=0}^{n-2} \lambda_i \text{ for all }j.
+\]
+In particular, all $\lambda_i$ have common value $\lambda \in k$ solving $(1-c(n-1))\lambda = 0$, which for generic $c$ implies that $\lambda = 0$, giving linear independence.
 
-We first consider the case $p=2$.
-In this case $[z^2]F_j(z)=1-c$ and $[z^2]F_i(z)=-c$.
-By setting $x_j=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne j, i \ne n-1$ for all $j=0,\dots,n-1$ in succession, we find that
+If $p > 2$, we have 
 \[
-\lambda_j-c\sum_{i=0}^{n-2} \lambda_i = 0 \text{ for all }j.
+[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}
 \]
-Therefore for all $j$, $\lambda_j=c\sum_{i=0}^{n-2} \lambda_i$.
-Then in particular all of the $\lambda_i$ are equal to some $\lambda \in k$ with $(1-c(n-1))\lambda = 0$.
-Since $c$ is generic, we can assume $(1-c(n-1)) \ne 0$, so then $\lambda=0$.
-Therefore $\lambda_j=0$ for all $j$; then the $f_i$ for $i=0,\dots,n-2$ are linearly independent as desired.
-
-We now suppose $p>2$.
-Then we have $[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}$ and $[z^p]F_i(z)=f_i=0$ for $n-1>i \ne j$ (since $p > 2$).
-Since $c$ is generic, we can assume $\binom{c-1}{(p-1)/2} \ne 0$.
-Then since $\sum_{i=0}^{n-2} \lambda_if_i=0$, we see that $\lambda_j\binom{c-1}{(p-1)/2}=0$; then we must have $\lambda_j=0$.
-
-By setting $x_j=1,x_{n-1}=-1$ and $x_i=0$ for $i \ne j, i \ne n-1$ for all $j=0,\dots,n-1$ in succession, we find that $\lambda_j=0$ for all $j$.
-Therefore the $f_i$ for $i=0,\dots,n-2$ are linearly independent as desired.
+and $[z^p]F_i(z)=f_i=0$ for $i < n - 1$ and $i \neq j$. For generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
+\[
+\sum_{i=0}^{n-2} \lambda_if_i=0 = \lambda_j\binom{c-1}{(p-1)/2}=0
+\]
+implies $\lambda_j=0$.  Varying $j$ implies that $\lambda_j=0$ for all $j$, again yielding linear independence.
 \end{proof}
@@
 \begin{proposition}\label{prop:ci}
-The quotient $A/I$ is a complete intersection. 
+For generic $c$, the quotient $A/I$ is a complete intersection. 
 \end{proposition}

### 2015-05-19 formalwriteup.tex
fixed differential operators

@@
 \[
-D_{y_i - y_j} = 
+D_{y_i - y_j} = \hbar \frac{\partial}{\partial (y_i-y_j)}-c\left(\sum_{k \ne i} \frac{1-s_{ki}}{x_i-x_k}\right)-c\left(\sum_{k \ne j} \frac{1-s_{ki}}{x_j-x_k}\right)
 \]
 
+where $\frac{\partial}{\partial (y_i-y_j)}$ is a differential operator we compute by letting $\frac{\partial x}{\partial (y_i-y_j)} = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$ and extending via the Leibnitz rule to the rest of $A=\Sym(\h^*)$.
 \todo[inline]{Remove $D_i$ and replace the quantity above}
@@
 
+\begin{lemma}\label{lem:z2g}
+We have $[z^0]g(z)=1$ and $[z^1]g(z)=0$, meaning $z^2 \mid g(z)-1$.
+\end{lemma}
+\begin{proof}
+Consider the expansion 
+\[
+g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+(-1)^nz^ne_n(x_0, \ldots, x_{n - 1})
+\]
+for the elementary symmetric polynomials $e_2, \ldots, e_n$.  Recalling that $\sum_i x_i=0$ by hypothesis, we see that $[z^1]g(z)=0$ and $[z^0]g(z)=1$, so $z^2 \mid g(z)-1$ as desired.
+\end{proof}
+
 \begin{lemma}\label{lem:dFdz}
@@
 \begin{align*}
-\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
+\frac{\partial F}{\partial z}
 &=\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\frac{\partial g}{\partial z}\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
 &=-\sum_j \frac{x_j}{1-x_jz}\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}(g-1+1)\\
-%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
 &=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\\
@@
 \]
-It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.  Consider the expansion 
-\[
-g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+z^ne_n(x_0, \ldots, x_{n - 1})
-\]
-for some polynomials $e_2, \ldots, e_n$.
-Recalling that $\sum_i x_i=0$ by hypothesis, we see that $z^2 \mid g(z)-1$.
-By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, hence $z^{2p-2} \mid V(z)$.
+It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.
+By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, hence by Lemma~\ref{lem:z2g}, $z^{2p-2} \mid V(z)$.
 Since $p \ge 2$, this implies $z^p \mid V(z)$, completing the proof.
@@
 
-\begin{lemma}\label{lem:dFdxi} For any $0 \le i < n-1$ we have 
+\begin{lemma}\label{lem:dFdxi} We have
 \[
-\frac{\partial F}{\partial x_i} = G_i(z) - \left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_iz}\right)F(z)
+\frac{\partial F}{\partial(y_1-y_0)} = G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)
 \]
-such that $G_i(z)$ is a power series with $[z^l]G_i(z)=0$ for $l=0,\dots,p$. 
+such that $G(z)$ is a power series with $[z^l]G(z)=0$ for $l=0,\dots,p$. 
 \end{lemma}
@@
 
-Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that
+We see that
 \[
-\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z} \text{ for all $0 \le i < n-1$}.
+\frac{\partial g}{\partial(y_1-y_0)}=-\frac{zg}{1-x_1z}+\frac{zg}{1-x_0z}.
 \]
-Then we see that for all $0 \le i < n-1$ we have 
+Then we see that
 \begin{align*}
-\frac{\partial F}{\partial x_i}%&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
-&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
-%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
-%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
-&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\\
-%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
-%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
+\frac{\partial F}{\partial(y_1-y_0)}&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial (y_1-y_0)}\\
+&=\left(-\frac{z}{1-x_1z}+\frac{z}{1-x_0z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
+&=\left(-\frac{z}{1-x_1z}+\frac{z}{1-x_0z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\\
+&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_0z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
 \end{align*}
@@
 \[
-G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
+G(z)=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_0z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
 \]
@@
 \[
-\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).
+\frac{\partial F}{\partial(y_1-y_0)}= G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)
 \]
-It remains only to show that $[z^l]G_i(z)=0$ for $l=0,\dots,p$. To show this, we need only show that $G_i(z)=z^{p+1}g_i(z)$ for some power series $v(z)$.  Consider the expansion 
-\[
-g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\left(\sum_i x_i\right)+z^2e_2(x_0, \ldots, x_{n-1})+\dots+z^ne_n(x_0, \ldots, x_{n - 1}).
-\]
-Recall that $\sum_i x_i = 0$, so $z^2 \mid g(z)-1$.
-By definition of $G_i(z)$, we see that $z(g-1)^{p-1} \mid G_i(z)$, so $z^{2p-1} \mid V(z)$.
-Since $p \ge 2$, this implies $z^{p+1} \mid G_i(z)$, giving the desired.
+It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$.
+By definition of $G(z)$, we see that $z(g-1)^{p-1} \mid G(z)$, so by Lemma~\ref{lem:z2g}, $z^{2p-1} \mid G(z)$.
+Since $p \ge 2$, this implies $z^{p+1} \mid G(z)$, completing the proof.
 \end{proof}
@@
 
-By Lemma~\ref{lem:dFdxi} we note that for $i=0,1$ we have $\frac{\partial F}{\partial x_i} = G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z)$ for power series $G_i(z)$ with $[z^l]G_i(z)=0$ for $l=0,\dots,p$.
+By Lemma~\ref{lem:dFdxi} we recall that $\frac{\partial F}{\partial(y_1-y_0)}= G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.
 
-We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. We compute
+We can now calculate $\frac{\partial F_0}{\partial (y_1-y_0)}$. We compute
 \begin{align*}
-\frac{\partial F_0}{\partial x_1}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
-&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
-&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
-&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
-\frac{\partial F_0}{\partial x_0}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
-&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
-&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
-%&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
-&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.
+\frac{\partial F_0}{\partial (y_1-y_0)}
+&=-\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial (y_1-y_0)}\\
+&=-\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(\frac{zc}{1-x_0z}-\frac{zc}{1-x_1z}\right)F(z)+\frac{G(z)}{1-x_0z}\\
+&=\left(\frac{z(c-1)}{1-x_0z}-\frac{zc}{1-x_1z}\right)F_0(z)+\frac{G(z)}{1-x_0z}.
 \end{align*}
@@
 \begin{align*}
-\frac{1-s_{0i}}{x_0-x_i}(F_0)%&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
+\frac{1-s_{0i}}{x_0-x_i}(F_0)
 &=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
-%&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
-%&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
 &=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
@@
 \end{align*}
-We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that 
+We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We see that 
 \[
-D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)
+D_1-D_0=\frac{\partial}{\partial (y_1-y_0)}-c\left(\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)-c\left(\frac{1-s_{01}}{x_1-x_0}\right)
 \]
@@
 \begin{align*}
-D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
-&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
-&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
-D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
-&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
-&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
-&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).
+(D_1-D_0)F_0&=\left(\frac{\partial}{\partial (y_1-y_0)}-c\left(\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)-c\left(\frac{1-s_{01}}{x_1-x_0}\right)\right)(F_0)\\
+&=\frac{\partial F_0}{\partial (y_1-y_0)}-c\sum_{j > 1} \left(\frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
+&=\frac{G(z)}{1-x_0z}+\left(\frac{z(c-1)}{1-x_0z}-\frac{zc}{1-x_1z}\right)F_0(z)-\sum_{j > 1} \frac{zc}{1-x_jz}F_0(z)\\
+&=\frac{G}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
 \end{align*}
-It is then easy to see that 
-\[
-(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
-\]
+
 In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.
@@
 \begin{align*}
-(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
-%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
-%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
-%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
-%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
-&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
-&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
+(D_1-D_0)(F_0)&=\frac{G(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
+&=\frac{G(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
+&=\frac{G(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\&=\frac{G(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
+&=\frac{G(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
 \end{align*}
 
-We note that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l](G_1(z)-G_0(z)+z^2V(z))$ for $0 \le l \le p$.
-This means that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l]G_0(z)$ for $0 \le l \le p$, $[z^l]G_1(z)$ for $0 \le l \le p$, and $[z^l]V(z)$ for $0 \le l \le p-2$.
-By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi} we recall that the coefficients of $G_i(z),V(z)$ under consideration are all $0$.
-This implies that $[z^p]\left(\frac{G_1-G_0+z^2V}{1-x_0z}\right)=0$.
+We note that $[z^p]\left(\frac{G+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$.
+This means that $[z^p]\left(\frac{G+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
+By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi} we recall that the coefficients of $G(z),V(z)$ under consideration are all $0$.
+This implies that $[z^p]\left(\frac{G+z^2V}{1-x_0z}\right)=0$.
 Therefore

### 2015-05-21 formalwriteup.tex
notation fixes

@@
 Let $S_n$ denote the symmetric group on $n$ elements, $V = k^n$ its permutation representation, and $s_{ij} \in S_n$ the transposition permuting $i$ and $j$.
-Fix a basis $y_0,\ldots,y_{n-1}$ for $V$ and a dual basis $x_0, \ldots, x_{n-1}$ for $V^*$.
+Fix a basis $y_1,\ldots,y_{n}$ for $V$ and a dual basis $x_1, \ldots, x_{n}$ for $V^*$.
 Let $\h$ and $\h^*$ be the dual $(n - 1)$-dimensional $S_n$-representations which are subrepresentation and quotient of $V$ and $V^*$, respectively given by
 \[
-\h = \sspan\{y_i - y_j \mid i \neq j\} \text{ and } \h^* = V^*/(x_0 + \cdots + x_{n - 1}).
+\h = \sspan\{y_i - y_j \mid i \neq j\} \text{ and } \h^* = V^*/(x_1 + \cdots + x_{n}).
 \]
@@
 \begin{align*}
-[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{k=0}^{n-1}\sum_{l=0}^{n-1} c\langle y_i,x_k-x_l \rangle\langle y_k-y_l,x_j\rangle s_{kl}
+[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{m=1}^{n}\sum_{l=1}^{n} c\langle y_i,x_m-x_l \rangle\langle y_m-y_l,x_j\rangle s_{ml}
 \end{align*}
-for all $0 \le i,j \le n-1$.
+for all $1 \le i,j \le n$.
 There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.
@@
 \begin{align*}
-D_y(f) = \hbar \partial_y f  - \sum_{k=0}^{n-1} \sum_{l=0}^{n-1} c  \langle y, x_k-x_l \rangle \frac{(1-s_{kl}) f}{x_k - x_l},
+D_y(f) = \hbar \partial_y f  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{(1-s_{ml}) f}{x_m - x_l},
 \end{align*}
-where we note that $\frac{(1-s_{kl}) f}{x_k - x_l}$ is a polynomial for $f \in A$. Explicitly, we have  
+where we note that $\frac{(1-s_{ml}) f}{x_m - x_l}$ is a polynomial for $f \in A$. Explicitly, we have  
 \[
-D_{y_i - y_j} = \hbar \frac{\partial}{\partial (y_i-y_j)}-c\left(\sum_{k \ne i} \frac{1-s_{ki}}{x_i-x_k}\right)-c\left(\sum_{k \ne j} \frac{1-s_{ki}}{x_j-x_k}\right)
+D_{y_i - y_j} = \hbar \partial_{y_i-y_j}-c\sum_{m \ne i} \frac{1-s_{mi}}{x_i-x_m}+c\sum_{m \ne j} \frac{1-s_{mi}}{x_j-x_m}
 \]
 
-where $\frac{\partial}{\partial (y_i-y_j)}$ is a differential operator we compute by letting $\frac{\partial x}{\partial (y_i-y_j)} = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$ and extending via the Leibnitz rule to the rest of $A=\Sym(\h^*)$.
-\todo[inline]{Remove $D_i$ and replace the quantity above}
+where $\partial_{y_i-y_j}$ is a differential operator we compute by letting $\partial_{y_i-y_j}(x) = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$ and extending via the Leibnitz rule to the rest of $A=\Sym(\h^*)$.
+
+We note that we can extend the Dunkl operators $D_y$ to formal power series in $z$ with coefficients from $A$ by letting the Dunkl operators act on each coefficient of the power series.
 
@@
 
-For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.  For $i = 0, \ldots, n - 2$, define the formal power series
+For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.
+We present some power series as rational functions which we expand near $z=0$.
+For $i = 1, \ldots, n - 1$, define the formal power series
 \[
-F_i(z)=\frac{1}{1-x_iz} \left(\sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right),
+F_i(z)=\frac{1}{1-x_iz} \left(\sum_{m=0}^{p-1} \binom{c}{m}(-1+\prod_{j=1}^{n} (1-x_jz))^m\right),
 \]
-where $\binom{c}{k} = \frac{c (c - 1) \cdots (c - k + 1)}{k!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.
+where $\binom{c}{m} = \frac{c (c - 1) \cdots (c - m + 1)}{m!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.
 
@@
 \[
-\Res_\infty\left[\frac{dz}{z-x_j} \prod_{i=0}^{n-1} (z-x_i)^c\right] \text{ for $j=0,\dots,n-2$}.
+\Res_\infty\left[\frac{dz}{z-x_j} \prod_{i=1}^{n} (z-x_i)^c\right] \text{ for $j=1,\dots,n-1$}.
 \]
@@
 \[
-g(z)=\prod_{j=0}^{n-1} (1-x_jz) \qquad \text{ and } \qquad F(z) = \sum_{k=0}^{p-1} \binom{c}{k} (g(z)-1)^k.
+g(z)=\prod_{j=1}^{n} (1-x_jz) \qquad \text{ and } \qquad F(z) = \sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m.
 \]
@@
 \[
-g(z)=\prod_{j=0}^{n-1} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_0, \ldots, x_{n - 1})+\dots+(-1)^nz^ne_n(x_0, \ldots, x_{n - 1})
+g(z)=\prod_{j=1}^{n} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_1, \ldots, x_{n})+\dots+(-1)^nz^ne_n(x_1, \ldots, x_{n})
 \]
@@
 \[
-F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z)
+F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z)
 \]
@@
 \frac{\partial F}{\partial z}
-&=\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\frac{\partial g}{\partial z}\\
-&=-\sum_j \frac{x_j}{1-x_jz}\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}(g-1+1)\\
-&=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\\
-&=-\sum_j \frac{x_j}{1-x_jz}\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
-&=-\sum_j \frac{cx_j}{1-x_jz}F(z)+\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g-1)^{p-1}.
+&=\sum_{m=1}^{p-1}m\binom{c}{m}(g(z)-1)^{m-1}\frac{\partial g}{\partial z}\\
+&=-\sum_j \frac{x_j}{1-x_jz}\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}(g(z)-1+1)\\
+&=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}+\sum_{m=1}^{p-1}c\binom{c-1}{m-1}(g(z)-1)^{m}\right)\\
+&=-\sum_j \frac{x_j}{1-x_jz}\left(-c\binom{c-1}{p-1}(g(z)-1)^{p-1}+\sum_{m=0}^{p-1}c\binom{c}{m}(g(z)-1)^{m}\right)\\
+&=-\sum_j \frac{cx_j}{1-x_jz}F(z)+\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g(z)-1)^{p-1}.
 \end{align*}
@@
 \[
-V(z)=\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g-1)^{p-1},
+V(z)=\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g(z)-1)^{p-1},
 \]
@@
 \[
-F'(z) = V(z) - \sum_{j=0}^{n-1} \frac{cx_j}{1-x_jz} F(z).
+F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z).
 \]
 It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.
-By definition of $V(z)$, we see that $(g-1)^{p-1} \mid V(z)$, hence by Lemma~\ref{lem:z2g}, $z^{2p-2} \mid V(z)$.
+By definition of $V(z)$, we see that $(g(z)-1)^{p-1} \mid V(z)$, hence by Lemma~\ref{lem:z2g}, $z^{2p-2} \mid V(z)$.
 Since $p \ge 2$, this implies $z^p \mid V(z)$, completing the proof.
@@
 \[
-\frac{\partial F}{\partial(y_1-y_0)} = G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)
+\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)
 \]
@@
 \[
-\frac{\partial g}{\partial(y_1-y_0)}=-\frac{zg}{1-x_1z}+\frac{zg}{1-x_0z}.
+\partial_{y_2-y_1}(g(z))=g(z)\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right).
 \]
@@
 \begin{align*}
-\frac{\partial F}{\partial(y_1-y_0)}&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial (y_1-y_0)}\\
-&=\left(-\frac{z}{1-x_1z}+\frac{z}{1-x_0z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
-&=\left(-\frac{z}{1-x_1z}+\frac{z}{1-x_0z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}+\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\\
-&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_0z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).
+\partial_{y_2-y_1}(F(z))&=\left(\sum_{m=1}^{p-1}m\binom{c}{m}(g(z)-1)^{m-1}\right)\partial_{y_2-y_1}(g(z))\\
+&=\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right)\left(\sum_{m=1}^{p-1}m\binom{c}{m}(g(z)-1)^{m-1}\right)g(z)\\
+&=\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right)\left(\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}+\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m+1}\right)\\
+&=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(-\binom{c-1}{p-1}(g(z)-1)^{p-1}+F(z)\right).
 \end{align*}
@@
 \[
-G(z)=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_0z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).
+G(z)=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(-\binom{c-1}{p-1}(g(z)-1)^{p-1}\right).
 \]
@@
 \[
-\frac{\partial F}{\partial(y_1-y_0)}= G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)
+\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)
 \]
 It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$.
-By definition of $G(z)$, we see that $z(g-1)^{p-1} \mid G(z)$, so by Lemma~\ref{lem:z2g}, $z^{2p-1} \mid G(z)$.
+By definition of $G(z)$, we see that $z(g(z)-1)^{p-1} \mid G(z)$, so by Lemma~\ref{lem:z2g}, $z^{2p-1} \mid G(z)$.
 Since $p \ge 2$, this implies $z^{p+1} \mid G(z)$, completing the proof.
@@
 \begin{proposition}\label{prop:ann} 
-The elements $f_i$ for $i=0,\dots,n-1$ are singular vectors in $A$.
+The elements $f_i$ for $i=1,\dots,n-1$ are singular vectors in $A$.
 \end{proposition}
@@
 We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$.
-It therefore suffices to consider the action of the Dunkl operators on $f_0$.
-We note that the Dunkl operators $D_i-D_j$ for all $i \ne j$ are spanned by $D_i-D_0$ for $0<i \le n-1$; then because $f_0$ is symmetric in the $x_i$ with $i > 0$, we see that it suffices to consider the action of $D_1-D_0$ on $f_0$ to show that the $f_i$ are annihilated by $D_i \ne D_j$ for all $i \ne j$.
+It therefore suffices to consider the action of the Dunkl operators on $f_1$.
+We note that the Dunkl operators $D_{y_i-y_j}$ for all $i \ne j$ are spanned by $D_{y_i-y_1}$ for $1<i \le n$; then because $f_1$ is symmetric in the $x_i$ with $i > 1$, we see that it suffices to consider the action of $D_{y_2-y_1}$ on $f_1$ to show that the $f_i$ are annihilated by $D_{y_i-y_j}$ for all $i \ne j$.
 
-By Lemma~\ref{lem:dFdxi} we recall that $\frac{\partial F}{\partial(y_1-y_0)}= G(z) - \left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_0z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.
+By Lemma~\ref{lem:dFdxi} we recall that $\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.
 
-We can now calculate $\frac{\partial F_0}{\partial (y_1-y_0)}$. We compute
+We can now calculate $\partial_{y_2-y_1}(F_1(z))$. We compute
 \begin{align*}
-\frac{\partial F_0}{\partial (y_1-y_0)}
-&=-\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial (y_1-y_0)}\\
-&=-\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(\frac{zc}{1-x_0z}-\frac{zc}{1-x_1z}\right)F(z)+\frac{G(z)}{1-x_0z}\\
-&=\left(\frac{z(c-1)}{1-x_0z}-\frac{zc}{1-x_1z}\right)F_0(z)+\frac{G(z)}{1-x_0z}.
+\partial_{y_2-y_1}(F_1(z))
+&=-\frac{z}{(1-x_1z)^2}F(z)+\frac{1}{1-x_1z}\partial_{y_2-y_1}(F(z))\\
+&=-\frac{z}{1-x_1z}F_1(z)+\frac{1}{1-x_1z}\left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_2z}\right)F(z)+\frac{G(z)}{1-x_1z}\\
+&=\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{G(z)}{1-x_1z}.
 \end{align*}
-We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that 
+We note that $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{1i}$ for $1 < i \le n$. We see that 
 \begin{align*}
-\frac{1-s_{0i}}{x_0-x_i}(F_0)
-&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
-&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
-&=\frac{z}{1-x_iz}F_0(z).
+\frac{1-s_{1i}}{x_1-x_i}(F_1(z))
+&=\frac{1}{x_1-x_i}\left(\frac{1}{1-x_1z}-\frac{1}{1-x_iz}\right)F(z)\\
+&=\frac{z}{(1-x_iz)(1-x_1z)}F(z)\\
+&=\frac{z}{1-x_iz}F_1(z).
 \end{align*}
-We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We see that 
+We recall that we need only consider the action of $D_{y_2-y_1}$ on $F_1(z)$. We see that 
 \[
-D_1-D_0=\frac{\partial}{\partial (y_1-y_0)}-c\left(\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)-c\left(\frac{1-s_{01}}{x_1-x_0}\right)
+D_{y_2-y_1}=\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}
 \]
-since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. We now compute
+since $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. We now compute
 \begin{align*}
-(D_1-D_0)F_0&=\left(\frac{\partial}{\partial (y_1-y_0)}-c\left(\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)-c\left(\frac{1-s_{01}}{x_1-x_0}\right)\right)(F_0)\\
-&=\frac{\partial F_0}{\partial (y_1-y_0)}-c\sum_{j > 1} \left(\frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
-&=\frac{G(z)}{1-x_0z}+\left(\frac{z(c-1)}{1-x_0z}-\frac{zc}{1-x_1z}\right)F_0(z)-\sum_{j > 1} \frac{zc}{1-x_jz}F_0(z)\\
-&=\frac{G}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.
+D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)(F_1(z))\\
+&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}(F_1(z))+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}(F_1(z))\\
+&=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z).
 \end{align*}
 
-In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_0}{\partial z}$.
+In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_1}{\partial z}$.
 
@@
 \begin{align*}
-\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
-&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
-&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
-&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).
+\frac{\partial F_1}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_1z}\right)\\
+&=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
+&=\frac{V(z)}{1-x_1z}+\frac{1}{1-x_1z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
+&=\frac{V(z)}{1-x_1z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_1(z)+\frac{x_1}{1-x_1z} F_1(z).
 \end{align*}
-We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
+We now again consider $D_{y_2-y_1}(F_1(z))$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_1(z)$ since that is $0$ in characteristic $p$. 
 \begin{align*}
-(D_1-D_0)(F_0)&=\frac{G(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
-&=\frac{G(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
-&=\frac{G(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\&=\frac{G(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
-&=\frac{G(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.
+D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z)+\left(\sum_{j} -zcF_1(z)+\frac{zc}{1-x_jz}F_1(z)\right)\\
+&=\frac{G(z)}{1-x_1z}-zF_1(z)+\frac{-x_1z^2}{1-x_1z}F_1(z)+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\right)\\&=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
+&=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}.
 \end{align*}
 
-We note that $[z^p]\left(\frac{G+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$.
-This means that $[z^p]\left(\frac{G+z^2V}{1-x_0z}\right)$ is a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
+We note that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$.
+This means that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
 By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi} we recall that the coefficients of $G(z),V(z)$ under consideration are all $0$.
-This implies that $[z^p]\left(\frac{G+z^2V}{1-x_0z}\right)=0$.
+This implies that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)=0$.
 Therefore
 \[
-[z^p]\left((D_1-D_0)(F_0)\right)=[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right).
+[z^p](D_{y_2-y_1}(F_1(z)))=[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right).
 \]
-Let $b=[z^{p-1}](F_0)$.
-We see that $[z^p](-zF_0)=-b$.
-Then $[z^{p-2}]\left(\frac{\partial F_0}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_0}{\partial z}\right)=b$.
-Therefore $[z^p]\left(-zF_0-z^2\frac{\partial F_0}{\partial z}\right)=-b+b=0$, so
+Let $b=[z^{p-1}](F_1(z))$.
+We see that $[z^p](-zF_1(z))=-b$.
+Then $[z^{p-2}]\left(\frac{\partial F_1}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_1}{\partial z}\right)=b$.
+Therefore $[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right)=-b+b=0$, so
 \[
-[z^p]((D_1-D_0)(F_0))=(D_1-D_0)([z^p]F_0)=(D_1-D_0)f_0=0.
+[z^p](D_{y_2-y_1}(F_1(z)))=D_{y_2-y_1}([z^p]F_1(z))=D_{y_2-y_1}f_1=0.
 \]
-By the symmetry of the $F_i$, this is the only Dunkl operator we need consider; it is clear that all the $f_i$ are killed by the Dunkl operators.
+By the symmetry of the $f_i$, this is the only Dunkl operator we need consider; it is clear that all the $f_i$ are killed by the Dunkl operators.
 \end{proof}
@@
 \begin{proposition}\label{prop:linind} 
-For generic $c$, the $f_i$ for $i=0,\dots,n-2$ are linearly independent degree $p$ homogeneous polynomials.
+For generic $c$, the $f_i$ for $i=1,\dots,n-1$ are linearly independent degree $p$ homogeneous polynomials.
 \end{proposition} 
@@
 \[
-F_i(z)=\frac{1}{1-x_iz}\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k=\sum_{k=0}^\infty x_i^kz^k\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k.
+F_i(z)=\frac{1}{1-x_iz}\sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m=\sum_{m=0}^\infty x_i^mz^m\sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m.
 \]
@@
 
-For linear independence, suppose that $\sum_{i=0}^{n-2} \lambda_if_i=0$ for some $\lambda_i \in k$.
-Substitute $x_{n-1} = -1$, $x_j=1$ and $x_i=0$ for $i \ne j,i < n-1$ so that $g(z)=(1-z)(1+z)=1-z^2$ and hence
+For linear independence, suppose that $\sum_{i=1}^{n-1} \lambda_if_i=0$ for some $\lambda_i \in k$.
+Substitute $x_{n} = -1$, $x_j=1$ and $x_i=0$ for $i \ne j,i < n$ so that $g(z)=(1-z)(1+z)=1-z^2$ and hence
 \[
-F_j(z)=\sum_{k=0}^\infty z^k\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k
+F_j(z)=\sum_{m=0}^\infty z^m\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m
 \]
@@
 \[
-F_i(z)=\sum_{k=0}^\infty 0^kz^k\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k=\sum_{k=0}^{p-1} \binom{c}{k} (-z^2)^k \text{ for $i < n - 1$, $i \neq j$}.
+F_i(z)=\sum_{m=0}^\infty 0^mz^m\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m=\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m \text{ for $i < n - 1$, $i \neq j$}.
 \]
@@
 \[
-\lambda_j = c\sum_{i=0}^{n-2} \lambda_i \text{ for all }j.
+\lambda_j = c\sum_{i=1}^{n-1} \lambda_i \text{ for all }j.
 \]
@@
 \[
-[z^p]F_j(z)=f_j=\sum_{k=0}^{(p-1)/2} (-1)^k\binom{c}{k}=\binom{c-1}{(p-1)/2}
+[z^p]F_j(z)=f_j=\sum_{m=0}^{(p-1)/2} (-1)^m\binom{c}{m}=\binom{c-1}{(p-1)/2}
 \]
-and $[z^p]F_i(z)=f_i=0$ for $i < n - 1$ and $i \neq j$. For generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
+and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
 \[
-\sum_{i=0}^{n-2} \lambda_if_i=0 = \lambda_j\binom{c-1}{(p-1)/2}=0
+\sum_{i=1}^{n-1} \lambda_if_i=0 = \lambda_j\binom{c-1}{(p-1)/2}=0
 \]
@@
 \[
-I = \langle f_0, \ldots, f_{n - 2} \rangle \subset A
+I = \langle f_1, \ldots, f_{n - 1} \rangle \subset A
 \]
@@
 
-\begin{lemma}\label{lem:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
+For any $s_1,\dots,s_{r}$ distinct elements of $k$ and positive integers $m_1,\dots,m_r$, we define 
+\[
+g(z)=\prod_{i=1}^{r} (1-s_iz)^{m_i} \text{  and } F(z)=\sum_{m=0}^{p-1} \binom{c}{m}(g(z)-1)^m
+\]
+as an analogue of $g(z)$ and $F(z)$ from the previous section. We also let $a(z)$ be the formal power series
+\[
+a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
+\]
+and define the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ for $i=1, \dots, r$.
+
+\begin{lemma}\label{lem:vand}Let $s_1, \ldots, s_{r }$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ are linearly independent.
 \end{lemma}
@@
 Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
-Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series.
-Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$.
-In particular for $l=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^l=0$.
-However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
+Then $\left(\prod_j (1-s_jz)\right)\left(\sum_i \frac{\lambda_i}{1-s_iz}\right)$ must be $0$ in the ring of formal power series.
+Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-s_iz}=0$.
+In particular for $l=0,\dots,r-1$ we have $\sum_i \lambda_is_i^l=0$.
+However, the vectors $(1,s_i,\dots,s_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
 \end{proof}
@@
 \begin{corollary}\label{corr:dFdz2}
-Let $y_0,\dots,y_{r-1}$ be distinct elements of $k$ and $m_i$ positive integers such that $\sum_i m_iy_i=0$.  Define 
-\[
-g(z)=\prod_{i=0}^{r-1} (1-y_iz)^{m_i} \text{  and } F(z)=\sum_{k=0}^{p-1} \binom{c}{k}(g-1)^k.
-\]
+Let $s_1,\dots,s_{r}$ be distinct elements of $k$ and $m_i$ positive integers such that $\sum_i m_is_i=0$.  
 For some $V(z)$ satisfying $[z^l]V(z)=0$ for $0 \le l \le p-1$, we have
 \[
-F'(z)=V(z) - \sum_j \frac{cm_jy_j}{1-y_jz}F(z).
+F'(z)=V(z) - \sum_j \frac{cm_js_j}{1-s_jz}F(z).
 \]
@@
 \begin{proof}
-Evaluate Lemma \ref{lem:dFdz} by substituting $m_i$ copies of $y_i$ for the $x_i$.
+Evaluate Lemma \ref{lem:dFdz} by substituting $m_i$ copies of $s_i$ for the $x_i$.
 \end{proof}
@@
 \begin{lemma} \label{lem:resbyparts}
-Let $y_0,\dots,y_{r-1}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_iy_i=0$.
-For $F(z)$ as in Corollary \ref{corr:dFdz2}, let $a(z)$ be the formal power series
-\[
-a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z).
-\]
+Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.
 For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
@@
 \[
-a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z)
+a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z)
 \]
@@
 \[
-F'(z)=V(z)+\left(\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right),
+F'(z)=V(z)+\left(\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right),
 \]
@@
 \begin{align*}
-a'(z)&=\frac{d}{dz}\left(\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z)\right)\\
-&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F'(z)+\sum_{j=0}^{r-1}\frac{y_j}{(1-y_jz)\prod_{i=0}^{r-1}(1-y_iz)}F(z)\\
-&=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}\left(V(z)+\sum_j \frac{-cm_jy_j}{1-y_jz}F(z)\right)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}+\sum_j \frac{-cm_jy_j}{1-y_jz}a(z)+\sum_{j=0}^{r-1}\frac{y_j}{1-y_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}-\sum_j \frac{(m_jc-1)y_j}{1-y_jz}a(z).
+a'(z)&=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)\\
+&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
+&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
+&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}+\sum_j \frac{-cm_js_j}{1-s_jz}a(z)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
+&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
 \end{align*}
@@
 \[
-\frac{V(z)}{\prod_{i=0}^{r-1}(1-y_iz)}=z^pb(z)
+\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}=z^pb(z)
 \]
@@
 \[
-h_l(z)=z^{-l-r}\prod_i(1-y_iz).
+h_l(z)=z^{-l-r}\prod_i(1-s_iz).
 \]
@@
 \begin{align*}
-\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_l(z) a(z) + h_l(z) a'(z) \\
-&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_i}{1 - y_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)y_i}{1 - y_ijz} a(z)  + z^ph_l(z) b(z)\\
-&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{y_im_i c}{1 - y_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
-&= -\left((l + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
+\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) + h_l(z) a'(z) \\
+&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
+&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_im_i c}{1 - s_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
+&= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
 \end{align*}
@@
 \[
--\left((l + r) z^{-1} + \sum_i \frac{y_im_i c}{1 - y_iz}\right) h_l(z)
+-\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z)
 \]
@@
 \[
-- z^{-l-r-1} \left(l + r + \sum_i y_i m_i c\right) = - z^{-l-r-1}(l+ r)
+- z^{-l-r-1} \left(l + r + \sum_i s_i m_i c\right) = - z^{-l-r-1}(l+ r)
 \]
@@
 \[
-- z^{-l - 1} (-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right).
+- z^{-l - 1} (-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right).
 \]
@@
 \[
-(-1)^r  \prod_i y_i\left((l + r) - \sum_i m_i c\right),
+(-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right),
 \]
-which is nonzero for $c$ generic and $\prod_i y_i \ne 0$. Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
+which is nonzero for $c$ generic and $\prod_i s_i \ne 0$. Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
 \end{proof}
@@
 \begin{proof}
-It suffices to show that if $x_0,\dots,x_{n-1} \in k$ satisfy $f_i(x_0,\dots,x_{n-1})=0$ for all $i$, then $x_0=\dots=x_{n-1}=0$.
-Suppose that the $x_i$ take the distinct values $\{y_0,\dots,y_{r-1}\}$, where $y_i$ occurs with multiplicity $m_i>0$ so that $g(z)=(1-y_iz)^{m_i}$.
+It suffices to show that if $x_1,\dots,x_{n} \in k$ satisfy $f_i(x_1,\dots,x_{n})=0$ for all $i$, then $x_1=\dots=x_{n}=0$.
+Suppose that the $x_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.
 In these terms, we have that
 \[
-[z^p]\left(\frac{1}{1-y_iz}F(z)\right)= 0
+[z^p]\left(\frac{1}{1-s_iz}F(z)\right)= 0
 \]
-for $i = 0, \ldots, r - 1$ and wish to show that $r=1$ and $y_0=0$.
+for $i = 1, \ldots, r $ and wish to show that $r=1$ and $s_1=0$.
 
-We first claim that at least one $y_i$ is $0$. Suppose for the sake of contradiction that $\prod_i y_i \ne 0$.  Then let
+We first claim that at least one $s_i$ is $0$. Suppose for the sake of contradiction that $\prod_i s_i \ne 0$.  We recall
 \[
-a(z)=\frac{1}{\prod_{i=0}^{r-1}(1-y_iz)}F(z)
+a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
 \]
-as in Lemma~\ref{lem:resbyparts}.  Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-y_iz}F(z)$ so in particular 
+as in Lemma~\ref{lem:resbyparts}.  Recall that $b_i(z)=\prod_{j \ne i} (1-s_jz)$ for $i=1,\dots,r$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-s_iz}F(z)$ so in particular 
 \[
-[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-y_iz}F(z)=0.
+[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-s_iz}F(z)=0.
 \]
@@
 \begin{equation}\label{eq:lincomb}
-\sum_{i=0}^{r-1} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=0}^{r-1}\lambda_ib_i(z)\right)=0.
+\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=1}^{r}\lambda_ib_i(z)\right)=0.
 \end{equation}
-By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$. Therefore for $0 \le k \le r-1$ we can choose $\{\lambda_i^k\}$ so that 
+By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$. Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that 
 \[
-\sum_i\lambda_i^kb_i(z)=z^k.
+\sum_i\lambda_i^mb_i(z)=z^m.
 \]
-Choosing these $\lambda_i^k$ in (\ref{eq:lincomb}), we see that
+Choosing these $\lambda_i^m$ in (\ref{eq:lincomb}), we see that
 \[
@@
 \]
-This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $y_i=0$ for some $i$.
+This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $s_i=0$ for some $i$.
 
-Now, suppose without loss of generality that $y_{r-1}=0$.
+Now, suppose without loss of generality that $s_{r}=0$.
 If $r = 1$, we are done.
-Otherwise, we have $\sum_{i=0}^{r-2} m_iy_i = \sum_{i=0}^{r-1} m_iy_i = 0$ and because the $y_i$ are distinct we see that $\prod_{i=0}^{r-2} y_i \ne 0$.
-Therefore, we may apply Lemma~\ref{lem:resbyparts} and repeat the argument above with $y_0, \ldots, y_{r - 2}$.
-We find that at least one of the $y_i$ with $i < r-1$ is $0$, a contradiction since the $y_i$ are distinct.
-Therefore, we must have $r=1$ and $y_0=0$, concluding the proof.
+Otherwise, we have $\sum_{i=1}^{r-1} m_is_i = \sum_{i=1}^{r} m_is_i = 0$ and because the $s_i$ are distinct we see that $\prod_{i=0}^{r-1} s_i \ne 0$.
+Therefore, we may apply Lemma~\ref{lem:resbyparts} and repeat the argument above with $s_1, \ldots, s_{r - 1}$.
+We find that at least one of the $s_i$ with $i < r$ is $0$, a contradiction since the $s_i$ are distinct.
+Therefore, we must have $r=1$ and $s_1=0$, concluding the proof.
 \end{proof}

### 2015-05-21 formalwriteup.tex
Line edits

@@
 \newtheorem*{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
-For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$, and the irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
+For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
+The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
 \[
@@
 \[
-G(z)=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(-\binom{c-1}{p-1}(g(z)-1)^{p-1}\right).
+G(z)=\left(\frac{zc}{1-x_2z}- \frac{zc}{1-x_1z}\right)\binom{c-1}{p-1}(g(z)-1)^{p-1}.
 \]
@@
 \begin{proof}
-We must show that $f_i$ is annihilated by annihilated by $D_j-D_l$ for all $j \ne l$.
+We must show that $f_i$ is annihilated by $D_{y_j - y_l}$ for all $j \ne l$.
+First, by symmetry it suffices to consider $f_1$.
+Because the Dunkl operators $D_{y_i-y_j}$ for all $i \ne j$ are spanned by $D_{y_i-y_1}$ for $1< i \le n$, it suffices to show $D_{y_i - y_1} f_1 = 0$.
+Finally, because $f_1$ is symmetric in the $x_i$ for $i > 1$, it suffices to show that $D_{y_2 - y_1} f_1 = 0$.
 
-We see that for all $i$, $f_i$ is symmetric in the $x_j$ for $j \ne i$.
-It therefore suffices to consider the action of the Dunkl operators on $f_1$.
-We note that the Dunkl operators $D_{y_i-y_j}$ for all $i \ne j$ are spanned by $D_{y_i-y_1}$ for $1<i \le n$; then because $f_1$ is symmetric in the $x_i$ with $i > 1$, we see that it suffices to consider the action of $D_{y_2-y_1}$ on $f_1$ to show that the $f_i$ are annihilated by $D_{y_i-y_j}$ for all $i \ne j$.
-
-By Lemma~\ref{lem:dFdxi} we recall that $\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.
-
-We can now calculate $\partial_{y_2-y_1}(F_1(z))$. We compute
+Recall by Lemma~\ref{lem:dFdxi} that $\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$.
+In terms of $G(z)$, we can calculate $\partial_{y_2-y_1}(F_1(z))$ as
 \begin{align*}
@@
 \begin{align*}
-D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)(F_1(z))\\
-&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}(F_1(z))+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}(F_1(z))\\
+D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)F_1(z)\\
+&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}(F_1(z))+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
 &=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
@@
 \end{align*}
-
-In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_1}{\partial z}$.
-
-We recall by Lemma~\ref{lem:dFdz} that
+In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_1}{\partial z}$.  Recall by Lemma~\ref{lem:dFdz} that
 \[
-\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).
+\frac{\partial F}{\partial z}=V(z)+\sum_j \frac{-cx_j}{1-x_jz}F(z).
 \]
@@
 &=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
-&=\frac{V(z)}{1-x_1z}+\frac{1}{1-x_1z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
-&=\frac{V(z)}{1-x_1z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_1(z)+\frac{x_1}{1-x_1z} F_1(z).
+&=\frac{V(z)}{1-x_1z}-\frac{1}{1-x_1z}\sum_j \frac{cx_j}{1-x_jz}F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
+&=\frac{V(z)}{1-x_1z} - \sum_j \frac{cx_j}{1-x_jz}F_1(z)+\frac{x_1}{1-x_1z} F_1(z).
 \end{align*}
@@
 D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z)\\
-&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z)+\left(\sum_{j} -zcF_1(z)+\frac{zc}{1-x_jz}F_1(z)\right)\\
-&=\frac{G(z)}{1-x_1z}-zF_1(z)+\frac{-x_1z^2}{1-x_1z}F_1(z)+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\right)\\&=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
+&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z)-\sum_{j} zcF_1(z)+\frac{zc}{1-x_jz}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}-zF_1(z)-\frac{x_1z^2}{1-x_1z}F_1(z)+\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
 &=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}.
 \end{align*}
-
 We note that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$.
@@
 Then $[z^{p-2}]\left(\frac{\partial F_1}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_1}{\partial z}\right)=b$.
-Therefore $[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right)=-b+b=0$, so
+Therefore $[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right)=-b+b=0$, yielding the desired
 \[
-[z^p](D_{y_2-y_1}(F_1(z)))=D_{y_2-y_1}([z^p]F_1(z))=D_{y_2-y_1}f_1=0.
+D_{y_2 - y_1} f_1 = [z^p](D_{y_2-y_1}(F_1(z)))=D_{y_2-y_1}([z^p]F_1(z))=D_{y_2-y_1}f_1=0. \qedhere
 \]
-By the symmetry of the $f_i$, this is the only Dunkl operator we need consider; it is clear that all the $f_i$ are killed by the Dunkl operators.
 \end{proof}
@@
 \begin{proof} 
-We will use an analogue of ``residues by parts'' in a formal power series setting.   We begin by showing that 
+We will use an analogue of ``residues by parts'' in a formal power series setting.   We first show that 
 \[
@@
 \[
-F'(z)=V(z)+\left(\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right),
+F'(z)=V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z),
 \]
-where $[z^l]V(z)=0$ for $0 \le l \le p-1$. 
-We now compute
+where $[z^l]V(z)=0$ for $0 \le l \le p-1$. We now compute
 \begin{align*}
@@
 If $r = 1$, we are done.
-Otherwise, we have $\sum_{i=1}^{r-1} m_is_i = \sum_{i=1}^{r} m_is_i = 0$ and because the $s_i$ are distinct we see that $\prod_{i=0}^{r-1} s_i \ne 0$.
+Otherwise, we have $\sum_{i=1}^{r-1} m_is_i = \sum_{i=1}^{r} m_is_i = 0$ and because the $s_i$ are distinct we see that $\prod_{i=1}^{r-1} s_i \ne 0$.
 Therefore, we may apply Lemma~\ref{lem:resbyparts} and repeat the argument above with $s_1, \ldots, s_{r - 1}$.
-We find that at least one of the $s_i$ with $i < r$ is $0$, a contradiction since the $s_i$ are distinct.
-Therefore, we must have $r=1$ and $s_1=0$, concluding the proof.
+We find that at least one of the $s_i$ with $i < r$ is $0$, contradicting distinctness of $s_i$.
+Therefore, we find $r=1$ and $s_1=0$, concluding the proof.
 \end{proof}
@@
 \begin{theorem}\label{thm:main}
-For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$, and the irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
+For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
+The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
 \[
@@
 \]
-for some polynomial $h(t)$ with nonnegative integer coefficients.
-On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ linearly independent generators $f_i$ in degree $p$.
-Therefore, its Hilbert series is
+for a polynomial $h(t)$ with nonnegative integer coefficients.
+On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ linearly independent degree $p$ generators $f_i$.
+Its Hilbert series is
 \[

### 2015-05-21 formalwriteup.tex
Line edits

@@
 Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.
-In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
-While we restrict our present study to the polynomial representation in type $A$, we view this problem as a test case for this philosophy and believe it may admit wider application.
+In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions with complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
+While we restrict our study to the polynomial representation in type $A$, we view it as a test case for this philosophy, which we believe may admit wider application.
 
-In the remainder of this introduction, we give precise statements of our results and explain how they relate to other recent work.
+We now state our results precisely and explain their relation to other recent work.
 
@@
 
-Throughout this paper, we work over an algebraically closed field $k$ of characteristic $p > 0$ and fix $n$ so that $p \mid n$.
+We work over an algebraically closed field $k$ of characteristic $p > 0$ and fix $n$ so that $p \mid n$.
 Let $S_n$ denote the symmetric group on $n$ elements, $V = k^n$ its permutation representation, and $s_{ij} \in S_n$ the transposition permuting $i$ and $j$.
@@
 The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.
-The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act via the \textit{Dunkl operator} $D_y$ defined by
+The action of $\Sym(\h)$ is implemented by letting $y \in \h$ act by the \textit{Dunkl operator}
 \begin{align*}
@@
 \[
-D_{y_i - y_j} = \hbar \partial_{y_i-y_j}-c\sum_{m \ne i} \frac{1-s_{mi}}{x_i-x_m}+c\sum_{m \ne j} \frac{1-s_{mi}}{x_j-x_m}
+D_{y_i - y_j} = \hbar \partial_{y_i-y_j}-c\sum_{m \ne i} \frac{1-s_{mi}}{x_i-x_m}+c\sum_{m \ne j} \frac{1-s_{mi}}{x_j-x_m},
 \]
-
-where $\partial_{y_i-y_j}$ is a differential operator we compute by letting $\partial_{y_i-y_j}(x) = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$ and extending via the Leibnitz rule to the rest of $A=\Sym(\h^*)$.
-
-We note that we can extend the Dunkl operators $D_y$ to formal power series in $z$ with coefficients from $A$ by letting the Dunkl operators act on each coefficient of the power series.
+where $\partial_{y_i-y_j}$ is the differential operator satisfying $\partial_{y_i-y_j}(x) = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$.
+We will also consier Dunkl operators acting on $A[[z]]$ by the coefficient-wise action.
 
@@
 For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.
-We present some power series as rational functions which we expand near $z=0$.
+Throughout the paper, we will consider formal power series in $z$ considered as expansions of rational functions around $z = 0$.
 For $i = 1, \ldots, n - 1$, define the formal power series
@@
 \]
-where $\binom{c}{m} = \frac{c (c - 1) \cdots (c - m + 1)}{m!}$ and consider the coefficients $f_i = [z^p] F_i(z)$.
+where $\binom{c}{m} = \frac{c (c - 1) \cdots (c - m + 1)}{m!}$ and denote the coefficients $f_i = [z^p] F_i(z)$.
 

### 2015-05-21 formalwriteup.tex
Line edits

@@
 \begin{align*}
-D_y(f) = \hbar \partial_y f  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{(1-s_{ml}) f}{x_m - x_l},
+D_y = \hbar \partial_y  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{1-s_{ml}}{x_m - x_l},
 \end{align*}
-where we note that $\frac{(1-s_{ml}) f}{x_m - x_l}$ is a polynomial for $f \in A$. Explicitly, we have  
+where we note that $\frac{1-s_{ml}}{x_m - x_l}f$ is a polynomial for $f \in A$. Explicitly, we have  
 \[
@@
 Such $f$ are known as \textit{singular vectors}.
-
-The quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.  It inherits a $\ZZ_{\geq 0}$-grading from $A$, and we recall that its Hilbert series is 
+The quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.
+It inherits a $\ZZ_{\geq 0}$-grading from $A$, and for $L_j$ the degree $j$ subspace of $L$, we may define its Hilbert series as
 \[
-h_L(t) = \sum_{j \geq 0} \dim L_j t^j,
+h_L(t) = \sum_{j \geq 0} \dim L_j t^j.
 \]
-where $L_j$ is the degree $j$ subspace of $L$.
 
@@
 \]
-In terms of $g(z)$ and $F(z)$, we have $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We will show that $f_i$ are singular vectors.
+In these terms, we have $F_i(z) = \frac{F(z)}{1-x_iz}$ and $f_i = [z^p] \frac{F(z)}{1-x_iz}$.  We will show that $f_i$ are singular vectors.
 
@@
 \begin{lemma}\label{lem:dFdz}
-We have
+For some formal power series $V(z)$ with $[z^l]V(z)=0$ for $l=0,\dots,p-1$, we have
 \[
-F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z)
+F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z).
 \]
-such that $V(z)$ is a power series with $[z^l]V(z)=0$ for $l=0,\dots,p-1$. 
 \end{lemma}
@@
 \begin{proof}
-We see easily that 
-\[
-\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.
-\]
-We now consider $\frac{\partial F}{\partial z}$. We compute
+We see easily that $\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$. We compute
 \begin{align*}
@@
 \]
-we see that 
-\[
-F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z).
-\]
-It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$.
-By definition of $V(z)$, we see that $(g(z)-1)^{p-1} \mid V(z)$, hence by Lemma~\ref{lem:z2g}, $z^{2p-2} \mid V(z)$.
-Since $p \ge 2$, this implies $z^p \mid V(z)$, completing the proof.
+we see that $F'(z) = V(z) - \sum_{j=1}^{n} \frac{cx_j}{1-x_jz} F(z)$.
+It remains only to show that $[z^l]V(z)=0$ for $l=0,\dots,p-1$, which follows by noting that $(g(z)-1)^{p-1} \mid V(z)$, applying Lemma~\ref{lem:z2g}, and noting $p \ge 2$.
 \end{proof}
 
-\begin{lemma}\label{lem:dFdxi} We have
+\begin{lemma}\label{lem:dFdxi} 
+For some formal power series $G(z)$ with $[z^l]V(z)=0$ for $l=0,\dots,p$, we have
 \[
-\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)
+\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z).
 \]
-such that $G(z)$ is a power series with $[z^l]G(z)=0$ for $l=0,\dots,p$. 
 \end{lemma}
-
 \begin{proof}
-
-We see that
-\[
-\partial_{y_2-y_1}(g(z))=g(z)\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right).
-\]
-Then we see that
+We may compute $\partial_{y_2-y_1}(g(z))=g(z)\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right)$. Using this, we see that
 \begin{align*}
@@
 \end{align*}
-We define
-\[
-G(z)=\left(\frac{zc}{1-x_2z}- \frac{zc}{1-x_1z}\right)\binom{c-1}{p-1}(g(z)-1)^{p-1}.
-\]
-Then we see that
+Defining $G(z)=\left(\frac{zc}{1-x_2z}- \frac{zc}{1-x_1z}\right)\binom{c-1}{p-1}(g(z)-1)^{p-1}$, we have shown that
 \[
@@
 \]
-It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$.
-By definition of $G(z)$, we see that $z(g(z)-1)^{p-1} \mid G(z)$, so by Lemma~\ref{lem:z2g}, $z^{2p-1} \mid G(z)$.
-Since $p \ge 2$, this implies $z^{p+1} \mid G(z)$, completing the proof.
+It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$. By definition of $G(z)$, which follows by noting that $z(g(z)-1)^{p-1} \mid G(z)$, applying Lemma~\ref{lem:z2g}, and noting $p \geq 2$.
 \end{proof}
@@
 We note that $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{1i}$ for $1 < i \le n$. We see that 
-\begin{align*}
+\[
 \frac{1-s_{1i}}{x_1-x_i}(F_1(z))
-&=\frac{1}{x_1-x_i}\left(\frac{1}{1-x_1z}-\frac{1}{1-x_iz}\right)F(z)\\
-&=\frac{z}{(1-x_iz)(1-x_1z)}F(z)\\
-&=\frac{z}{1-x_iz}F_1(z).
-\end{align*}
+=\frac{1}{x_1-x_i}\left(\frac{1}{1-x_1z}-\frac{1}{1-x_iz}\right)F(z)=\frac{z}{(1-x_iz)(1-x_1z)}F(z)=\frac{z}{1-x_iz}F_1(z).
+\]
 We recall that we need only consider the action of $D_{y_2-y_1}$ on $F_1(z)$. We see that 
@@
 \begin{align*}
-\frac{\partial F_1}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_1z}\right)\\
-&=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
+\frac{\partial F_1}{\partial z} = \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_1z}\right) &=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
 &=\frac{V(z)}{1-x_1z}-\frac{1}{1-x_1z}\sum_j \frac{cx_j}{1-x_jz}F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
@@
 \]
-for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have
-\[
-F'(z)=V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z),
-\]
-where $[z^l]V(z)=0$ for $0 \le l \le p-1$. We now compute
+for some formal power series $b(z)$.
+By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)$.
+We now compute
 \begin{align*}
@@
 \end{align*}
-Since $[z^l]V(z)=0$ for $0 \le l \le p-1$ we see that 
-\[
-\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}=z^pb(z)
-\]
-for some power series $b(z)$, giving the claim.
+The fact that $[z^l]V(z)=0$ for $0 \le l \le p-1$ then gives the claim.
 
@@
 \]
-so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z),[z^{l+1}]a(z),\dots,[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has nonzero coefficient
-\[
-(-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right),
-\]
-which is nonzero for $c$ generic and $\prod_i s_i \ne 0$. Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
+so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$, which is nonzero for $c$ generic and $\prod_i s_i \ne 0$.
+Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$.
 \end{proof}
@@
 \end{equation}
-By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$. Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that 
-\[
-\sum_i\lambda_i^mb_i(z)=z^m.
-\]
+By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$.
+Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that $\sum_i\lambda_i^mb_i(z)=z^m$.
 Choosing these $\lambda_i^m$ in (\ref{eq:lincomb}), we see that

### 2015-05-21 formalwriteup.tex
Line edits

@@
 
-Define the polynomials 
+In $A$, define the polynomials 
 \[
@@
 \begin{proof}
-Consider the expansion 
+For elementary symmetric polynomials $e_2, \ldots, e_n$, we have the expansion 
 \[
-g(z)=\prod_{j=1}^{n} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_1, \ldots, x_{n})+\dots+(-1)^nz^ne_n(x_1, \ldots, x_{n})
+g(z)=\prod_{j=1}^{n} (1-x_jz) = 1-z\sum_i x_i+z^2e_2(x_1, \ldots, x_{n})+\dots+(-1)^nz^ne_n(x_1, \ldots, x_{n}).
 \]
-for the elementary symmetric polynomials $e_2, \ldots, e_n$.  Recalling that $\sum_i x_i=0$ by hypothesis, we see that $[z^1]g(z)=0$ and $[z^0]g(z)=1$, so $z^2 \mid g(z)-1$ as desired.
+Recalling that $\sum_i x_i=0$ in $A$, we see that $[z^1]g(z)=0$ and $[z^0]g(z)=1$, so $z^2 \mid g(z)-1$ as desired.
 \end{proof}

### 2015-05-21 formalwriteup.tex
Line edits

@@
 \newtheorem*{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
-For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
+For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
 The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
@@
 \begin{proposition}\label{prop:linind} 
-For generic $c$, the $f_i$ for $i=1,\dots,n-1$ are linearly independent degree $p$ homogeneous polynomials.
+For generic $c$, $f_1, \ldots, f_{n - 1}$ are linearly independent degree $p$ homogeneous polynomials.
 \end{proposition} 
@@
 \begin{theorem}\label{thm:main}
-For generic $c$, the $f_i$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
+For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
 The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series

### 2015-05-22 formalwriteup.tex
Line edits

@@
 \[
-F_i(z)=\frac{1}{1-x_iz} \left(\sum_{m=0}^{p-1} \binom{c}{m}(-1+\prod_{j=1}^{n} (1-x_jz))^m\right),
+F_i(z)=\frac{1}{1-x_iz} \sum_{m=0}^{p-1} \binom{c}{m}\left(\prod_{j=1}^{n} (1-x_jz) - 1\right)^m
 \]
-where $\binom{c}{m} = \frac{c (c - 1) \cdots (c - m + 1)}{m!}$ and denote the coefficients $f_i = [z^p] F_i(z)$.
+for $\binom{c}{m} = \frac{c (c - 1) \cdots (c - m + 1)}{m!}$.  Denote by $f_i$ the coefficients $f_i = [z^p] F_i(z)$.
 
@@
 &=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}+\sum_{m=1}^{p-1}c\binom{c-1}{m-1}(g(z)-1)^{m}\right)\\
-&=-\sum_j \frac{x_j}{1-x_jz}\left(-c\binom{c-1}{p-1}(g(z)-1)^{p-1}+\sum_{m=0}^{p-1}c\binom{c}{m}(g(z)-1)^{m}\right)\\
+&=-\sum_j \frac{x_j}{1-x_jz}\left(\sum_{m=0}^{p-1}c\binom{c}{m}(g(z)-1)^{m}-c\binom{c-1}{p-1}(g(z)-1)^{p-1}\right)\\
 &=-\sum_j \frac{cx_j}{1-x_jz}F(z)+\sum_j \frac{x_j}{1-x_jz}c\binom{c-1}{p-1}(g(z)-1)^{p-1}.
@@
 &=\left(-\frac{z}{1-x_2z}+\frac{z}{1-x_1z}\right)\left(\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m}+\sum_{m=0}^{p-2}c\binom{c-1}{m}(g(z)-1)^{m+1}\right)\\
-&=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(-\binom{c-1}{p-1}(g(z)-1)^{p-1}+F(z)\right).
+&=\left(-\frac{zc}{1-x_2z}+\frac{zc}{1-x_1z}\right)\left(F(z)-\binom{c-1}{p-1}(g(z)-1)^{p-1}\right).
 \end{align*}
@@
 \end{align*}
-We note that $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{1i}$ for $1 < i \le n$. We see that 
+In addition, we have that 
 \[
@@
 \]
-We recall that we need only consider the action of $D_{y_2-y_1}$ on $F_1(z)$. We see that 
-\[
-D_{y_2-y_1}=\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}
-\]
-since $F_1(z)$ is invariant under $s_{ij}$ where $1 < i,j$. We now compute
+Because $F_1(z)$ is invariant under $s_{ij}$ for $i,j > 1$, we now compute
 \begin{align*}
 D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)F_1(z)\\
-&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}(F_1(z))+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
+&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}F_1(z)+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
 &=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
-&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z).
+&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z).
 \end{align*}
-In order to show that the $p$th coefficient in this formal power series is $0$, we must consider $\frac{\partial F_1}{\partial z}$.  Recall by Lemma~\ref{lem:dFdz} that
+To show that the $z^p$ coefficient in $D_{y_2-y_1}(F_1(z))$ vanishes, we must consider $\frac{\partial F_1}{\partial z}$.  By Lemma~\ref{lem:dFdz}, we have
 \[
-\frac{\partial F}{\partial z}=V(z)+\sum_j \frac{-cx_j}{1-x_jz}F(z).
+\frac{\partial F}{\partial z}=V(z) - \sum_j \frac{cx_j}{1-x_jz}F(z),
 \]
-where $[z^l]V(z)=0$ for $l=0,\dots,p-1$.
-
-From this it follows that
+where $[z^l]V(z)=0$ for $l=0,\dots,p-1$. From this, it follows that
 \begin{align*}
@@
 \end{align*}
-We now again consider $D_{y_2-y_1}(F_1(z))$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_1(z)$ since that is $0$ in characteristic $p$. 
+We now compute
 \begin{align*}
-D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}+\frac{z(c-1)}{1-x_1z}F_1(z)+\sum_{j>1} \frac{zc}{1-x_jz}F_1(z)\\
-&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z)-\sum_{j} zcF_1(z)+\frac{zc}{1-x_jz}F_1(z)\\
+D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z) + \sum_{j} \left(\frac{zc}{1-x_jz} - zc\right) F_1(z)\\
 &=\frac{G(z)}{1-x_1z}-zF_1(z)-\frac{x_1z^2}{1-x_1z}F_1(z)+\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\\
 &=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
-&=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}.
+&=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z},
 \end{align*}
-We note that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$.
-This means that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
-By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi} we recall that the coefficients of $G(z),V(z)$ under consideration are all $0$.
-This implies that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)=0$.
-Therefore
+where in the second step we have subtracted $n zc F_1(z)$.
+We note that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$, hence a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
+By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi}, these coefficients of $G(z)$ and $V(z)$ are all $0$, hence $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)=0$.
+We conclude that
 \[
-[z^p](D_{y_2-y_1}(F_1(z)))=[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right).
+[z^p]D_{y_2-y_1}(F_1(z))=[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right).
 \]
-Let $b=[z^{p-1}](F_1(z))$.
-We see that $[z^p](-zF_1(z))=-b$.
-Then $[z^{p-2}]\left(\frac{\partial F_1}{\partial z}\right)=(p-1)b=-b$, so $[z^p]\left(-z^2\frac{\partial F_1}{\partial z}\right)=b$.
-Therefore $[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right)=-b+b=0$, yielding the desired
+If $b=[z^{p-1}](F_1(z))$, then $[z^p](-zF_1(z))=-b$ and $[z^p]\left(-z^2\frac{\partial F_1}{\partial z}\right)=b$, which implies that 
 \[
-D_{y_2 - y_1} f_1 = [z^p](D_{y_2-y_1}(F_1(z)))=D_{y_2-y_1}([z^p]F_1(z))=D_{y_2-y_1}f_1=0. \qedhere
+D_{y_2 - y_1} f_1 = [z^p]D_{y_2-y_1}(F_1(z))= [z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right) = -b + b = 0. \qedhere
 \]

### 2015-05-22 formalwriteup.tex
Line edits

@@
 where in the second step we have subtracted $n zc F_1(z)$.
-We note that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$, hence a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
-By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi}, these coefficients of $G(z)$ and $V(z)$ are all $0$, hence $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)=0$.
+We note that $[z^p]\,\frac{G(z)+z^2V(z)}{1-x_1z}$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$, hence a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
+By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi}, these coefficients of $G(z)$ and $V(z)$ are all $0$, hence $[z^p]\,\frac{G(z)+z^2V(z)}{1-x_1z}=0$.
 We conclude that
@@
 
-Consider the ideal
-\[
-I = \langle f_1, \ldots, f_{n - 1} \rangle \subset A
-\]
-generated by the $f_i$.  In this section, we will show that $A/I$ is a complete intersection, for which we require some preparatory computations.
+Consider the ideal $I = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
+In this section, we will show that $A/I$ is a complete intersection, for which we require some preparatory computations.
 
@@
 Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
-Then $\left(\prod_j (1-s_jz)\right)\left(\sum_i \frac{\lambda_i}{1-s_iz}\right)$ must be $0$ in the ring of formal power series.
+Then $\prod_j (1-s_jz)\sum_i \frac{\lambda_i}{1-s_iz}$ must be $0$ in the ring of formal power series.
 Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-s_iz}=0$.
@@
 \begin{align*}
-a'(z)&=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)\\
-&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
+a'(z)=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
 &=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}+\sum_j \frac{-cm_js_j}{1-s_jz}a(z)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
+%&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}+\sum_j \frac{-cm_js_j}{1-s_jz}a(z)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
 &=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
@@
 
-Now, for any integer $l$, define the Laurent polynomial 
-\[
-h_l(z)=z^{-l-r}\prod_i(1-s_iz).
-\]
-Notice that
+Now, for any integer $l$, define the Laurent polynomial $h_l(z)=z^{-l-r}\prod_i(1-s_iz)$. Notice that
 \begin{align*}
@@
 &=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
-&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_im_i c}{1 - s_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
+%&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_im_i c}{1 - s_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
 &= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
@@
 \[
-[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0,
+[z^{-1}]\,\frac{d}{dz}( h_l(z) a(z))=0,
 \]
@@
 \[
-[z^p]\left(\frac{1}{1-s_iz}F(z)\right)= 0
+[z^p]\frac{1}{1-s_iz}F(z)= 0
 \]
@@
 \begin{equation}\label{eq:lincomb}
-\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=1}^{r}\lambda_ib_i(z)\right)=0.
+\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p] \,a(z)\sum_{i=1}^{r}\lambda_ib_i(z)=0.
 \end{equation}

### 2015-05-25 formalwriteup.tex
Spell check
Add Pavel's grant
changes 1-6

@@
 We study the polynomial representation of the rational Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$.
-We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient.
+We give explicit formulas for generators for the maximal proper graded submodule, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient.
 Our methods are motivated by taking characteristic $p$ analogues of existing characteristic $0$ results.
@@
 For $\hbar = 1$ and generic $c$, we provide a complete characterization of the irreducible quotient of the polynomial representation.
-We give explicit generators for the unique maximal ideal, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.
+We give explicit generators for the unique maximal proper graded submodule $J$, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.
 
 Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.
-In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions with complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
+In particular, our explicit expression for generators of $J$ was obtained by converting expressions with complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
 While we restrict our study to the polynomial representation in type $A$, we view it as a test case for this philosophy, which we believe may admit wider application.
@@
 \begin{align*}
-[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_j] = \hbar\langle y_i,x_j\rangle - \sum_{m=1}^{n}\sum_{l=1}^{n} c\langle y_i,x_m-x_l \rangle\langle y_m-y_l,x_j\rangle s_{ml}
-\end{align*}
-for all $1 \le i,j \le n$.
+[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_i] = \hbar- c \sum_{m \ne i} s_{im},\quad [y_i,x_j] =cs_{ij}\end{align*}
+for all $1 \le i < j \le n$.
 There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.
@@
 
-The rational Cherednik algebra $\HH_{\hbar, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.
+The rational Cherednik algebra $\HH_{1, c}(\h)$ admits a $\ZZ_{\geq 0}$-graded representation on the polynomial ring $A = \Sym(\h^*)$, known as the \textit{polynomial representation}.
 The actions of $\Sym(\h^*)$ and $k[S_n]$ on $A$ are by left multiplication and the $S_n$ action on $\h^*$, respectively.
@@
 \begin{align*}
-D_y = \hbar \partial_y  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{1-s_{ml}}{x_m - x_l},
+D_y =  \partial_y  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{1-s_{ml}}{x_m - x_l},
 \end{align*}
@@
 \[
-D_{y_i - y_j} = \hbar \partial_{y_i-y_j}-c\sum_{m \ne i} \frac{1-s_{mi}}{x_i-x_m}+c\sum_{m \ne j} \frac{1-s_{mi}}{x_j-x_m},
-\]
+D_{y_i - y_j} =  \partial_{y_i-y_j}-c\sum_{m \ne i} \frac{1-s_{mi}}{x_i-x_m}+c\sum_{m \ne j} \frac{1-s_{mj}}{x_j-x_m},
+\] \noindent
 where $\partial_{y_i-y_j}$ is the differential operator satisfying $\partial_{y_i-y_j}(x) = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$.
-We will also consier Dunkl operators acting on $A[[z]]$ by the coefficient-wise action.
+We will also consider Dunkl operators acting on $A[[z]]$ by the coefficient-wise action.
 
-\subsection{Maximal ideal and irreducible quotient of the polynomial representation}
+\subsection{Maximal proper graded submodule and irreducible quotient of the polynomial representation}
 
@@
 Such $f$ are known as \textit{singular vectors}.
-The quotient $L = A/J$ is an irreducible representation of $\HH_{\hbar,c}(\h)$.
+The quotient $L = A/J$ is an irreducible representation of $\HH_{1,c}(\h)$.
 It inherits a $\ZZ_{\geq 0}$-grading from $A$, and for $L_j$ the degree $j$ subspace of $L$, we may define its Hilbert series as
@@
 \newtheorem*{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
-For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
+For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
 The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
@@
 Our study is motivated by previous work on the representation theory of the type $A$ rational Cherednik algebra in both characteristic $0$ and $p$.
-The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and some properties of the maximal ideal of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
+The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and some properties of the maximal proper graded submodule of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
 In the modular case $p \mid n$, for $p = 2$, the polynomial representation associated to the $n$-dimensional permutation representation was studied.
@@
 \]
-The corresponding maximal ideal is generated by $n - 1$ elements of degree $2$ and one element of degree $4$. 
+The corresponding maximal proper graded submodule is generated by $n - 1$ elements of degree $2$ and one element of degree $4$. 
 \end{theorem} 
-It was further conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with maximal ideal having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
+It was further conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with $J$ having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
 Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.
 It would be interesting to extend our work to prove Lian's conjecture in full.
-For general $p \mid n$, a subideal of the maximal ideal was computed in \cite[Proposition 6.1]{DS}.
+For general $p \mid n$, a subideal of the maximal proper graded submodule was computed in \cite[Proposition 6.1]{DS}.
 
 In characteristic $0$, our results parallel the explicit decomposition of the polynomial representation of the type $A$ rational Cherednik algebra given in \cite{BEG, CE}.
-There, the polynomial representation is irreducible unless $c = \frac{r}{n}$ for some integer $r$, and an explicit set of generators of the maximal ideal is known.
+There, the polynomial representation is irreducible unless $c = \frac{r}{n}$ for some integer $r$, and an explicit set of generators of the maximal proper graded submodule is known.
 \begin{proposition}[{\cite[Proposition 3.1]{CE}}] \label{prop:ce}
-If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal ideal $J \subset A$ of the polynomial representation $A$ of $\HH_{\hbar,c}(\h)$ is generated by
+If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal proper graded submodule $J \subset A$ of the polynomial representation $A$ of $\HH_{\hbar,c}(\h)$ is generated by
 \[
@@
 was supported by a NSF Graduate Research Fellowship (NSF Grant \#1122374).
-
-\todo[inline]{Ask Pavel for his grant number}
+Both authors were also supported by NSF Grant DMS-1000113.
 
@@
 \begin{theorem}\label{thm:main}
-For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal ideal $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
+For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
 The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series

### 2015-05-25 formalwriteup.tex
other wording changes

@@
 For $\hbar = 1$ and generic $c$, we provide a complete characterization of the irreducible quotient of the polynomial representation.
-We give explicit generators for the unique maximal proper graded submodule $J$, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.
+We give explicit generators for the unique maximal proper graded submodule $J_c$, show that the irreducible quotient is a complete intersection, and compute its Hilbert series.
 
 Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.
-In particular, our explicit expression for generators of $J$ was obtained by converting expressions with complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
+In particular, our explicit expression for generators of $J_c$ was obtained by converting expressions with complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.
 While we restrict our study to the polynomial representation in type $A$, we view it as a test case for this philosophy, which we believe may admit wider application.
@@
 [x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_i] = \hbar- c \sum_{m \ne i} s_{im},\quad [y_i,x_j] =cs_{ij}\end{align*}
-for all $1 \le i < j \le n$.
+for all $1 \le i , j \le n$ such that $i \neq j$.
 There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.
@@
 where $\partial_{y_i-y_j}$ is the differential operator satisfying $\partial_{y_i-y_j}(x) = \langle y_i-y_j,x\rangle$ for all $x \in \h^*$.
-We will also consider Dunkl operators acting on $A[[z]]$ by the coefficient-wise action.
 
@@
 \[
-\beta_c(xf,g)=\beta_c(f,xg) \qquad \text{ and } \qquad \beta_c(f,yg) = \beta_c(yf,g).
+\beta_c(xf,g)=\beta_c(f,D_x(g)) \qquad \text{ and } \qquad \beta_c(f,yg) = \beta_c(D_y(f),g).
 \]
-Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J = \ker(\beta_c)$.
-By the definition of $\beta_c$, $J$ is generated by homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.
+Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
+By the definition of $\beta_c$, $J_c$ contains all homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.
 Such $f$ are known as \textit{singular vectors}.
-The quotient $L = A/J$ is an irreducible representation of $\HH_{1,c}(\h)$.
+The quotient $L = A/J_c$ is an irreducible representation of $\HH_{1,c}(\h)$.
 It inherits a $\ZZ_{\geq 0}$-grading from $A$, and for $L_j$ the degree $j$ subspace of $L$, we may define its Hilbert series as
@@
 \newtheorem*{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
-For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
-The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
+For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J_c$ of the polynomial representation for $\HH_{1, c}(\h)$.
+The irreducible quotient $L = A/J_c$ is a complete intersection with Hilbert series
 \[
@@
 \begin{remark}
-In Theorem \ref{thm:main}, by generic $c$ we mean $c$ avoiding countably many values.
+In Theorem \ref{thm:main}, by generic $c$ we mean $c$ avoiding finitely many values.
 \end{remark}
@@
 \end{theorem} 
-It was further conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with $J$ having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
+It was further conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with $J_c$ having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
 Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.
@@
 \begin{proposition}[{\cite[Proposition 3.1]{CE}}] \label{prop:ce}
-If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal proper graded submodule $J \subset A$ of the polynomial representation $A$ of $\HH_{\hbar,c}(\h)$ is generated by
+If $\char(k) = 0$ and $c = \frac{r}{n}$, the maximal proper graded submodule $J_c \subset A$ of the polynomial representation $A$ of $\HH_{1,c}(\h)$ is generated by
 \[
@@
 \end{proposition}
-We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then taking $c = \frac{p}{n}$ should correspond to taking generic $c$.
+We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then since $p/n$ is an indeterminacy in characteristic $p$ (because it is equivalent to $0/0$), $c=p/n$ in characteristic $0$ in some sense corresponds to $c$ generic in characteristic $p$.
+
 While this substitution is of course invalid, Proposition \ref{prop:ce} may be interpreted as a statement about certain formal power series.
@@
 \[
-F_i(z)=\frac{1}{1-x_iz}\sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m=\sum_{m=0}^\infty x_i^mz^m\sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m.
+F_i(z)=\frac{1}{1-x_iz}\sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m=\sum_{l=0}^\infty x_i^lz^l\sum_{m=0}^{p-1} \binom{c}{m} (g(z)-1)^m.
 \]
@@
 \[
-F_j(z)=\sum_{m=0}^\infty z^m\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m
+F_j(z)=\sum_{l=0}^\infty z^l\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m
 \]
@@
 \[
-F_i(z)=\sum_{m=0}^\infty 0^mz^m\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m=\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m \text{ for $i < n - 1$, $i \neq j$}.
+F_i(z)=\sum_{l=0}^\infty 0^lz^l\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m=\sum_{m=0}^{p-1} \binom{c}{m} (-z^2)^m \text{ for $i < n - 1$, $i \neq j$}.
 \]
@@
 Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
-Then $\prod_j (1-s_jz)\sum_i \frac{\lambda_i}{1-s_iz}$ must be $0$ in the ring of formal power series.
-Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-s_iz}=0$.
-In particular for $l=0,\dots,r-1$ we have $\sum_i \lambda_is_i^l=0$.
-However, the vectors $(1,s_i,\dots,s_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
+Let $w_i(z)= \prod_{j \neq i} (z-s_j)$.
+Then we see that $\sum_i \lambda_iw_i(1/z)=\sum_i \lambda_i b_i(z)/z^{r-1}=0$, so $\sum_i \lambda_i w_i(z)=0$.
+Since the $s_i$ are distinct, we see that $w_i(s_i) \ne 0$ and $w_i(s_j)=0$ for all $i \neq j$.
+Therefore by evaluating $\sum_i \lambda_i w_i(z)=0$ at $z=s_1,\dots,s_r$ we see that $\lambda_iw_i(s_i)=0$ for all $i$, so $\lambda_i=0$ for all $i$.
+Then $b_i(z)$ are linearly independent.
 \end{proof}
@@
 \begin{proof}
-Evaluate Lemma \ref{lem:dFdz} by substituting $m_i$ copies of $s_i$ for the $x_i$.
+Apply Lemma~\ref{lem:dFdz} by letting the $x_i$ be $m_i$ copies of the $s_i$. 
 \end{proof}
@@
 &=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
-%&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}+\sum_j \frac{-cm_js_j}{1-s_jz}a(z)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
 &=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
@@
 &=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
-%&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_im_i c}{1 - s_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
 &= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
@@
 \begin{theorem}\label{thm:main}
-For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J$ of the polynomial representation for $\HH_{1, c}(\h)$.
-The irreducible quotient $L = A/J$ is a complete intersection with Hilbert series
+For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J_c$ of the polynomial representation for $\HH_{1, c}(\h)$.
+The irreducible quotient $L = A/J_c$ is a complete intersection with Hilbert series
 \[
@@
 \]
-By Proposition~\ref{prop:ann}, the generators $f_i$ of $I$ are singular vectors, so $I \subseteq J$, implying that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficient-wise.
-We conclude that $h(t) = 1$, hence $h_{A/I}(t)=h_{A/J}(t)$ and $I=J$, completing the proof.
+By Proposition~\ref{prop:ann}, the generators $f_i$ of $I$ are singular vectors, so $I \subseteq J_c$, implying that $h_{A/I}(t) \ge h_{A/J_c}(t)$ coefficient-wise.
+We conclude that $h(t) = 1$, hence $h_{A/I}(t)=h_{A/J_c}(t)$ and $I=J_c$, completing the proof.
 \end{proof}

### 2015-05-26 formalwriteup.tex
line edits
Line edits

@@
 Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
-By the definition of $\beta_c$, $J_c$ contains all homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.
+By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.
 Such $f$ are known as \textit{singular vectors}.
@@
 It was further conjectured by Lian in \cite[Conjecture 5.2]{L} that for all $p$ the corresponding irreducible is a complete intersection with $J_c$ having $n - 1$ generators in degree $p$ and a single generator in degree $p^2$.
-Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is restricted to the $(n - 1)$-dimensional quotient.
+Our results are consistent with the restriction of Lian's conjecture to the case when $\h$ is the $(n - 1)$-dimensional quotient.
 It would be interesting to extend our work to prove Lian's conjecture in full.
-For general $p \mid n$, a subideal of the maximal proper graded submodule was computed in \cite[Proposition 6.1]{DS}.
+For general $p \mid n$, a submodule of the maximal proper graded submodule was computed in \cite[Proposition 6.1]{DS}.
 
@@
 \end{proposition}
-We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then since $p/n$ is an indeterminacy in characteristic $p$ (because it is equivalent to $0/0$), $c=p/n$ in characteristic $0$ in some sense corresponds to $c$ generic in characteristic $p$.
-
+We interpret the characteristic $p$ analogue of Proposition \ref{prop:ce} to mean that if $r = p$ and $p \mid n$, then since $p/n$ is equivalent to $0/0$ and thus an indeterminacy in characteristic $p$, taking $c=p/n$ in characteristic $0$ should correspond to taking $c$ generic in characteristic $p$.
 While this substitution is of course invalid, Proposition \ref{prop:ce} may be interpreted as a statement about certain formal power series.
@@
 
-Consider the ideal $I = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
-In this section, we will show that $A/I$ is a complete intersection, for which we require some preparatory computations.
+Consider the ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
+In this section, we will show that $A/I_c$ is a complete intersection, for which we require some preparatory computations.
 
@@
 
-We now show that $A/I$ is a complete intersection.  Our technique is a translation of the idea of the proof of \cite[Theorem 3.2]{CE} to the formal power series context.
+We now show that $A/I_c$ is a complete intersection.  Our technique is a translation of the idea of the proof of \cite[Theorem 3.2]{CE} to the formal power series context.
 
 \begin{proposition}\label{prop:ci}
-For generic $c$, the quotient $A/I$ is a complete intersection. 
+For generic $c$, the quotient $A/I_c$ is a complete intersection. 
 \end{proposition}
@@
 for a polynomial $h(t)$ with nonnegative integer coefficients.
-On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I$ is a complete intersection with $n-1$ linearly independent degree $p$ generators $f_i$.
+On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I_c$ is a complete intersection with $n-1$ linearly independent degree $p$ generators $f_i$.
 Its Hilbert series is
 \[
-h_{A/I}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}.
+h_{A/I_c}(t)=\left(\frac{1-t^p}{1-t}\right)^{n-1}.
 \]
-By Proposition~\ref{prop:ann}, the generators $f_i$ of $I$ are singular vectors, so $I \subseteq J_c$, implying that $h_{A/I}(t) \ge h_{A/J_c}(t)$ coefficient-wise.
-We conclude that $h(t) = 1$, hence $h_{A/I}(t)=h_{A/J_c}(t)$ and $I=J_c$, completing the proof.
+By Proposition~\ref{prop:ann}, the generators $f_i$ of $I_c$ are singular vectors, so $I_c \subseteq J_c$, implying that $h_{A/I_c}(t) \ge h_{A/J_c}(t)$ coefficient-wise.
+We conclude that $h(t) = 1$, hence $h_{A/I_c}(t)=h_{A/J_c}(t)$ and $I_c=J_c$, completing the proof.
 \end{proof}

### 2015-05-26 formalwriteup.tex
Add comment on generic c

@@
 \begin{proof}
-Apply Lemma~\ref{lem:dFdz} by letting the $x_i$ be $m_i$ copies of the $s_i$. 
+Take the $x_i$ to be $m_i$ copies of the $s_i$ in Lemma~\ref{lem:dFdz}.
 \end{proof}
@@
 Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.
-For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
+For generic $c$ and any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
 \end{lemma}
@@
 \]
-By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$, we find that 
+By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$ (but finitely many times and with finitely many choices of $l$, $r$, and $m_i$), we find for generic $c$ that
 \[

### 2015-05-26 formalwriteup.tex
Line edits
Line edit

@@
 
-\subsection{Maximal proper graded submodule and irreducible quotient of the polynomial representation}
+\subsection{Maximal proper graded submodule and irreducible quotient of polynomial representation}
 
@@
 The type $A$ non-modular case $p \gg n$ was studied in \cite{BFG}, and some properties of the maximal proper graded submodule of the polynomial representation were given in both modular and non-modular cases in \cite{BC1}.
-In the modular case $p \mid n$, for $p = 2$, the polynomial representation associated to the $n$-dimensional permutation representation was studied.
+In the modular case $p \mid n$, for $p = 2$ the polynomial representation associated to the $n$-dimensional permutation representation was studied in \cite{L}.
 \begin{theorem}[{\cite[Theorem 5.1]{L}}] \label{thm:lian}
@@
 \[
-\sum_{i=1}^{n-1} \lambda_if_i=0 = \lambda_j\binom{c-1}{(p-1)/2}=0
+\sum_{i=1}^{n-1} \lambda_if_i = \lambda_j\binom{c-1}{(p-1)/2}=0,
 \]
-implies $\lambda_j=0$.  Varying $j$ implies that $\lambda_j=0$ for all $j$, again yielding linear independence.
+which implies $\lambda_j=0$.  Varying $j$ implies that $\lambda_j=0$ for all $j$, again yielding linear independence.
 \end{proof}
@@
 \begin{proof}
-Take the $x_i$ to be $m_i$ copies of the $s_i$ in Lemma~\ref{lem:dFdz}.
+Take the variables $x_j$ to consist of $m_i$ copies of each $s_i$ in Lemma~\ref{lem:dFdz}.
 \end{proof}

### 2015-05-27 formalwriteup.tex
commutation relations + singular vectors

@@
 \begin{align*}
-[x_i,x_j]=0, \quad [y_i,y_j] = 0, \quad [y_i,x_i] = \hbar- c \sum_{m \ne i} s_{im},\quad [y_i,x_j] =cs_{ij}\end{align*}
-for all $1 \le i , j \le n$ such that $i \neq j$.
+[x_i,x_j]=0, \quad [y_i-y_j,y_l-y_m] = 0, \quad [y_i-y_j,x_i] = \hbar- cs_{ij}-c \sum_{t \ne i} s_{it},\quad [y_i-y_j,x_l] =cs_{il}-cs_{jl}\end{align*}
+for all $1 \le i , j, l, m \le n$ such that $i,j,l$ are distinct and $l \neq m$.
 There is a $\ZZ$-grading on $\HH_{\hbar,c}(\h)$ given by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[S_n]$.
@@
 Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
-By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ killed by all Dunkl operators $D_y$.
+By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ of positive degree that are killed by all Dunkl operators $D_y$.
 Such $f$ are known as \textit{singular vectors}.

### 2015-05-27 formalwriteup.tex
Fix Dunkl operator definition
line edits

@@
 \begin{align*}
-D_y =  \partial_y  - \sum_{m=1}^{n} \sum_{l=1}^{n} c  \langle y, x_m-x_l \rangle \frac{1-s_{ml}}{x_m - x_l},
+D_y =  \partial_y  - \sum_{m < l} c  \langle y, x_m-x_l \rangle \frac{1-s_{ml}}{x_m - x_l},
 \end{align*}
@@
 \begin{proof}
-We see easily that $\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$. We compute
+We see easily that $\frac{\partial g}{\partial z} = -g(z) \sum_j \frac{x_j}{1-x_jz}$. We now consider $\frac{\partial F}{\partial z}$. We compute
 \begin{align*}
@@
 \begin{lemma}\label{lem:dFdxi} 
-For some formal power series $G(z)$ with $[z^l]V(z)=0$ for $l=0,\dots,p$, we have
+For some formal power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$, we have
 \[
@@
 \]
-It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$. By definition of $G(z)$, which follows by noting that $z(g(z)-1)^{p-1} \mid G(z)$, applying Lemma~\ref{lem:z2g}, and noting $p \geq 2$.
+It remains only to show that $[z^l]G(z)=0$ for $l=0,\dots,p$, which follows by noting that $z(g(z)-1)^{p-1} \mid G(z)$, applying Lemma~\ref{lem:z2g}, and noting $p \geq 2$.
 \end{proof}
@@
 \]
-for some formal power series $b(z)$.
-By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)$.
-We now compute
+for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)-\sum_j \frac{cm_js_j}{1-s_jz}F(z)$. We now compute
 \begin{align*}
 a'(z)=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
-&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
+&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)-\sum_j \frac{cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
 &=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).

### 2015-05-29 submission.tex
format for submission

--- 2015-05-27 formalwriteup.tex
@@
-\documentclass{amsart}
+\documentclass[smallcondensed]{svjour3}
 \usepackage{amsmath}
 \usepackage{amsfonts}
-\usepackage{amssymb,amsthm}
+\usepackage{amssymb}%,amsthm}
 \usepackage{color}
@@
 \numberwithin{equation}{section}
-\theoremstyle{definition}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem*{remark}{Remark}
-\newtheorem{definition}[equation]{Definition}
+%\theoremstyle{definition}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{conjecture}[theorem]{Conjecture}
+%\newtheorem{problem}[theorem]{Problem}
+%\newtheorem*{remark}{Remark}
+%\newtheorem{definition}[equation]{Definition}
 \newenvironment{defn}[1][]{%
@@
 \begin{document}
-\title[Polynomial representation of type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$]{The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$}
-\author{Sheela Devadas}
-\email[S. Devadas]{sheelad@mit.edu}
-\author{Yi Sun}
-\email[Y. Sun]{yisun@math.mit.edu}
-\date{\today}
+
+ \author{Sheela Devadas\thanks{Math Dept., MIT, Cambridge MA 02139
+ E-mail: {\tt sheelad@mit.edu}. Phone: {\tt 781-325-6895}}\;and Yi Sun\thanks{Math Dept., MIT, Cambridge MA 02139
+ E-mail: {\tt yisun@math.mit.edu}.
+ Research supported by NSF Grant \#1122374. \\\\ Both authors were also supported by NSF Grant DMS-1000113.
+}}
+ \title{The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$}
+\date{May 28, 2015}
+\journalname{ALGE}
+\institute{}
+
+\maketitle
 
@@
 
-\maketitle
 \setcounter{tocdepth}{1}
@@
 
-\newtheorem*{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
+\newtheorem{thm:main}{Theorem \ref{thm:main}} \begin{thm:main}
 For generic $c$, $f_1, \ldots, f_{n-1}$ are linearly independent and generate the maximal proper graded submodule $J_c$ of the polynomial representation for $\HH_{1, c}(\h)$.
@@
 
-In characteristic $0$, our results parallel the explicit decomposition of the polynomial representation of the type $A$ rational Cherednik algebra given in \cite{BEG, CE}.
+In characteristic $0$, our results parallel the explicit decomposition of the polynomial representation of the type $A$ rational Cherednik algebra given in \cite{BEG,CE}.
 There, the polynomial representation is irreducible unless $c = \frac{r}{n}$ for some integer $r$, and an explicit set of generators of the maximal proper graded submodule is known.
@@
 While this substitution is of course invalid, Proposition \ref{prop:ce} may be interpreted as a statement about certain formal power series.
-By using a power series version of this construction of generators which makes sense in characteristic $p$, we are able to mimic the arguments of \cite{BEG, CE} to show that they cut out a complete intersection and generate the entire ideal.
+By using a power series version of this construction of generators which makes sense in characteristic $p$, we are able to mimic the arguments of \cite{BEG,CE} to show that they cut out a complete intersection and generate the entire ideal.
 We believe that the philosophy of taking characteristic $p$ analogues of characteristic $0$ results for the rational Cherednik algebra should apply more generally and hope to explore this further in future work.
@@
 \[
-D_{y_2 - y_1} f_1 = [z^p]D_{y_2-y_1}(F_1(z))= [z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right) = -b + b = 0. \qedhere
+D_{y_2 - y_1} f_1 = [z^p]D_{y_2-y_1}(F_1(z))= [z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right) = -b + b = 0. \qed
 \]

### 2015-06-13 formalwriteup.tex
referee's comments

@@
 \]
+where $D_x$ is an operator representing the action of $x \in \h^*$ on $\Sym(\h)$ (defined similarly to $D_y$ above).
+
 Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
@@
 \begin{theorem}[{\cite[Theorem 5.1]{L}}] \label{thm:lian}
-The irreducible quotient of the polynomial representation associated to the $n$-dimensional reflection representation is a complete intersection with Hilbert series
+The irreducible quotient of the polynomial representation associated to the permutation representation is a complete intersection with Hilbert series
 \[

### 2015-06-13 submission2.tex
submission 2

--- 2015-06-13 formalwriteup.tex
@@
-\documentclass{amsart}
+\documentclass{elsarticle}
 \usepackage{amsmath}
@@
 \begin{document}
-\title[Polynomial representation of type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$]{The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$}
-\author{Sheela Devadas}
-\email[S. Devadas]{sheelad@mit.edu}
-\author{Yi Sun}
-\email[Y. Sun]{yisun@math.mit.edu}
+\title{The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$}
+\author[mit]{Sheela~Devadas\corref{cor1}}
+\ead{sheelad@mit.edu}
+\author[mit]{Yi~Sun}
+\ead{yisun@math.mit.edu}
+\cortext[cor1]{Corresponding author}
+\address[mit]{Massachusetts Institute of Technology, 77 Massachusetts Ave., Cambridge MA 02139}
 \date{\today}
@@
 \end{abstract}
+\begin{keyword}
+modular representation theory \sep rational Cherednik algebras \MSC{16G99, 20C20}
+\end{keyword}
 
 \maketitle
+
 \setcounter{tocdepth}{1}

### 2015-06-14 submission2.tex
Line edits

@@
 \]
-where $D_x$ is an operator representing the action of $x \in \h^*$ on $\Sym(\h)$ (defined similarly to $D_y$ above).
+where for $x \in \h^*$ we denote by $D_x$ the Dunkl operator implementing the action of $\HH_{1, c}(\h^*)$ on its polynomial representation $\Sym(\h)$.
 
-Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
+The polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
 By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ of positive degree that are killed by all Dunkl operators $D_y$.
@@
 \begin{theorem}[{\cite[Theorem 5.1]{L}}] \label{thm:lian}
-The irreducible quotient of the polynomial representation associated to the permutation representation is a complete intersection with Hilbert series
+The irreducible quotient of the polynomial representation associated to the $n$-dimensional permutation representation is a complete intersection with Hilbert series
 \[

### 2015-09-27 formalwriteup.tex
copied line edits to formalwriteup
small edits

@@
 \author{Sheela Devadas}
-\email[S. Devadas]{sheelad@mit.edu}
+\email[S. Devadas]{sheelad@stanford.edu}
 \author{Yi Sun}
@@
 \]
-where $D_x$ is an operator representing the action of $x \in \h^*$ on $\Sym(\h)$ (defined similarly to $D_y$ above).
+where for $x \in \h^*$ we denote by $D_x$ the Dunkl operator implementing the action of $\HH_{1, c}(\h^*)$ on its polynomial representation $\Sym(\h)$.
 
@@
 \begin{proof}
-It suffices to show that if $x_1,\dots,x_{n} \in k$ satisfy $f_i(x_1,\dots,x_{n})=0$ for all $i$, then $x_1=\dots=x_{n}=0$.
-Suppose that the $x_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.
+It suffices to show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
+Suppose that the $\alpha_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.
 In these terms, we have that

### 2015-09-27 submission3.tex
third submission

--- 2015-06-14 submission2.tex
@@
 \title{The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$}
-\author[mit]{Sheela~Devadas\corref{cor1}}
-\ead{sheelad@mit.edu}
+\author[stan]{Sheela~Devadas\corref{cor1}}
+\ead{sheelad@stanford.edu}
 \author[mit]{Yi~Sun}
@@
 \cortext[cor1]{Corresponding author}
+\address[stan]{Stanford University, 450 Serra Mall, Stanford, CA 94305}
 \address[mit]{Massachusetts Institute of Technology, 77 Massachusetts Ave., Cambridge MA 02139}

### 2016-01-11 submission3r1.tex
referee revisions

--- 2015-09-27 submission3.tex
@@
 \]
-In particular, all $\lambda_i$ have common value $\lambda \in k$ solving $(1-c(n-1))\lambda = 0$, which for generic $c$ implies that $\lambda = 0$, giving linear independence.
+In particular, all $\lambda_i$ have common value $\lambda \in k$ solving $(1-c(n-1))\lambda = 0$, which for $c \ne -1$ and hence for $c$ generic implies that $\lambda = 0$, giving linear independence.
 
@@
 \]
-and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
+and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For $c \ne 1,2,\dots,(p-1)/2$ and hence for generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
 \[
@@
 In this section, we will show that $A/I_c$ is a complete intersection, for which we require some preparatory computations.
+
+In the general case of an ideal $I$ in a polynomial ring $k[X_1,\dots,X_n]$, $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ is generated by $l$ elements with $\dim k[X_1,\dots,X_n]/I=m-l$.
 
@@
 \]
-so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$, which is nonzero for $c$ generic and $\prod_i s_i \ne 0$.
+so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$.
+This coefficient is nonzero for $c \ne \frac{l+r}{\sum_i m_i}$ (hence for generic $c$) and $\prod_i s_i \ne 0$.
 Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$.
@@
 \begin{proof}
-It suffices to show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
-Suppose that the $\alpha_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.
-In these terms, we have that
+By Proposition~\ref{prop:linind}, $I_c$ has $n-1$ linearly independent generators $\{f_i\}$.
+Hence we wish to show that $A/I_c$ has dimension $0$, for which it suffices to show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
+
+Suppose that the $\alpha_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.  In these terms, we have that 
 \[
@@
 Therefore, we find $r=1$ and $s_1=0$, concluding the proof.
+
+We apply Lemma~\ref{lem:resbyparts} finitely many times with finitely many choices of $l,r,m_i$  and hence we need only avoid the finite set of values $\{\frac{l+r}{\sum_i m_i}\} \cup \{1,\dots,(p-1)/2\}$ in order that Lemma~\ref{lem:resbyparts} may be applied and for the $f_i$ to be linearly independent according to Proposition~\ref{prop:linind}.
+For $c$ avoiding this finite set of values, $A/I_c$ is a complete intersection; hence this is true for generic $c$.
 \end{proof}

### 2016-01-12 submission3r1.tex
Fix complete intersection statements

@@
 Consider the ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
-In this section, we will show that $A/I_c$ is a complete intersection, for which we require some preparatory computations.
-
-In the general case of an ideal $I$ in a polynomial ring $k[X_1,\dots,X_n]$, $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ is generated by $l$ elements with $\dim k[X_1,\dots,X_n]/I=m-l$.
+In this section, we will show that $A/I_c$ is a complete intersection.
+Recall that for an ideal $I \subset k[X_1,\dots,X_m]$, the quotient ring $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ has a minimal set of generators $g_1, \ldots, g_l$ with $\dim k[X_1,\dots,X_m]/I = m - l$.
+We require now some preparatory computations.
 
@@
 \begin{proof}
-By Proposition~\ref{prop:linind}, $I_c$ has $n-1$ linearly independent generators $\{f_i\}$.
-Hence we wish to show that $A/I_c$ has dimension $0$, for which it suffices to show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
+By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $\{f_i\}$ in degree $p$.
+We will now show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
+This will imply that $\supp A/I_c = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
 

### 2016-01-14 submission3r1.tex
Specify c range, add todo

@@
 \]
-and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For $c \ne 1,2,\dots,(p-1)/2$ and hence for generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
+and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For $c \notin \{1,2,\dots,(p-1)/2\}$ and hence for generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
 \[
@@
 Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.
-For generic $c$ and any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
+For generic $c$ and any non-negative integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
 \end{lemma}
@@
 so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$.
-This coefficient is nonzero for $c \ne \frac{l+r}{\sum_i m_i}$ (hence for generic $c$) and $\prod_i s_i \ne 0$.
+This coefficient is nonzero since $\prod_i s_i \ne 0$ and $c \ne \frac{l+r}{\sum_i m_i}$ for generic $c$.
+
+\todo[inline]{This does not work if $\sum_i m_i = 0$ and $l + r = 0$, which is where we use it.}
+
  Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
 \end{proof}
+
+\begin{remark}
+In Lemma \ref{lem:resbyparts}, $c$ must be generic in the sense that it must avoid finitely many values for each choice of $(l, r, \{m_i\})$.
+\end{remark}
 
@@
 Therefore, we find $r=1$ and $s_1=0$, concluding the proof.
-
-We apply Lemma~\ref{lem:resbyparts} finitely many times with finitely many choices of $l,r,m_i$  and hence we need only avoid the finite set of values $\{\frac{l+r}{\sum_i m_i}\} \cup \{1,\dots,(p-1)/2\}$ in order that Lemma~\ref{lem:resbyparts} may be applied and for the $f_i$ to be linearly independent according to Proposition~\ref{prop:linind}.
-For $c$ avoiding this finite set of values, $A/I_c$ is a complete intersection; hence this is true for generic $c$.
 \end{proof}
@@
 
+\begin{remark}
+In the proof of Proposition \ref{prop:ci}, we require that $c$ avoids $\{-1, 1,\dots,(p-1)/2\}$ for Proposition \ref{prop:linind} and that $c$ avoids $\{\frac{l+r}{\sum_i m_i}\}$ for each of the finitely many applications of Lemma~\ref{lem:resbyparts}.
+These are the only uses of the assumption that $c$ is generic, so Proposition \ref{prop:ci} and Theorem \ref{thm:main} hold for $c$ avoiding this finite set of values.
+\end{remark}
+
 \bibliographystyle{alpha}

### 2016-01-20 submission3r1.tex
Replace argument for complete intersection

--- 2016-01-12 submission3r1.tex
@@
 \newcommand{\sspan}{\text{span}}
+\newcommand{\wF}{\widetilde{F}}
+\newcommand{\supp}{\text{supp}}
 
@@
 
+We now show that the $f_i$ are singular vectors summing to $0$.
+
+\begin{lemma} \label{lem:sum-zero}
+For $c \neq 0$, we have $\sum_{i = 1}^n f_i = 0$.
+\end{lemma}
+\begin{proof}
+By Lemma \ref{lem:dFdz}, we have that
+\[
+zF'(z) = z V(z) - \sum_{j = 1}^n \frac{cx_jz}{1 - x_j z} F(z) = z V(z) - c \sum_{j = 1}^n \frac{1 - x_j z} F(z),
+\]
+where we subtract $ncF(z)$ in the second equality.
+Notice that $[z^p]$ coefficient of the left side is $0$ because $[z^{p - 1}] F'(z) = 0$ and that $[z^p] zV(z) = 0$.
+Therefore, we conclude that $c \sum_i f_i = 0$, giving the desired.
+\end{proof}
+
 \begin{proposition}\label{prop:ann} 
@@
 Recall that for an ideal $I \subset k[X_1,\dots,X_m]$, the quotient ring $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ has a minimal set of generators $g_1, \ldots, g_l$ with $\dim k[X_1,\dots,X_m]/I = m - l$.
-We require now some preparatory computations.
-
-\subsection{Computations of derivatives}
-
-Our goal in this subsection is to establish Lemma \ref{lem:resbyparts}, which is a formal power series analogue of \cite[Lemma 3.4]{CE}.
-Our method will be an adaptation of the ``residues by parts'' argument which appears there.
-First, we require some direct computations of derivatives.
-
-For any $s_1,\dots,s_{r}$ distinct elements of $k$ and positive integers $m_1,\dots,m_r$, we define 
-\[
-g(z)=\prod_{i=1}^{r} (1-s_iz)^{m_i} \text{  and } F(z)=\sum_{m=0}^{p-1} \binom{c}{m}(g(z)-1)^m
-\]
-as an analogue of $g(z)$ and $F(z)$ from the previous section. We also let $a(z)$ be the formal power series
-\[
-a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
-\]
-and define the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ for $i=1, \dots, r$.
-
-\begin{lemma}\label{lem:vand}Let $s_1, \ldots, s_{r }$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ are linearly independent.
-\end{lemma}
-\begin{proof}
-Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
-Let $w_i(z)= \prod_{j \neq i} (z-s_j)$.
-Then we see that $\sum_i \lambda_iw_i(1/z)=\sum_i \lambda_i b_i(z)/z^{r-1}=0$, so $\sum_i \lambda_i w_i(z)=0$.
-Since the $s_i$ are distinct, we see that $w_i(s_i) \ne 0$ and $w_i(s_j)=0$ for all $i \neq j$.
-Therefore by evaluating $\sum_i \lambda_i w_i(z)=0$ at $z=s_1,\dots,s_r$ we see that $\lambda_iw_i(s_i)=0$ for all $i$, so $\lambda_i=0$ for all $i$.
-Then $b_i(z)$ are linearly independent.
-\end{proof}
-
-\begin{corollary}\label{corr:dFdz2}
-Let $s_1,\dots,s_{r}$ be distinct elements of $k$ and $m_i$ positive integers such that $\sum_i m_is_i=0$.  
-For some $V(z)$ satisfying $[z^l]V(z)=0$ for $0 \le l \le p-1$, we have
-\[
-F'(z)=V(z) - \sum_j \frac{cm_js_j}{1-s_jz}F(z).
-\]
-\end{corollary}
-\begin{proof}
-Take the variables $x_j$ to consist of $m_i$ copies of each $s_i$ in Lemma~\ref{lem:dFdz}.
-\end{proof}
-
-\begin{lemma} \label{lem:resbyparts}
-Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.
-For generic $c$ and any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
-\end{lemma}
-\begin{proof} 
-We will use an analogue of ``residues by parts'' in a formal power series setting.   We first show that 
-\[
-a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z)
-\]
-for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)-\sum_j \frac{cm_js_j}{1-s_jz}F(z)$. We now compute
-\begin{align*}
-a'(z)=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
-&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)-\sum_j \frac{cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
-\end{align*}
-The fact that $[z^l]V(z)=0$ for $0 \le l \le p-1$ then gives the claim.
-
-Now, for any integer $l$, define the Laurent polynomial $h_l(z)=z^{-l-r}\prod_i(1-s_iz)$. Notice that
-\begin{align*}
-\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) + h_l(z) a'(z) \\
-&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
-&= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
-\end{align*}
-We note that 
-\[
--\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z)
-\]
-is a Laurent polynomial with lowest degree term 
-\[
-- z^{-l-r-1} \left(l + r + \sum_i s_i m_i c\right) = - z^{-l-r-1}(l+ r)
-\]
-and highest degree term 
-\[
-- z^{-l - 1} (-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right).
-\]
-The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$. We always have 
-\[
-[z^{-1}]\,\frac{d}{dz}( h_l(z) a(z))=0,
-\]
-so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$.
-This coefficient is nonzero for $c \ne \frac{l+r}{\sum_i m_i}$ (hence for generic $c$) and $\prod_i s_i \ne 0$.
-Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$.
-\end{proof}
-
-\subsection{Complete intersection property}
-
-We now show that $A/I_c$ is a complete intersection.  Our technique is a translation of the idea of the proof of \cite[Theorem 3.2]{CE} to the formal power series context.
 
@@
 By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $\{f_i\}$ in degree $p$.
-We will now show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
-This will imply that $\supp A/I_c = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
+We will now show that for generic $c$, if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for $i = 1, \ldots, n$, then $\alpha_1=\dots=\alpha_{n}=0$.
+Because $f_n$ lies in the span of $f_1, \ldots, f_{n - 1}$ for $c \neq 0$ by Lemma \ref{lem:sum-zero}, this will imply that $\supp(A/I_c) = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
 
-Suppose that the $\alpha_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.  In these terms, we have that 
+Suppose that the $\alpha_i$ take values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i > 0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$, $\sum_i m_i s_i = 0$, and $\sum_i m_i = n$.
+We claim that for generic $c$ this implies $s_i = 0$ for all $i$.
+Let $B = k[s_1, \ldots, s_r]/(\sum_i m_i s_i = 0)$; it suffices to check that with $I_c$ interpreted as an ideal in $B$, the quotient $B/I_c$ is finite dimensional over $k$.
+
+Define the polynomial $h(z) = \prod_{i = 1}^r (z - s_i)$, and let the series expansion of $F(z)$ be given by 
 \[
-[z^p]\frac{1}{1-s_iz}F(z)= 0
+F(z) = \sum_{i \geq 0} a_i(s_1, \ldots, s_r, c) z^i,
 \]
-for $i = 1, \ldots, r $ and wish to show that $r=1$ and $s_1=0$.
+where $a_i$ has degree $i$ in $s_1, \ldots, s_r$ and $a_0(s_1, \ldots, s_r, c) = 1$.  Define a degree $p$ polynomial in $z$ by
+\[
+\wF(z; s_1, \ldots, s_r, c) := \sum_{i = 0}^p a_i(s_1, \ldots, s_r, c) z^{p - i}.
+\]
+In this notation, we have that 
+\[
+f_i = [z^p]\frac{1}{1-s_iz}F(z) = \wF(s_i; s_1, \ldots, s_r, c) = 0
+\]
+for $i = 1, \ldots, r$.  Notice that $\wF(s_i; s_1, \ldots, s_r, c)$ is a polynomial in $s_1, \ldots, s_r$ of homogeneous degree $p$.  By the definition of $F(z)$, we have
+\[
+\wF(z; s_1, \ldots, s_r, 0) = z^p,
+\]
+meaning that if $c = 0$, we have $s_1 = \cdots = s_r = 0$, hence $B/I_0$ is finite dimensional over $k$.
 
-We first claim that at least one $s_i$ is $0$. Suppose for the sake of contradiction that $\prod_i s_i \ne 0$.  We recall
-\[
-a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
-\]
-as in Lemma~\ref{lem:resbyparts}.  Recall that $b_i(z)=\prod_{j \ne i} (1-s_jz)$ for $i=1,\dots,r$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-s_iz}F(z)$ so in particular 
-\[
-[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-s_iz}F(z)=0.
-\]
-Therefore for any $\lambda_i \in k$, we have
-\begin{equation}\label{eq:lincomb}
-\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p] \,a(z)\sum_{i=1}^{r}\lambda_ib_i(z)=0.
-\end{equation}
-By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$.
-Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that $\sum_i\lambda_i^mb_i(z)=z^m$.
-Choosing these $\lambda_i^m$ in (\ref{eq:lincomb}), we see that
-\[
-[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0.
-\]
-By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$ (but finitely many times and with finitely many choices of $l$, $r$, and $m_i$), we find for generic $c$ that
-\[
-[z^l]a(z)=0 \text{ for $l=p-r,p-r-1,\dots,0$}.
-\]
-This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $s_i=0$ for some $i$.
+Now, let $B^d$ and $I_c^d$ denote the degree $d$ pieces of $B$ and the homogeneous ideal $I_c$, respectively.
+Choose a monomial basis $\{t_i\}$ for $B^d$ independent of $c$, and let $I_c^d$ be spanned by a finite set of polynomials $\{g_j\}$ with $g_j = \sum_i h_{ji}(c) t_i$.
+Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies is the vanishing ideal of all $\dim B^d$ minors of $H$.
+This implies that for all but finitely many $c$ we have $\dim I^d_c = \dim B^d$ and hence $B/I_c$ is finite-dimensional over $k$.
 
-Now, suppose without loss of generality that $s_{r}=0$.
-If $r = 1$, we are done.
-Otherwise, we have $\sum_{i=1}^{r-1} m_is_i = \sum_{i=1}^{r} m_is_i = 0$ and because the $s_i$ are distinct we see that $\prod_{i=1}^{r-1} s_i \ne 0$.
-Therefore, we may apply Lemma~\ref{lem:resbyparts} and repeat the argument above with $s_1, \ldots, s_{r - 1}$.
-We find that at least one of the $s_i$ with $i < r$ is $0$, contradicting distinctness of $s_i$.
-Therefore, we find $r=1$ and $s_1=0$, concluding the proof.
-
-We apply Lemma~\ref{lem:resbyparts} finitely many times with finitely many choices of $l,r,m_i$  and hence we need only avoid the finite set of values $\{\frac{l+r}{\sum_i m_i}\} \cup \{1,\dots,(p-1)/2\}$ in order that Lemma~\ref{lem:resbyparts} may be applied and for the $f_i$ to be linearly independent according to Proposition~\ref{prop:linind}.
-For $c$ avoiding this finite set of values, $A/I_c$ is a complete intersection; hence this is true for generic $c$.
+For each of the finitely many choices of $r, m_1, \ldots, m_r > 0$ with $\sum_i m_i = n$, we conclude that for all but finitely many $c$, if $\{\alpha_1, \ldots, \alpha_n\}$ contains $s_i$ with multiplicity $s_i$, then $\alpha_1 = \cdots = \alpha_n = 0$.
+Taking the union over excluded possibilities for $c$, we conclude that $f_i(\alpha_1, \ldots, \alpha_n) = 0$ implies $\alpha_1 = \cdots = \alpha_n = 0$ unconditionally for generic $c$, so $A/I_c$ is a complete intersection as desired.
 \end{proof}
 
+\begin{remark}
+Proposition \ref{prop:ci} is a formal power series analogue of \cite[Theorem 3.2]{CE}.
+However, our proof differs from the ``residues by parts'' argument which appears there, as the crucial \cite[Lemma 3.2]{CE} fails in the modular case.
+It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as no analogue of the polynomial $\wF(z; s_1, \ldots, s_r, c)$ exists in that setting.
+\end{remark}
+
 \section{Proof of the main result}
+
+We now put everything together to obtain our main result.
 
@@
 
+\begin{remark}
+In the proof of Proposition \ref{prop:ci}, we require that $c$ avoids $0$ for Lemma \ref{lem:sum-zero}, $c$ avoids $\{-1, 1,\dots,(p-1)/2\}$ for Proposition \ref{prop:linind}, and that $c$ avoids a non-explicit finite set given by vanishing of a determinantal ideal.
+These are the only uses of the assumption that $c$ is generic, so Proposition \ref{prop:ci} and Theorem \ref{thm:main} hold for $c$ avoiding these values.
+\end{remark}
+
 \bibliographystyle{alpha}

### 2016-01-21 submission3r1.tex
small typo corrections

@@
 
-For a formal Laurent series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.
+For a formal power series $r(z)$, we denote by $[z^l] r(z)$ the coefficient of $z^l$ in $r(z)$.
 Throughout the paper, we will consider formal power series in $z$ considered as expansions of rational functions around $z = 0$.
@@
 \[
-zF'(z) = z V(z) - \sum_{j = 1}^n \frac{cx_jz}{1 - x_j z} F(z) = z V(z) - c \sum_{j = 1}^n \frac{1 - x_j z} F(z),
+zF'(z) = z V(z) - \sum_{j = 1}^n \frac{cx_jz}{1 - x_j z} F(z) = z V(z) - c \sum_{j = 1}^n \frac{1}{1 - x_j z} F(z),
 \]
@@
 Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
-On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies is the vanishing ideal of all $\dim B^d$ minors of $H$.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies in the vanishing ideal of all $\dim B^d$ minors of $H$.
 This implies that for all but finitely many $c$ we have $\dim I^d_c = \dim B^d$ and hence $B/I_c$ is finite-dimensional over $k$.
 
-For each of the finitely many choices of $r, m_1, \ldots, m_r > 0$ with $\sum_i m_i = n$, we conclude that for all but finitely many $c$, if $\{\alpha_1, \ldots, \alpha_n\}$ contains $s_i$ with multiplicity $s_i$, then $\alpha_1 = \cdots = \alpha_n = 0$.
+For each of the finitely many choices of $r, m_1, \ldots, m_r > 0$ with $\sum_i m_i = n$, we conclude that for all but finitely many $c$, if $\{\alpha_1, \ldots, \alpha_n\}$ contains $s_i$ with multiplicity $m_i$, then $\alpha_1 = \cdots = \alpha_n = 0$.
 Taking the union over excluded possibilities for $c$, we conclude that $f_i(\alpha_1, \ldots, \alpha_n) = 0$ implies $\alpha_1 = \cdots = \alpha_n = 0$ unconditionally for generic $c$, so $A/I_c$ is a complete intersection as desired.

### 2016-01-21 submission3r1.tex
Remove use of vanishing ideal

@@
 Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
-On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies in the vanishing ideal of all $\dim B^d$ minors of $H$.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies in the zero set of all $\dim B^d$ minors of $H$.
 This implies that for all but finitely many $c$ we have $\dim I^d_c = \dim B^d$ and hence $B/I_c$ is finite-dimensional over $k$.

### 2016-01-21 formalwriteup.tex
edits to formalwriteup

@@
 
-Then the polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
+The polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
 By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ of positive degree that are killed by all Dunkl operators $D_y$.
@@
 
+We now show that the $f_i$ are singular vectors summing to $0$.
+
+\begin{lemma} \label{lem:sum-zero}
+For $c \neq 0$, we have $\sum_{i = 1}^n f_i = 0$.
+\end{lemma}
+\begin{proof}
+By Lemma \ref{lem:dFdz}, we have that
+\[
+zF'(z) = z V(z) - \sum_{j = 1}^n \frac{cx_jz}{1 - x_j z} F(z) = z V(z) - c \sum_{j = 1}^n \frac{1}{1 - x_j z} F(z),
+\]
+where we subtract $ncF(z)$ in the second equality.
+Notice that $[z^p]$ coefficient of the left side is $0$ because $[z^{p - 1}] F'(z) = 0$ and that $[z^p] zV(z) = 0$.
+Therefore, we conclude that $c \sum_i f_i = 0$, giving the desired.
+\end{proof}
+
 \begin{proposition}\label{prop:ann} 
@@
 \]
-and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
+and $[z^p]F_i(z)=f_i=0$ for $i < n$ and $i \neq j$. For $c \notin \{1,2,\dots,(p-1)/2\}$ and hence for generic $c$, we have $\binom{c-1}{(p-1)/2} \ne 0$, meaning that 
 \[
@@
 Consider the ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
-In this section, we will show that $A/I_c$ is a complete intersection, for which we require some preparatory computations.
-
-\subsection{Computations of derivatives}
-
-Our goal in this subsection is to establish Lemma \ref{lem:resbyparts}, which is a formal power series analogue of \cite[Lemma 3.4]{CE}.
-Our method will be an adaptation of the ``residues by parts'' argument which appears there.
-First, we require some direct computations of derivatives.
-
-For any $s_1,\dots,s_{r}$ distinct elements of $k$ and positive integers $m_1,\dots,m_r$, we define 
-\[
-g(z)=\prod_{i=1}^{r} (1-s_iz)^{m_i} \text{  and } F(z)=\sum_{m=0}^{p-1} \binom{c}{m}(g(z)-1)^m
-\]
-as an analogue of $g(z)$ and $F(z)$ from the previous section. We also let $a(z)$ be the formal power series
-\[
-a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
-\]
-and define the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ for $i=1, \dots, r$.
-
-\begin{lemma}\label{lem:vand}Let $s_1, \ldots, s_{r }$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ are linearly independent.
-\end{lemma}
-\begin{proof}
-Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.
-Let $w_i(z)= \prod_{j \neq i} (z-s_j)$.
-Then we see that $\sum_i \lambda_iw_i(1/z)=\sum_i \lambda_i b_i(z)/z^{r-1}=0$, so $\sum_i \lambda_i w_i(z)=0$.
-Since the $s_i$ are distinct, we see that $w_i(s_i) \ne 0$ and $w_i(s_j)=0$ for all $i \neq j$.
-Therefore by evaluating $\sum_i \lambda_i w_i(z)=0$ at $z=s_1,\dots,s_r$ we see that $\lambda_iw_i(s_i)=0$ for all $i$, so $\lambda_i=0$ for all $i$.
-Then $b_i(z)$ are linearly independent.
-\end{proof}
-
-\begin{corollary}\label{corr:dFdz2}
-Let $s_1,\dots,s_{r}$ be distinct elements of $k$ and $m_i$ positive integers such that $\sum_i m_is_i=0$.  
-For some $V(z)$ satisfying $[z^l]V(z)=0$ for $0 \le l \le p-1$, we have
-\[
-F'(z)=V(z) - \sum_j \frac{cm_js_j}{1-s_jz}F(z).
-\]
-\end{corollary}
-\begin{proof}
-Take the variables $x_j$ to consist of $m_i$ copies of each $s_i$ in Lemma~\ref{lem:dFdz}.
-\end{proof}
-
-\begin{lemma} \label{lem:resbyparts}
-Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.
-For generic $c$ and any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
-\end{lemma}
-\begin{proof} 
-We will use an analogue of ``residues by parts'' in a formal power series setting.   We first show that 
-\[
-a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z)
-\]
-for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)-\sum_j \frac{cm_js_j}{1-s_jz}F(z)$. We now compute
-\begin{align*}
-a'(z)=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
-&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)-\sum_j \frac{cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
-&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
-\end{align*}
-The fact that $[z^l]V(z)=0$ for $0 \le l \le p-1$ then gives the claim.
-
-Now, for any integer $l$, define the Laurent polynomial $h_l(z)=z^{-l-r}\prod_i(1-s_iz)$. Notice that
-\begin{align*}
-\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) + h_l(z) a'(z) \\
-&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
-&= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
-\end{align*}
-We note that 
-\[
--\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z)
-\]
-is a Laurent polynomial with lowest degree term 
-\[
-- z^{-l-r-1} \left(l + r + \sum_i s_i m_i c\right) = - z^{-l-r-1}(l+ r)
-\]
-and highest degree term 
-\[
-- z^{-l - 1} (-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right).
-\]
-The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$. We always have 
-\[
-[z^{-1}]\,\frac{d}{dz}( h_l(z) a(z))=0,
-\]
-so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$, which is nonzero for $c$ generic and $\prod_i s_i \ne 0$.
-Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$.
-\end{proof}
-
-\subsection{Complete intersection property}
-
-We now show that $A/I_c$ is a complete intersection.  Our technique is a translation of the idea of the proof of \cite[Theorem 3.2]{CE} to the formal power series context.
+In this section, we will show that $A/I_c$ is a complete intersection.
+Recall that for an ideal $I \subset k[X_1,\dots,X_m]$, the quotient ring $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ has a minimal set of generators $g_1, \ldots, g_l$ with $\dim k[X_1,\dots,X_m]/I = m - l$.
 
@@
 \begin{proof}
-It suffices to show that if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for all $i$, then $\alpha_1=\dots=\alpha_{n}=0$.
-Suppose that the $\alpha_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.
-In these terms, we have that
+By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $\{f_i\}$ in degree $p$.
+We will now show that for generic $c$, if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for $i = 1, \ldots, n$, then $\alpha_1=\dots=\alpha_{n}=0$.
+Because $f_n$ lies in the span of $f_1, \ldots, f_{n - 1}$ for $c \neq 0$ by Lemma \ref{lem:sum-zero}, this will imply that $\supp(A/I_c) = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
+
+Suppose that the $\alpha_i$ take values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i > 0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$, $\sum_i m_i s_i = 0$, and $\sum_i m_i = n$.
+We claim that for generic $c$ this implies $s_i = 0$ for all $i$.
+Let $B = k[s_1, \ldots, s_r]/(\sum_i m_i s_i = 0)$; it suffices to check that with $I_c$ interpreted as an ideal in $B$, the quotient $B/I_c$ is finite dimensional over $k$.
+
+Define the polynomial $h(z) = \prod_{i = 1}^r (z - s_i)$, and let the series expansion of $F(z)$ be given by 
 \[
-[z^p]\frac{1}{1-s_iz}F(z)= 0
+F(z) = \sum_{i \geq 0} a_i(s_1, \ldots, s_r, c) z^i,
 \]
-for $i = 1, \ldots, r $ and wish to show that $r=1$ and $s_1=0$.
+where $a_i$ has degree $i$ in $s_1, \ldots, s_r$ and $a_0(s_1, \ldots, s_r, c) = 1$.  Define a degree $p$ polynomial in $z$ by
+\[
+\wF(z; s_1, \ldots, s_r, c) := \sum_{i = 0}^p a_i(s_1, \ldots, s_r, c) z^{p - i}.
+\]
+In this notation, we have that 
+\[
+f_i = [z^p]\frac{1}{1-s_iz}F(z) = \wF(s_i; s_1, \ldots, s_r, c) = 0
+\]
+for $i = 1, \ldots, r$.  Notice that $\wF(s_i; s_1, \ldots, s_r, c)$ is a polynomial in $s_1, \ldots, s_r$ of homogeneous degree $p$.  By the definition of $F(z)$, we have
+\[
+\wF(z; s_1, \ldots, s_r, 0) = z^p,
+\]
+meaning that if $c = 0$, we have $s_1 = \cdots = s_r = 0$, hence $B/I_0$ is finite dimensional over $k$.
 
-We first claim that at least one $s_i$ is $0$. Suppose for the sake of contradiction that $\prod_i s_i \ne 0$.  We recall
-\[
-a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
-\]
-as in Lemma~\ref{lem:resbyparts}.  Recall that $b_i(z)=\prod_{j \ne i} (1-s_jz)$ for $i=1,\dots,r$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-s_iz}F(z)$ so in particular 
-\[
-[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-s_iz}F(z)=0.
-\]
-Therefore for any $\lambda_i \in k$, we have
-\begin{equation}\label{eq:lincomb}
-\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p] \,a(z)\sum_{i=1}^{r}\lambda_ib_i(z)=0.
-\end{equation}
-By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$.
-Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that $\sum_i\lambda_i^mb_i(z)=z^m$.
-Choosing these $\lambda_i^m$ in (\ref{eq:lincomb}), we see that
-\[
-[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0.
-\]
-By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$ (but finitely many times and with finitely many choices of $l$, $r$, and $m_i$), we find for generic $c$ that
-\[
-[z^l]a(z)=0 \text{ for $l=p-r,p-r-1,\dots,0$}.
-\]
-This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $s_i=0$ for some $i$.
+Now, let $B^d$ and $I_c^d$ denote the degree $d$ pieces of $B$ and the homogeneous ideal $I_c$, respectively.
+Choose a monomial basis $\{t_i\}$ for $B^d$ independent of $c$, and let $I_c^d$ be spanned by a finite set of polynomials $\{g_j\}$ with $g_j = \sum_i h_{ji}(c) t_i$.
+Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies in the zero set of all $\dim B^d$ minors of $H$.
+This implies that for all but finitely many $c$ we have $\dim I^d_c = \dim B^d$ and hence $B/I_c$ is finite-dimensional over $k$.
 
-Now, suppose without loss of generality that $s_{r}=0$.
-If $r = 1$, we are done.
-Otherwise, we have $\sum_{i=1}^{r-1} m_is_i = \sum_{i=1}^{r} m_is_i = 0$ and because the $s_i$ are distinct we see that $\prod_{i=1}^{r-1} s_i \ne 0$.
-Therefore, we may apply Lemma~\ref{lem:resbyparts} and repeat the argument above with $s_1, \ldots, s_{r - 1}$.
-We find that at least one of the $s_i$ with $i < r$ is $0$, contradicting distinctness of $s_i$.
-Therefore, we find $r=1$ and $s_1=0$, concluding the proof.
+For each of the finitely many choices of $r, m_1, \ldots, m_r > 0$ with $\sum_i m_i = n$, we conclude that for all but finitely many $c$, if $\{\alpha_1, \ldots, \alpha_n\}$ contains $s_i$ with multiplicity $m_i$, then $\alpha_1 = \cdots = \alpha_n = 0$.
+Taking the union over excluded possibilities for $c$, we conclude that $f_i(\alpha_1, \ldots, \alpha_n) = 0$ implies $\alpha_1 = \cdots = \alpha_n = 0$ unconditionally for generic $c$, so $A/I_c$ is a complete intersection as desired.
 \end{proof}
 
+\begin{remark}
+Proposition \ref{prop:ci} is a formal power series analogue of \cite[Theorem 3.2]{CE}.
+However, our proof differs from the ``residues by parts'' argument which appears there, as the crucial \cite[Lemma 3.2]{CE} fails in the modular case.
+It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as no analogue of the polynomial $\wF(z; s_1, \ldots, s_r, c)$ exists in that setting.
+\end{remark}
+
 \section{Proof of the main result}
+
+We now put everything together to obtain our main result.
 

### 2016-03-28 submission3r2.tex
Make minor referee edits

--- 2016-01-21 submission3r1.tex
@@
 \[
-\HH_{\hbar,c}(\h) = \Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*).
+\HH_{\hbar,c}(\h) \simeq \Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*).
 \]
@@
 The polynomial representation $\Sym(\h^*)$ has unique maximal graded proper submodule $J_c = \ker(\beta_c)$.
-By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ of positive degree that are killed by all Dunkl operators $D_y$.
+By the definition of $\beta_c$, $J_c$ contains the ideal generated by all homogeneous vectors $f \in A$ of positive degree that lie in the kernel of all Dunkl operators $D_y$.
 Such $f$ are known as \textit{singular vectors}.
@@
 The remainder of this paper is organized as follows.
-In Section 2, we check that the generators $f_i$ are linearly independent singular vectors.
+In Section 2, we check that the generators $f_1, \ldots, f_{n - 1}$ are linearly independent singular vectors.
 In Section 3, we show that they cut out a complete intersection.
@@
 
-We now show that the $f_i$ are singular vectors summing to $0$.
+We now show that $f_1, \ldots, f_n$ are singular vectors summing to $0$.
 
@@
 Notice that $[z^p]$ coefficient of the left side is $0$ because $[z^{p - 1}] F'(z) = 0$ and that $[z^p] zV(z) = 0$.
-Therefore, we conclude that $c \sum_i f_i = 0$, giving the desired.
+Therefore, we conclude that $c \sum_{i = 1}^n f_i = 0$, giving the desired.
 \end{proof}
@@
 \begin{proposition}\label{prop:ann} 
-The elements $f_i$ for $i=1,\dots,n-1$ are singular vectors in $A$.
+The elements $f_1, \ldots, f_{n - 1}$ are singular vectors in $A$.
 \end{proposition}
 \begin{proof}
-We must show that $f_i$ is annihilated by $D_{y_j - y_l}$ for all $j \ne l$.
+We must show that for $i = 1, \ldots, n - 1$, $f_i$ is annihilated by $D_{y_j - y_l}$ for all $j \ne l$.
 First, by symmetry it suffices to consider $f_1$.
@@
 \]
-Because $F_1(z)$ is invariant under $s_{ij}$ for $i,j > 1$, we now compute
-\begin{align*}
-D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)F_1(z)\\
-&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}F_1(z)+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
-&=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
-&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z).
-\end{align*}
-To show that the $z^p$ coefficient in $D_{y_2-y_1}(F_1(z))$ vanishes, we must consider $\frac{\partial F_1}{\partial z}$.  By Lemma~\ref{lem:dFdz}, we have
+Finally, by Lemma~\ref{lem:dFdz}, we have
 \[
@@
 \end{align*}
-We now compute
+Because $F_1(z)$ is invariant under $s_{ij}$ for $i,j > 1$, we now compute
 \begin{align*}
-D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z)\\
+D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)F_1(z)\\
+&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}F_1(z)+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
+&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z)\\
 &=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z) + \sum_{j} \left(\frac{zc}{1-x_jz} - zc\right) F_1(z)\\
@@
 \end{align*}
-where in the second step we have subtracted $n zc F_1(z)$.
+where in the fifth step we have subtracted $n zc F_1(z)$.
 We note that $[z^p]\,\frac{G(z)+z^2V(z)}{1-x_1z}$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$, hence a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$.
@@
 
-\subsection{Proof of linear independence of $f_i$}
+\subsection{Proof of linear independence of $f_1, \ldots, f_{n-1}$}
 
@@
 \begin{proof}
-By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $\{f_i\}$ in degree $p$.
+By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $f_1, \ldots, f_{n-1}$ in degree $p$.
 We will now show that for generic $c$, if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for $i = 1, \ldots, n$, then $\alpha_1=\dots=\alpha_{n}=0$.
@@
 for a polynomial $h(t)$ with nonnegative integer coefficients.
-On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I_c$ is a complete intersection with $n-1$ linearly independent degree $p$ generators $f_i$.
+On the other hand, by Propositions~\ref{prop:linind} and \ref{prop:ci}, $A/I_c$ is a complete intersection with $n-1$ linearly independent degree $p$ generators $f_1, \ldots, f_{n-1}$.
 Its Hilbert series is
@@
 \]
-By Proposition~\ref{prop:ann}, the generators $f_i$ of $I_c$ are singular vectors, so $I_c \subseteq J_c$, implying that $h_{A/I_c}(t) \ge h_{A/J_c}(t)$ coefficient-wise.
+By Proposition~\ref{prop:ann}, the generators $f_1, \ldots, f_{n - 1}$ of $I_c$ are singular vectors, so $I_c \subseteq J_c$, implying that $h_{A/I_c}(t) \ge h_{A/J_c}(t)$ coefficient-wise.
 We conclude that $h(t) = 1$, hence $h_{A/I_c}(t)=h_{A/J_c}(t)$ and $I_c=J_c$, completing the proof.

### 2016-03-28 submission3r2.tex
Rewrite ci proof

@@
 \newcommand{\supp}{\text{supp}}
+\newcommand{\PP}{\mathbb{P}}
 
@@
 The authors thank P.
-Etingof for suggesting the problem and for helpful discussions.
+Etingof for suggesting the problem and for helpful discussions; the authors thank also the anonymous referee for comments leading to the streamlined proof of Proposition \ref{prop:ci} which appears here.
 Some exploratory computations were done using Sage.
@@
 
-\subsection{Proving $f_i$ are singular vectors}
-
-We now show that $f_1, \ldots, f_n$ are singular vectors summing to $0$.
-
-\begin{lemma} \label{lem:sum-zero}
-For $c \neq 0$, we have $\sum_{i = 1}^n f_i = 0$.
-\end{lemma}
-\begin{proof}
-By Lemma \ref{lem:dFdz}, we have that
-\[
-zF'(z) = z V(z) - \sum_{j = 1}^n \frac{cx_jz}{1 - x_j z} F(z) = z V(z) - c \sum_{j = 1}^n \frac{1}{1 - x_j z} F(z),
-\]
-where we subtract $ncF(z)$ in the second equality.
-Notice that $[z^p]$ coefficient of the left side is $0$ because $[z^{p - 1}] F'(z) = 0$ and that $[z^p] zV(z) = 0$.
-Therefore, we conclude that $c \sum_{i = 1}^n f_i = 0$, giving the desired.
-\end{proof}
+\subsection{Proving $f_1, \ldots, f_{n-1}$ are singular vectors}
 
@@
 
-Consider the ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
+Consider the homogeneous ideal $I_c = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.
 In this section, we will show that $A/I_c$ is a complete intersection.
-Recall that for an ideal $I \subset k[X_1,\dots,X_m]$, the quotient ring $k[X_1,\dots,X_m]/I$ is a complete intersection if $I$ has a minimal set of generators $g_1, \ldots, g_l$ with $\dim k[X_1,\dots,X_m]/I = m - l$.
+Recall from \cite[Example 11.8]{Har} that for a homogeneous ideal $I \subset k[X_0,\dots,X_m]$ with a minimal set of generators of size $l$, the quotient ring $k[X_0, \ldots, X_m]/I$ is a complete intersection if the closed projective subvariety of $\PP^m$ defined by $I$ has dimension $m - l$.
 
@@
 By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $f_1, \ldots, f_{n-1}$ in degree $p$.
-We will now show that for generic $c$, if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for $i = 1, \ldots, n$, then $\alpha_1=\dots=\alpha_{n}=0$.
-Because $f_n$ lies in the span of $f_1, \ldots, f_{n - 1}$ for $c \neq 0$ by Lemma \ref{lem:sum-zero}, this will imply that $\supp(A/I_c) = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
+Therefore $A/I_c$ is a complete intersection if and only $I_c$ cuts out a projective variety of dimension $(n - 2) - (n - 1) = -1$, meaning it is empty.
+This occurs if and only if the saturation of $I_c$ is $A$, which occurs if and only if $\dim_k(A/I_c) < \infty$.
 
-Suppose that the $\alpha_i$ take values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i > 0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$, $\sum_i m_i s_i = 0$, and $\sum_i m_i = n$.
-We claim that for generic $c$ this implies $s_i = 0$ for all $i$.
-Let $B = k[s_1, \ldots, s_r]/(\sum_i m_i s_i = 0)$; it suffices to check that with $I_c$ interpreted as an ideal in $B$, the quotient $B/I_c$ is finite dimensional over $k$.
-
-Define the polynomial $h(z) = \prod_{i = 1}^r (z - s_i)$, and let the series expansion of $F(z)$ be given by 
+If $c = 0$, by definition of $f_i$ we see that $f_i = x_i^p$.  Note that 
 \[
-F(z) = \sum_{i \geq 0} a_i(s_1, \ldots, s_r, c) z^i,
+f_n = x_n^p = (-x_1 - \cdots - x_{n-1})^p = - x_1^p - \cdots - x_{n - 1}^p = - f_1 - \cdots - f_{n -1} \in I_0,
 \]
-where $a_i$ has degree $i$ in $s_1, \ldots, s_r$ and $a_0(s_1, \ldots, s_r, c) = 1$.  Define a degree $p$ polynomial in $z$ by
-\[
-\wF(z; s_1, \ldots, s_r, c) := \sum_{i = 0}^p a_i(s_1, \ldots, s_r, c) z^{p - i}.
-\]
-In this notation, we have that 
-\[
-f_i = [z^p]\frac{1}{1-s_iz}F(z) = \wF(s_i; s_1, \ldots, s_r, c) = 0
-\]
-for $i = 1, \ldots, r$.  Notice that $\wF(s_i; s_1, \ldots, s_r, c)$ is a polynomial in $s_1, \ldots, s_r$ of homogeneous degree $p$.  By the definition of $F(z)$, we have
-\[
-\wF(z; s_1, \ldots, s_r, 0) = z^p,
-\]
-meaning that if $c = 0$, we have $s_1 = \cdots = s_r = 0$, hence $B/I_0$ is finite dimensional over $k$.
-
-Now, let $B^d$ and $I_c^d$ denote the degree $d$ pieces of $B$ and the homogeneous ideal $I_c$, respectively.
-Choose a monomial basis $\{t_i\}$ for $B^d$ independent of $c$, and let $I_c^d$ be spanned by a finite set of polynomials $\{g_j\}$ with $g_j = \sum_i h_{ji}(c) t_i$.
+meaning that $(x_1^p, \ldots, x_n^p) \subset I_0$ and hence $\dim_k(A/I_c) < \infty$.
+Now, let $A^d$ and $I_c^d$ denote the degree $d$ pieces of $A$ and $I_c$, respectively.
+Choose a monomial basis $\{t_i\}$ for $A^d$ independent of $c$, and let $I_c^d$ be spanned by a finite set of polynomials $\{g_j\}$ with $g_j = \sum_i h_{ji}(c) t_i$.
 Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
-On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies in the zero set of all $\dim B^d$ minors of $H$.
-This implies that for all but finitely many $c$ we have $\dim I^d_c = \dim B^d$ and hence $B/I_c$ is finite-dimensional over $k$.
-
-For each of the finitely many choices of $r, m_1, \ldots, m_r > 0$ with $\sum_i m_i = n$, we conclude that for all but finitely many $c$, if $\{\alpha_1, \ldots, \alpha_n\}$ contains $s_i$ with multiplicity $m_i$, then $\alpha_1 = \cdots = \alpha_n = 0$.
-Taking the union over excluded possibilities for $c$, we conclude that $f_i(\alpha_1, \ldots, \alpha_n) = 0$ implies $\alpha_1 = \cdots = \alpha_n = 0$ unconditionally for generic $c$, so $A/I_c$ is a complete intersection as desired.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I_0^d = A^d$, meaning that $\dim I_c^d < \dim A^d$ exactly when $c$ lies in the zero set of all size $\dim A^d$ minors of $H$.
+This implies that for all but finitely many $c$ we have $\dim I_c^d = \dim A^d$, hence $\dim_k(A/I_c) < \infty$ and $A/I_c$ is a complete intersection.
 \end{proof}
@@
 However, our proof differs from the ``residues by parts'' argument which appears there, as the crucial \cite[Lemma 3.2]{CE} fails in the modular case.
-It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as no analogue of the polynomial $\wF(z; s_1, \ldots, s_r, c)$ exists in that setting.
+It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as there is no analogue of operation of specializing $c$ to $0$.
 \end{remark}
@@
 \begin{remark}
-In the proof of Proposition \ref{prop:ci}, we require that $c$ avoids $0$ for Lemma \ref{lem:sum-zero}, $c$ avoids $\{-1, 1,\dots,(p-1)/2\}$ for Proposition \ref{prop:linind}, and that $c$ avoids a non-explicit finite set given by vanishing of a determinantal ideal.
+In the proof of Proposition \ref{prop:ci}, we require that $c$ avoids $\{-1, 1,\dots,(p-1)/2\}$ for Proposition \ref{prop:linind} and that $c$ avoids a non-explicit finite set given by vanishing of a determinantal ideal.
 These are the only uses of the assumption that $c$ is generic, so Proposition \ref{prop:ci} and Theorem \ref{thm:main} hold for $c$ avoiding these values.

### 2016-03-28 submission3r2.tex
Fix wording

@@
 Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
-On the other hand, we just showed that there is some degree $d > 0$ so that $I_0^d = A^d$, meaning that $\dim I_c^d < \dim A^d$ exactly when $c$ lies in the zero set of all size $\dim A^d$ minors of $H$.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I_0^d = A^d$, meaning that $\dim I_c^d < \dim A^d$ exactly when $c$ lies in the zero set of all size $\dim A^d$ minors of $H$, viewed as polynomials in $c$.
 This implies that for all but finitely many $c$ we have $\dim I_c^d = \dim A^d$, hence $\dim_k(A/I_c) < \infty$ and $A/I_c$ is a complete intersection.

### 2016-04-04 submission3r2.tex
minor typos

@@
 By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $f_1, \ldots, f_{n-1}$ in degree $p$.
-Therefore $A/I_c$ is a complete intersection if and only $I_c$ cuts out a projective variety of dimension $(n - 2) - (n - 1) = -1$, meaning it is empty.
+Therefore $A/I_c$ is a complete intersection if and only if $I_c$ cuts out a projective variety of dimension $(n - 2) - (n - 1) = -1$, meaning it is empty.
 This occurs if and only if the saturation of $I_c$ is $A$, which occurs if and only if $\dim_k(A/I_c) < \infty$.
@@
 \]
-meaning that $(x_1^p, \ldots, x_n^p) \subset I_0$ and hence $\dim_k(A/I_c) < \infty$.
+meaning that $(x_1^p, \ldots, x_n^p) \subset I_0$ and hence $\dim_k(A/I_0) < \infty$.
 Now, let $A^d$ and $I_c^d$ denote the degree $d$ pieces of $A$ and $I_c$, respectively.
@@
 However, our proof differs from the ``residues by parts'' argument which appears there, as the crucial \cite[Lemma 3.2]{CE} fails in the modular case.
-It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as there is no analogue of operation of specializing $c$ to $0$.
+It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as there is no analogue for the operation of specializing $c$ to $0$.
 \end{remark}

### 2016-05-12 formalwriteup.tex
updated formalwriteup

@@
 
-\subsection{Proving $f_i$ are singular vectors}
-
-We now show that the $f_i$ are singular vectors summing to $0$.
-
-\begin{lemma} \label{lem:sum-zero}
-For $c \neq 0$, we have $\sum_{i = 1}^n f_i = 0$.
-\end{lemma}
-\begin{proof}
-By Lemma \ref{lem:dFdz}, we have that
-\[
-zF'(z) = z V(z) - \sum_{j = 1}^n \frac{cx_jz}{1 - x_j z} F(z) = z V(z) - c \sum_{j = 1}^n \frac{1}{1 - x_j z} F(z),
-\]
-where we subtract $ncF(z)$ in the second equality.
-Notice that $[z^p]$ coefficient of the left side is $0$ because $[z^{p - 1}] F'(z) = 0$ and that $[z^p] zV(z) = 0$.
-Therefore, we conclude that $c \sum_i f_i = 0$, giving the desired.
-\end{proof}
+\subsection{Proving $f_1, \ldots, f_{n-1}$ are singular vectors}
 
 \begin{proposition}\label{prop:ann} 
-The elements $f_i$ for $i=1,\dots,n-1$ are singular vectors in $A$.
+The elements $f_1, \ldots, f_{n - 1}$ are singular vectors in $A$.
 \end{proposition}
 \begin{proof}
-We must show that $f_i$ is annihilated by $D_{y_j - y_l}$ for all $j \ne l$.
+We must show that for $i = 1, \ldots, n - 1$, $f_i$ is annihilated by $D_{y_j - y_l}$ for all $j \ne l$.
 First, by symmetry it suffices to consider $f_1$.
@@
 \begin{proof}
-By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $\{f_i\}$ in degree $p$.
-We will now show that for generic $c$, if $\alpha_1,\dots,\alpha_{n} \in k$ satisfy $f_i(\alpha_1,\dots,\alpha_{n})=0$ for $i = 1, \ldots, n$, then $\alpha_1=\dots=\alpha_{n}=0$.
-Because $f_n$ lies in the span of $f_1, \ldots, f_{n - 1}$ for $c \neq 0$ by Lemma \ref{lem:sum-zero}, this will imply that $\supp(A/I_c) = \{(0, \ldots, 0)\}$ and hence $A/I_c$ has dimension $0$, completing the proof.
+By Proposition~\ref{prop:linind}, $I_c$ has a set of $n-1$ linearly independent and therefore minimal generators $f_1, \ldots, f_{n-1}$ in degree $p$.
+Therefore $A/I_c$ is a complete intersection if and only if $I_c$ cuts out a projective variety of dimension $(n - 2) - (n - 1) = -1$, meaning it is empty.
+This occurs if and only if the saturation of $I_c$ is $A$, which occurs if and only if $\dim_k(A/I_c) < \infty$.
 
-Suppose that the $\alpha_i$ take values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i > 0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$, $\sum_i m_i s_i = 0$, and $\sum_i m_i = n$.
-We claim that for generic $c$ this implies $s_i = 0$ for all $i$.
-Let $B = k[s_1, \ldots, s_r]/(\sum_i m_i s_i = 0)$; it suffices to check that with $I_c$ interpreted as an ideal in $B$, the quotient $B/I_c$ is finite dimensional over $k$.
-
-Define the polynomial $h(z) = \prod_{i = 1}^r (z - s_i)$, and let the series expansion of $F(z)$ be given by 
+If $c = 0$, by definition of $f_i$ we see that $f_i = x_i^p$.  Note that 
 \[
-F(z) = \sum_{i \geq 0} a_i(s_1, \ldots, s_r, c) z^i,
+f_n = x_n^p = (-x_1 - \cdots - x_{n-1})^p = - x_1^p - \cdots - x_{n - 1}^p = - f_1 - \cdots - f_{n -1} \in I_0,
 \]
-where $a_i$ has degree $i$ in $s_1, \ldots, s_r$ and $a_0(s_1, \ldots, s_r, c) = 1$.  Define a degree $p$ polynomial in $z$ by
-\[
-\wF(z; s_1, \ldots, s_r, c) := \sum_{i = 0}^p a_i(s_1, \ldots, s_r, c) z^{p - i}.
-\]
-In this notation, we have that 
-\[
-f_i = [z^p]\frac{1}{1-s_iz}F(z) = \wF(s_i; s_1, \ldots, s_r, c) = 0
-\]
-for $i = 1, \ldots, r$.  Notice that $\wF(s_i; s_1, \ldots, s_r, c)$ is a polynomial in $s_1, \ldots, s_r$ of homogeneous degree $p$.  By the definition of $F(z)$, we have
-\[
-\wF(z; s_1, \ldots, s_r, 0) = z^p,
-\]
-meaning that if $c = 0$, we have $s_1 = \cdots = s_r = 0$, hence $B/I_0$ is finite dimensional over $k$.
-
-Now, let $B^d$ and $I_c^d$ denote the degree $d$ pieces of $B$ and the homogeneous ideal $I_c$, respectively.
-Choose a monomial basis $\{t_i\}$ for $B^d$ independent of $c$, and let $I_c^d$ be spanned by a finite set of polynomials $\{g_j\}$ with $g_j = \sum_i h_{ji}(c) t_i$.
+meaning that $(x_1^p, \ldots, x_n^p) \subset I_0$ and hence $\dim_k(A/I_0) < \infty$.
+Now, let $A^d$ and $I_c^d$ denote the degree $d$ pieces of $A$ and $I_c$, respectively.
+Choose a monomial basis $\{t_i\}$ for $A^d$ independent of $c$, and let $I_c^d$ be spanned by a finite set of polynomials $\{g_j\}$ with $g_j = \sum_i h_{ji}(c) t_i$.
 Notice that $\dim I_c^d$ is given by the size of the maximal non-vanishing minor of the matrix $H = (h_{ji})$.
-On the other hand, we just showed that there is some degree $d > 0$ so that $I^d_0 = B^d$, meaning that $\dim I^d_c < \dim B^d$ exactly when $c$ lies in the zero set of all $\dim B^d$ minors of $H$.
-This implies that for all but finitely many $c$ we have $\dim I^d_c = \dim B^d$ and hence $B/I_c$ is finite-dimensional over $k$.
-
-For each of the finitely many choices of $r, m_1, \ldots, m_r > 0$ with $\sum_i m_i = n$, we conclude that for all but finitely many $c$, if $\{\alpha_1, \ldots, \alpha_n\}$ contains $s_i$ with multiplicity $m_i$, then $\alpha_1 = \cdots = \alpha_n = 0$.
-Taking the union over excluded possibilities for $c$, we conclude that $f_i(\alpha_1, \ldots, \alpha_n) = 0$ implies $\alpha_1 = \cdots = \alpha_n = 0$ unconditionally for generic $c$, so $A/I_c$ is a complete intersection as desired.
+On the other hand, we just showed that there is some degree $d > 0$ so that $I_0^d = A^d$, meaning that $\dim I_c^d < \dim A^d$ exactly when $c$ lies in the zero set of all size $\dim A^d$ minors of $H$, viewed as polynomials in $c$.
+This implies that for all but finitely many $c$ we have $\dim I_c^d = \dim A^d$, hence $\dim_k(A/I_c) < \infty$ and $A/I_c$ is a complete intersection.
 \end{proof}
@@
 However, our proof differs from the ``residues by parts'' argument which appears there, as the crucial \cite[Lemma 3.2]{CE} fails in the modular case.
-It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as no analogue of the polynomial $\wF(z; s_1, \ldots, s_r, c)$ exists in that setting.
+It is interesting to note that our proof does not appear to translate to the characteristic $0$ case, as there is no analogue for the operation of specializing $c$ to $0$.
 \end{remark}
